### 2015-01-14 Proposal/proposal.tex
Proposal Start

\documentclass[dvips,12pt]{article}

% Any percent sign marks a comment to the end of the line

% Every latex document starts with a documentclass declaration like this
% The option dvips allows for graphics, 12pt is the font size, and article
%   is the style

\usepackage[pdftex]{graphicx}
\usepackage{url}

% These are additional packages for "pdflatex", graphics, and to include
% hyperlinks inside a document.

\setlength{\oddsidemargin}{0.25in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}

% These force using more of the margins that is the default style

\begin{document}

% Everything after this becomes content
% Replace the text between curly brackets with your own

\title{A Template for Your Project Proposal}
\author{Ryan Drapeau, Nick Huynh, Aaron Nech}
\date{\today}

% You can leave out "date" and it will be added automatically for today
% You can change the "\today" date to any text you like

\maketitle

% This command causes the title to be created in the document

\section{Introduction}

% An article style is separated into sections and subsections with
%   markup such as this.  Use \section*{Principles} for unnumbered sections.

Each working group should prepare a brief proposal describing what they want
to do.  Please make sure that everyone participates in the discussions and
reviews the document.  The usual way to do this is to have a principle author,
but to pass it around so that everyone can comment and add or edit.  Prepare the
document using \LaTeX\/ because it is good practice and will help you learn the
basics.  However, note that Google Docs (a.k.a. Google Drive) also allows
\LaTeX\/ math symbols and is a reasonable alternative except for submissions
to journals for professional use.  There is help for \LaTeX\/ on the
class website.

Write a brief introduction in which you  outline the scope of your proposed
work. Use this space to explain why you are interested in this topic and what
you hope to learn. Connect your interest with what is currently known, and
include at least two references to related articles in the astronomical
literature.  You can use ADS  \url{http://adswww.harvard.edu/} and other links
on the class website \url{http://prancer.physics.louisville.edu/classes/308/}
to help you find out more. An example citation is this paper
\cite{gonzalez2012}.

One to two pages should suffice for this part, but use more if you want.
Include figures or images if needed.  Figure~\ref{m42} is an example of  how to
do it in \LaTeX.

% \begin{figure}
%     \begin{center}
        % \resizebox{6in}{!}{\includegraphics*{image.png}}
%     \end{center}

%     \caption{Caption}
% \end{figure}

\section{Targets}

Identify the targets you want to study.  Define their observable characteristics
by giving their identifiers (e.g. common name if any, NGC or HD or other catalog
entry you can find with AstroCC and Simbad), celestial coordinates, optical
magnitudes, and angular size if the object is extended, that is, non-stellar.
Please select targets that we have a good likelihood of observing:
\begin{itemize}
\item Not fainter than magnitude 19 (18 is better)
\item Not larger than $0.5^\circ$, but see below
\item Above the horizon at either observatory for several hours this fall
\end{itemize}

A single 100 second exposure with the 0.5 meter telescopes will reach magnitude
18 on a clear night.  Accurate quantitative measurements require a little
brighter, or longer total accumulated exposures.  The telescopes resolve 1
arcsecond in two pixels and have a field of view of $0.6^\circ$.  Larger fields
must be mosaics of several exposures. These factors will affect your
choices.

For planetary imaging the CDK20's can take exposures as short as 0.01 seconds.
The longest practical single exposure is about 300 seconds, but typically we
take 100 second exposures and add them in order to make small guiding
corrections between exposures. Use AstroCC with Stellarium to assure that the
targets are observable this season.

\section{Filters, exposures, and special requests}

Assuming that the best telescope for your work is one of the two 0.5 meters
(CDK20N at Moore Observatory, CDK20S at Mt. Kent), you will have a choice of
filters:  Sloan filter set (g, r, i, or z),  Johnson-Cousins (U, B, V, R, or I),
color imaging (B, G, R, or clear), and narrow band (S $[II]$, red continuum,
H$\alpha$,  O$[III]$.  Identify which filters are of interest.

A typical exposure time for a magnitude 12 star to about half saturation is 100
seconds, but it depends on the filter choice.  Based on this, estimate how many
exposures you will need, and what total time you require.  In some cases, for
example studying an eclipsing or variable star, or an exoplanet transit, you
would use only one filter and make many measurements over a night.  In others,
you may make only a few exposures in each filter, and try many different
filters.   Changing filter sets takes an operator and several minutes, but
changing filters within one set (e.g. a different Sloan filter) takes only a few
seconds.

We have other telescopes that may be available at Moore Observatory this season.
There is a wide field astrograph that has a field of view of $4^\circ$ and is a
fast $f/4$,  especially good for large nebula, comets, or surveys.  A 14-inch
(0.36 meter) Celestron  telescope can be equipped with a fast camera for
planetary imaging.  A 27-inch (0.7 meter)  corrected Dall-Kirkham is scheduled
to be be delivered to Australia this fall, although we are unsure of the actual
date it could see light yet.

\begin{thebibliography}{99}

\bibitem{gonzalez2012} Jonay I. Gonz\'{a}lez Hern\'{a}ndez,
Pilar Ruiz-Lapuente,
Hugo M. Tabernero,
David Montes,
Ramon Canal,
Javier M\'{e}ndez
and Luigi R. Bedin,
{No surviving evolved companions of the progenitor of SN1006},
Nature, {\bf 489}, 533-536 (2012).

\end{thebibliography}

\end{document}

### 2015-01-15 src/js/App.ts
fixed

@@ -1,4 +1,4 @@
-///<reference path="./def/phaser.d.ts"/>
+///<reference path="./def/phaser.d.ts" />
 
 import SpeechProcesser = require('./speechprocessing/SpeechProcesser');
 

### 2015-01-15 src/js/BootState.ts

@@ -5,18 +5,22 @@
 class BootState extends Phaser.State {
     public preload() {
         this.load.image('menuBackground', 'img/menu-background.png');
+        this.load.image('balloonsBackground', 'img/balloons-background.png');
         this.load.image('playButton', 'img/play-button.png');
         this.load.image('upButton', 'img/up-button.png');
         this.load.image('downButton', 'img/down-button.png');
         this.load.image('settingsButton', 'img/settings-button.png');
         this.load.image('combContainer', 'img/comb-container.png');
-        this.load.image('gameIconBalloons', 'img/game-icon-balloons.png')
-        this.load.image('gameIconMaze', 'img/game-icon-maze.png')
+        this.load.image('gameIconBalloons', 'img/game-icon-balloons.png');
+        this.load.image('gameIconMaze', 'img/game-icon-maze.png');
+        this.load.spritesheet('beeBig', 'img/bee-big.png', 128, 109, 2);
+        this.load.image('beeBasket', 'img/bee-basket.png');
+        this.load.image('balloon', 'img/balloon.png');
     }
 
     public create() {
         // Cause the game to go fullscreen
-        (<any> this.game.scale).scaleMode = Phaser.ScaleManager.SHOW_ALL;
+        this.game.scale.scaleMode = Phaser.ScaleManager.SHOW_ALL;
         // Maximum touches allowed at once
         this.input.maxPointers = 1;
 

### 2015-01-15 src/js/balloongame/BalloonGameState.ts

@@ -2,13 +2,20 @@
  * The main balloon game state
  */
 class BalloonGameState extends Phaser.State {
+    private background : Phaser.Sprite;
+    private basket : Phaser.Sprite;
+    private balloon : Phaser.Sprite;
 
     public preload() {
 
     }
 
     public create() {
-
+        this.background = this.game.add.sprite(0, 0, 'balloonsBackground');
+        this.basket = this.game.add.sprite(this.world.centerX - 38, this.world.height - 100, 'beeBasket');
+        this.balloon = this.game.add.sprite(this.world.centerX - 20, this.world.height - 200, 'balloon')
+        this.game.add.tween(this.basket)
+                     .to({y:this.world.height - 108}, 600, Phaser.Easing.Linear.None, true, 0, 1000, true);
     }
 }
 

### 2015-01-15 src/js/def/phaser.d.ts

@@ -1,4 +1,4 @@
-/// <reference path="pixi.d.ts" />
+/// <reference path="./pixi.d.ts" />
 
 // Type definitions for Phaser dev2.2.0 RC12 2014-12-02
 // Project: https://github.com/photonstorm/phaser

### 2015-01-15 src/js/menu/MainMenuState.ts

@@ -17,6 +17,8 @@ class MainMenuState extends Phaser.State {
 
     private gameIcon : Phaser.Sprite;
 
+    private bee : Phaser.Sprite;
+
     private currentSelected : number;
 
     public preload() {
@@ -26,6 +28,7 @@ class MainMenuState extends Phaser.State {
     public create() {
         this.currentSelected = 0;
         this.background = this.game.add.sprite(0, 0, 'menuBackground');
+        this.bee = this.game.add.sprite(520, 15, 'beeBig');
 
         this.combContainer = this.game.add.sprite(this.world.centerX - 230, 270, 'combContainer');
 
@@ -37,6 +40,12 @@ class MainMenuState extends Phaser.State {
         this.settings = this.add.button(
                             this.world.width - 50, this.world.height - 50,
                             'settingsButton', this.onClickSettings, this);
+        // Animate the bee
+        var anim = this.bee.animations.add('fly');
+        anim.play(10, true);
+        this.game.add.tween(this.bee).to({y:30}, 350, Phaser.Easing.Linear.None, true, 0, 1000, true);
+
+
         this.gameIcon = null;
 
         this.updateSelectedGame();
@@ -48,7 +57,7 @@ class MainMenuState extends Phaser.State {
             this.gameIcon.destroy();
             this.gameIcon = null;
         }
-        this.gameIcon = this.add.sprite(this.world.centerX - 220, 281, selectedMinigame.icon);
+        this.gameIcon = this.add.sprite(this.world.centerX - 219, 281, selectedMinigame.icon);
     }
 
     private onClickPlay(state) {

### 2015-01-15 src/js/speechprocessing/SpeechProcesser.ts

@@ -1,9 +1,12 @@
+import SpeechSettings = require('./SpeechSettings');
+
 /**
  * The speech processor is a singleton that can be configured
- *
  */
 class SpeechProcesser {
     private static INSTANCE : SpeechProcesser = null;
+
+    private settings : SpeechSettings;
 
     /**
      * Should not be called directly. Use getInstance() instead.
@@ -12,6 +15,8 @@ class SpeechProcesser {
         if (SpeechProcesser.INSTANCE != null) {
             throw 'Singleton already constructed!';
         }
+
+        this.settings = new SpeechSettings();
     }
 
     /**
@@ -23,6 +28,7 @@ class SpeechProcesser {
         if (SpeechProcesser.INSTANCE == null) {
             return new SpeechProcesser();
         }
+
         return SpeechProcesser.INSTANCE;
     }
 }

### 2015-01-15 src/js/speechprocessing/SpeechSettings.ts

@@ -1,0 +1,10 @@
+/**
+ * Encapsulation of the speech settings specified by the user
+ */
+class SpeechSettings {
+    constructor() {
+
+    }
+}
+
+export = SpeechSettings;

### 2015-01-15 Proposal/proposal.tex

@@
-\documentclass[dvips,12pt]{article}
+\documentclass{article}
+\usepackage{graphicx}
+\usepackage{hyperref}
 
-% Any percent sign marks a comment to the end of the line
-
-% Every latex document starts with a documentclass declaration like this
-% The option dvips allows for graphics, 12pt is the font size, and article
-%   is the style
-
-\usepackage[pdftex]{graphicx}
-\usepackage{url}
-
-% These are additional packages for "pdflatex", graphics, and to include
-% hyperlinks inside a document.
-
-\setlength{\oddsidemargin}{0.25in}
+\setlength{\oddsidemargin}{0in}
+\setlength{\evensidemargin}{0in}
 \setlength{\textwidth}{6.5in}
@@
 \setlength{\textheight}{8.5in}
-
-% These force using more of the margins that is the default style
+\hypersetup{colorlinks = true, urlcolor = blue}
 
@@
 
-% Everything after this becomes content
-% Replace the text between curly brackets with your own
-
-\title{A Template for Your Project Proposal}
-\author{Ryan Drapeau, Nick Huynh, Aaron Nech}
-\date{\today}
-
-% You can leave out "date" and it will be added automatically for today
-% You can change the "\today" date to any text you like
+\title{Kimbee: A Speech Therapy Application For Children}
+\author{Ryan Drapeau \and Nick Huynh \and Aaron Nech}
+\date{\{drapeau, necha, huynick\}@cs.washington.edu}
 
@@
 
-% This command causes the title to be created in the document
+\section{Abstract}
 
-\section{Introduction}
+Many kids have difficulty pronouncing certain sounds and their parents are forced to pay for speech therapy for their children.
+We hope to create a web application that doubles as a game in order to help children who are undergoing speech therapy recognize and pronounce certain sounds.
+The game should keep children wanting to play more, making their speech therapy seem like less of a chore and help them learn by having the children try say the word then correct or reward them depending on their pronunciation.
 
-% An article style is separated into sections and subsections with
-%   markup such as this.  Use \section*{Principles} for unnumbered sections.
+\section{Scenarios and Goals}
 
-Each working group should prepare a brief proposal describing what they want
-to do.  Please make sure that everyone participates in the discussions and
-reviews the document.  The usual way to do this is to have a principle author,
-but to pass it around so that everyone can comment and add or edit.  Prepare the
-document using \LaTeX\/ because it is good practice and will help you learn the
-basics.  However, note that Google Docs (a.k.a. Google Drive) also allows
-\LaTeX\/ math symbols and is a reasonable alternative except for submissions
-to journals for professional use.  There is help for \LaTeX\/ on the
-class website.
+A scenario that highlights how the project will actually be used by an end-user.
+You might include a sketch of the UI, if there is one.
+Describe any special constraints (e.g., speed, size, storage, scale, robustness) your design needs to satisfy.\\\\
+A child has difficulty pronouncing and differentiating the ``l'' and ``r'' sounds.
+He goes to speech therapy but in order to reinforce his learning, he can use Kimbee.
+Before starting, his mother or father can pick the setting designed to help correct ``l'' and ``r'' sounds then let him play Kimbee.
+He will hear a word, say it back and depending on his pronunciation, advance in the game or have the word repeated back at him until he learns.
 
-Write a brief introduction in which you  outline the scope of your proposed
-work. Use this space to explain why you are interested in this topic and what
-you hope to learn. Connect your interest with what is currently known, and
-include at least two references to related articles in the astronomical
-literature.  You can use ADS  \url{http://adswww.harvard.edu/} and other links
-on the class website \url{http://prancer.physics.louisville.edu/classes/308/}
-to help you find out more. An example citation is this paper
-\cite{gonzalez2012}.
+\section{Design Strategy}
 
-One to two pages should suffice for this part, but use more if you want.
-Include figures or images if needed.  Figure~\ref{m42} is an example of  how to
-do it in \LaTeX.
+\href{http://syl22-00.github.io/pocketsphinx.js/}{PocketSphinx.js}
 
-% \begin{figure}
-%     \begin{center}
-        % \resizebox{6in}{!}{\includegraphics*{image.png}}
-%     \end{center}
+An open source port of CMU pocketsphinx to javascript that will serve as our sound processing backend.\\\\
+Word Processor
 
-%     \caption{Caption}
-% \end{figure}
+A set of software built on top of (and interfaces with) the PocketSphinx.js library.
+This will be the set of software that our game(s) communicates with while playing.
+This will also track performance on certain words.
+This set of software will also serve words to the game upon request (i.e, getNextWord()).\\\\
+Game(s)
 
-\section{Targets}
+A series of mini games (one or more depending on how far we get), that utilize the Word Processor described above as a central part of gameplay for practicing speech.\\\\
+App
 
-Identify the targets you want to study.  Define their observable characteristics
-by giving their identifiers (e.g. common name if any, NGC or HD or other catalog
-entry you can find with AstroCC and Simbad), celestial coordinates, optical
-magnitudes, and angular size if the object is extended, that is, non-stellar.
-Please select targets that we have a good likelihood of observing:
-\begin{itemize}
-\item Not fainter than magnitude 19 (18 is better)
-\item Not larger than $0.5^\circ$, but see below
-\item Above the horizon at either observatory for several hours this fall
-\end{itemize}
+The container where the games are launched from.
+This will also contain options for selecting certain key sounds (``L'' and ``R'' at first), selecting these options will interact with the Word Processor ultimately configuring it for the Game(s).
 
-A single 100 second exposure with the 0.5 meter telescopes will reach magnitude
-18 on a clear night.  Accurate quantitative measurements require a little
-brighter, or longer total accumulated exposures.  The telescopes resolve 1
-arcsecond in two pixels and have a field of view of $0.6^\circ$.  Larger fields
-must be mosaics of several exposures. These factors will affect your
-choices.
+\section{Unkowns and Risks}
 
-For planetary imaging the CDK20's can take exposures as short as 0.01 seconds.
-The longest practical single exposure is about 300 seconds, but typically we
-take 100 second exposures and add them in order to make small guiding
-corrections between exposures. Use AstroCC with Stellarium to assure that the
-targets are observable this season.
+Recognizing the difference between a correct pronunciation and an incorrect one.\\\\
+Designing a game geared towards kids that they will enjoy.
 
-\section{Filters, exposures, and special requests}
+\section{Implementation Plan and Schedule}
 
-Assuming that the best telescope for your work is one of the two 0.5 meters
-(CDK20N at Moore Observatory, CDK20S at Mt. Kent), you will have a choice of
-filters:  Sloan filter set (g, r, i, or z),  Johnson-Cousins (U, B, V, R, or I),
-color imaging (B, G, R, or clear), and narrow band (S $[II]$, red continuum,
-H$\alpha$,  O$[III]$.  Identify which filters are of interest.
+\section{Evaluation}
 
-A typical exposure time for a magnitude 12 star to about half saturation is 100
-seconds, but it depends on the filter choice.  Based on this, estimate how many
-exposures you will need, and what total time you require.  In some cases, for
-example studying an eclipsing or variable star, or an exoplanet transit, you
-would use only one filter and make many measurements over a night.  In others,
-you may make only a few exposures in each filter, and try many different
-filters.   Changing filter sets takes an operator and several minutes, but
-changing filters within one set (e.g. a different Sloan filter) takes only a few
-seconds.
+\section{Related Work}
 
-We have other telescopes that may be available at Moore Observatory this season.
-There is a wide field astrograph that has a field of view of $4^\circ$ and is a
-fast $f/4$,  especially good for large nebula, comets, or surveys.  A 14-inch
-(0.36 meter) Celestron  telescope can be equipped with a fast camera for
-planetary imaging.  A 27-inch (0.7 meter)  corrected Dall-Kirkham is scheduled
-to be be delivered to Australia this fall, although we are unsure of the actual
-date it could see light yet.
-
-\begin{thebibliography}{99}
-
-\bibitem{gonzalez2012} Jonay I. Gonz\'{a}lez Hern\'{a}ndez,
-Pilar Ruiz-Lapuente,
-Hugo M. Tabernero,
-David Montes,
-Ramon Canal,
-Javier M\'{e}ndez
-and Luigi R. Bedin,
-{No surviving evolved companions of the progenitor of SN1006},
-Nature, {\bf 489}, 533-536 (2012).
-
-\end{thebibliography}
+\href{https://itunes.apple.com/us/app/articulation-station-pro/id491998279}{Articulation Station Pro}\\
+``Learn how to pronounce and practice the consonantal sounds in the English language...''\\\\
+Although this application helps young children learn how to pronounce and dictate words, it was not made with children with speech disorders in mind.
+Our application will have a setting which will allow the user or speech therapist the ability to change the part of speech that is being addressed in the game.
+We might also explore the possibility of developing a model of each user’s speech to gain insight into every person that uses Kimbee.
+This will allow us to track the user’s performance over time as he or she continues to use the application.\\\\
+\href{http://dihana.cps.unizar.es/~alborada/docu/2006cvaquero.pdf}{Vocaliza}\\
+``The objective of this application is to help the daily work of the speech therapists that train the linguistic skills of Spanish speakers with different language pathologies.''\\\\
+Unfortunately, as mentioned at the end of this paper, this application failed to create a game that was intuitive for children to play.
+Although the authors designed an impressive system for modeling user speech, the “game” wasn’t anything of the sort.
+Vocaliza allowed users to select a word and then practice speaking it over and over.
+This did not include any game like mechanics.
+Kimbee will be a progressive move based game where the user can earn more moves by performing better in speech.\\\\
+\href{http://www.speech.kth.se/prod/publications/files/841.pdf}{OLP (Ortho-Logo-Paedia)}\\
+``This paper presents an overview of a newly started EU-funded research project and outlines the design of the speech therapy structure to be used within the project.''\\\\
+This paper addresses the fact that having a visual feedback system is important for children to be able to learn and improve their speech.
+However, it fails to provide a solution.
+Kimbee will be a tool to help children with speech impediments wrapped around a game that provides the user with feedback.
+For example, the user could attain a move to use every time they score high on a word or sentence.
+This would keep the child or user entertained and engaged while they used the application and it provides motivation to improve and do better.
 

### 2015-01-15 src/js/balloongame/BalloonGameState.ts
fixed

@@ -1,3 +1,5 @@
+import MicrophoneButton = require('../common/MicrophoneButton');
+
 /**
  * The main balloon game state
  */

### 2015-01-15 src/js/common/MicrophoneButton.ts

@@ -1,0 +1,31 @@
+/**
+ * Acts as a button for recording sound by interfacing with our speech processing singleton
+ * For use in all application games
+ */
+class MicrophoneButton extends Phaser.Button {
+
+    constructor(game : Phaser.Game, x : number, y : number) {
+        super(game, x, y, 'microphoneButton', this.onClickAction, this);
+        this.onInputOver.add(this.onOverAction, this);
+        this.onInputOut.add(this.onOutAction, this);
+        this.onInputUp.add(this.onUpAction, this);
+    }
+
+    private onClickAction() {
+
+    }
+
+    private onUpAction() {
+
+    }
+
+    private onOutAction() {
+
+    }
+
+    private onOverAction() {
+
+    }
+}
+
+export = MicrophoneButton;

### 2015-01-16 Proposal/proposal.tex
Finished Proposal

@@
 \usepackage{hyperref}
+\usepackage[parfill]{parskip}
 
@@
 \setlength{\textwidth}{6.5in}
-\setlength{\topmargin}{0in}
-\setlength{\textheight}{8.5in}
+\setlength{\topmargin}{-0.75in}
+\setlength{\textheight}{9.25in}
 \hypersetup{colorlinks = true, urlcolor = blue}
@@
 The game should keep children wanting to play more, making their speech therapy seem like less of a chore and help them learn by having the children try say the word then correct or reward them depending on their pronunciation.
+We will speak with a professional speech therapist in order to help shape our game and the feedback it gives back to children in order to give more constructive feedback than simply repeating the correct pronunciation back to them.
 
@@
 
-A scenario that highlights how the project will actually be used by an end-user.
-You might include a sketch of the UI, if there is one.
-Describe any special constraints (e.g., speed, size, storage, scale, robustness) your design needs to satisfy.\\\\
 A child has difficulty pronouncing and differentiating the ``l'' and ``r'' sounds.
-He goes to speech therapy but in order to reinforce his learning, he can use Kimbee.
-Before starting, his mother or father can pick the setting designed to help correct ``l'' and ``r'' sounds then let him play Kimbee.
-He will hear a word, say it back and depending on his pronunciation, advance in the game or have the word repeated back at him until he learns.
+He or she goes to speech therapy but in order to reinforce his or her learning, he or she can use Kimbee.
+Before starting, his or her mother or father can pick the setting designed to help correct ``l'' and ``r'' sounds then let him or her play Kimbee.
+He or she will hear a word, say it back and depending on his pronunciation, advance in the game or have the word repeated back at him or her until he learns.
 
@@
 
-\href{http://syl22-00.github.io/pocketsphinx.js/}{PocketSphinx.js}
+\centerline{\textbf{Main Components}}
 
-An open source port of CMU pocketsphinx to javascript that will serve as our sound processing backend.\\\\
-Word Processor
+\begin{tabular}{cc}
+    \centering
+    \includegraphics[width=0.46\textwidth]{outline.png} & \includegraphics[width=0.5\textwidth]{states.png}\\
+    Figure 1 & Figure 2
+\end{tabular}
 
+\newpage
+
+\href{http://syl22-00.github.io/pocketsphinx.js/}{\textbf{PocketSphinx.js}}\\
+An open source port of CMU pocket-sphinx to javascript that will serve as our sound processing backend.
+
+\textbf{Speech Processor}\\
 A set of software built on top of (and interfaces with) the PocketSphinx.js library.
@@
 This will also track performance on certain words.
-This set of software will also serve words to the game upon request (i.e, getNextWord()).\\\\
-Game(s)
+This set of software will also serve words to the game upon request (i.e, getNextWord()).
 
-A series of mini games (one or more depending on how far we get), that utilize the Word Processor described above as a central part of gameplay for practicing speech.\\\\
-App
+\href{http://phaser.io/}{\textbf{Phaser.js}}\\
+The game framework we will utilize to manage game state, media assets, and user interactivity. This framework is a good choice because it allows multiple platform targets for our final product.
 
-The container where the games are launched from.
-This will also contain options for selecting certain key sounds (``L'' and ``R'' at first), selecting these options will interact with the Word Processor ultimately configuring it for the Game(s).
+\textbf{Game(s)}\\
+A series of bee-themed mini games (one or more depending on how far we get), that utilize the Word Processor described above as a central part of gameplay for practicing speech.
+
+\textbf{Launch / Settings Platform}\\
+The entry point of our application where the games are launched from.
+This will also contain options for selecting certain key sounds (``L'' and ``R'' at first), selecting these options will interact with the \textit{Word Processor} ultimately configuring it for the \textit{Game(s)}.
+Implementation wise, this is analogous to our main menu.
+
+The interactions between all of these components are shown in Figure 1.
+
+\section{Implementation Details}
+
+\textbf{States}\\
+The flow of the application will be modeled with Phaser states. See Figure 2.
+
+\textbf{Speech Processor}\\
+The main internal speech processor API will be constructed as a singleton object.
+This will be a interface that is a composite of many objects that run and manage the speech therapy part of the game.
+The game states above will interact with this singleton through its interface.
+Exact architecture of the speech processor is yet to be determined, but will interact with the PocketSphinx.js library.
 
@@
 
-Recognizing the difference between a correct pronunciation and an incorrect one.\\\\
+Recognizing the difference between a correct pronunciation and an incorrect one.
 Designing a game geared towards kids that they will enjoy.
+Giving feedback when a child gives an incorrect answer that is constructive and assists their learning further than just repeating the word back to them.
 
@@
 
+\begin{enumerate}
+    \item Application scaffolding (game structure, menu, options) (week 4)
+    \begin{enumerate}
+        \item Create phaser.js application
+        \item Create game states listed above in this project specification
+        \item Setup main menu with game launching capabilities
+        \item Create SpeechProcessor singleton and associated speech module classes
+    \end{enumerate}
+    \item Simple game screen to connect to speech API for testing (week 4)
+    \begin{enumerate}
+        \item Create simple game, and hook up to launcher created in (1)
+        \item Connect API calls to fetch next available therapy word
+        \item Connect API calls to start and stop microphone data gathering through a phaser based object that materializes as a microphone start/stop button
+        \item Connect API calls to process data
+        \item Connect API calls to determine success or failure on pronunciation
+        \item Place (a)-(d) in an iterative game loop with some termination amount until game completion
+        \item After game completion, move user to completed screen, and allow returning to launch menu defined in (1)
+    \end{enumerate}
+    \item Contact therapists and refine project goals / industry need (week 6)
+    \begin{enumerate}
+        \item Email therapist
+        \item Set up meetings to learn about current processes and how to best target our project
+    \end{enumerate}
+    \item Web Audio API, Microphone capture, Data pipeline in javascript (week 6)
+    \begin{enumerate}
+        \item Create module/class interfaced by (2) through the API singleton created in (1) to store and manipulate therapy settings
+        \item Create module/class interfaced by (2) through the API singleton created in (1) to get next word based on settings defined in (a)
+        \item Create module/class interfaced by (2) through the API singleton created in (1) to gather microphone audio feedback and return it
+    \end{enumerate}
+    \item Speech, phoneme recognition in javascript with pocketsphinx.js (week 6)
+    \begin{enumerate}
+        \item Create module/class interfaced by (2) through the API singleton created in (1) to take microphone feedback and compute phoneme translation confidences with pocketsphinx.js and the phoneme translator model
+        \item Create module interfaced by (2) through the API singleton created in (1) to process phoneme confidences produced by (d) and return a success or failure based on settings stored in (4a) and defined by the user through the option menu specified in (1)
+    \end{enumerate}
+    \item Progress tracking metrics related to confidence data on child performance (week 8)
+    \begin{enumerate}
+        \item Create ProgressTracker object that will be composited in the SpeechProcessor singleton
+        \item Hook up this tracker object to intercept API calls on SpeechProcessor and record progress on metrics determined in (3)
+        \item Create screen attached to option menu to display progress stored in (a)
+        \item Create web server endpoints to store child data and accessible by therapist (this a further goal)
+        \item Further machine learning, predictions, etc on the data as therapist suggests
+    \end{enumerate}
+    \item Iterate specific progress tracking implementations with therapist feedback (week 8)
+    \begin{enumerate}
+        \item Stay in contact with therapist and show them how our work progresses
+    \end{enumerate}
+    \item More games that utilize javascript speech API defined in the above sections (week 10)
+    \begin{enumerate}
+        \item Create a maze based game (idea 1)
+    \end{enumerate}
+    \item Polish everything, animations, graphics, sound etc. (week 10)
+    \begin{enumerate}
+        \item Check for bugs, issues, screen transition problems
+        \item Test speech api extensively until it is smooth
+        \item Gather feedback from therapist and maybe children
+        \item Spend a lot of effort polishing art work, game tweens, animations, and sound
+    \end{enumerate}
+    \item Package up to apps and deliver to app store (week 10)
+    \begin{enumerate}
+        \item Use phaser.js and phone pipelines that exist
+        \item Create app icons, splash screens, and other necessary app store content
+    \end{enumerate}
+    \item Write up / Poster (week 11)
+\end{enumerate}
+
 \section{Evaluation}
+
+We will try to meet with a speech therapist to see if they will implement Kimbee as part of their therapy course or if they can recommend it to their patients.
+We will be successful if we provide a game that the kids can learn from and a game that they will enjoy playing.
+We can measure the first by tracking a child's feedback and seeing if their responses become clearer as time moves on and the second by measuring how much a child is using the app per week.
+By charting multiple childrens' feedback, we can display their learning on our final report and evaluate whether or not a game setting was appropriate or not for helping children learn.
 
@@
 Our application will have a setting which will allow the user or speech therapist the ability to change the part of speech that is being addressed in the game.
-We might also explore the possibility of developing a model of each user’s speech to gain insight into every person that uses Kimbee.
-This will allow us to track the user’s performance over time as he or she continues to use the application.\\\\
+We might also explore the possibility of developing a model of each user's speech to gain insight into every person that uses Kimbee.
+This will allow us to track the user’s performance over time as he or she continues to use the application.\\[25 pt]
 \href{http://dihana.cps.unizar.es/~alborada/docu/2006cvaquero.pdf}{Vocaliza}\\
@@
 This did not include any game like mechanics.
-Kimbee will be a progressive move based game where the user can earn more moves by performing better in speech.\\\\
+Kimbee will be a progressive move based game where the user can earn more moves by performing better in speech.\\[25 pt]
 \href{http://www.speech.kth.se/prod/publications/files/841.pdf}{OLP (Ortho-Logo-Paedia)}\\

### 2015-01-16 src/js/App.ts
fixed

@@ -1,6 +1,6 @@
 ///<reference path="./def/phaser.d.ts" />
 
-import SpeechProcesser = require('./speechprocessing/SpeechProcesser');
+import SpeechProcessor = require('./speechprocessing/SpeechProcessor');
 
 // Boot state
 import BootState = require('./BootState');

### 2015-01-16 src/js/BootState.ts

@@ -16,6 +16,7 @@ class BootState extends Phaser.State {
         this.load.spritesheet('beeBig', 'img/bee-big.png', 128, 109, 2);
         this.load.image('beeBasket', 'img/bee-basket.png');
         this.load.image('balloon', 'img/balloon.png');
+        this.load.spritesheet('microphoneButton', 'img/microphone-button.png', 110, 110, 3);
     }
 
     public create() {

### 2015-01-16 src/js/balloongame/BalloonGameState.ts

@@ -7,6 +7,7 @@ class BalloonGameState extends Phaser.State {
     private background : Phaser.Sprite;
     private basket : Phaser.Sprite;
     private balloon : Phaser.Sprite;
+    private microphone : MicrophoneButton;
 
     public preload() {
 
@@ -15,7 +16,8 @@ class BalloonGameState extends Phaser.State {
     public create() {
         this.background = this.game.add.sprite(0, 0, 'balloonsBackground');
         this.basket = this.game.add.sprite(this.world.centerX - 38, this.world.height - 100, 'beeBasket');
-        this.balloon = this.game.add.sprite(this.world.centerX - 20, this.world.height - 200, 'balloon')
+        this.balloon = this.game.add.sprite(this.world.centerX - 20, this.world.height - 200, 'balloon');
+        this.microphone = new MicrophoneButton(this.game, 20, 20);
         this.game.add.tween(this.basket)
                      .to({y:this.world.height - 108}, 600, Phaser.Easing.Linear.None, true, 0, 1000, true);
     }

### 2015-01-16 src/js/common/MicrophoneButton.ts

@@ -1,30 +1,35 @@
+import SpeechProcessor = require('../speechprocessing/SpeechProcessor');
+
 /**
  * Acts as a button for recording sound by interfacing with our speech processing singleton
  * For use in all application games
  */
 class MicrophoneButton extends Phaser.Button {
+    private speechProcessor : SpeechProcessor;
+    private isActive : boolean;
+
+    private static DISABLED_FRAME : number = 2;
+    private static ACTIVE_FRAME : number = 1;
+    private static NORMAL_FRAME : number = 0;
 
     constructor(game : Phaser.Game, x : number, y : number) {
         super(game, x, y, 'microphoneButton', this.onClickAction, this);
-        this.onInputOver.add(this.onOverAction, this);
-        this.onInputOut.add(this.onOutAction, this);
-        this.onInputUp.add(this.onUpAction, this);
+        this.frame = MicrophoneButton.NORMAL_FRAME;
+        this.isActive = false;
+        this.speechProcessor = SpeechProcessor.getInstance();
+        game.add.existing(this);
     }
 
     private onClickAction() {
-
-    }
-
-    private onUpAction() {
-
-    }
-
-    private onOutAction() {
-
-    }
-
-    private onOverAction() {
-
+        if (this.isActive) {
+            // Disable and process
+            this.frame = MicrophoneButton.DISABLED_FRAME;
+            this.isActive = false;
+        } else {
+            // Start processing
+            this.frame = MicrophoneButton.ACTIVE_FRAME;
+            this.isActive = true;
+        }
     }
 }
 

### 2015-01-16 src/js/speechprocessing/SpeechProcessor.ts

@@ -3,8 +3,8 @@ import SpeechSettings = require('./SpeechSettings');
 /**
  * The speech processor is a singleton that can be configured
  */
-class SpeechProcesser {
-    private static INSTANCE : SpeechProcesser = null;
+class SpeechProcessor {
+    private static INSTANCE : SpeechProcessor = null;
 
     private settings : SpeechSettings;
 
@@ -12,7 +12,7 @@ class SpeechProcesser {
      * Should not be called directly. Use getInstance() instead.
      */
     constructor() {
-        if (SpeechProcesser.INSTANCE != null) {
+        if (SpeechProcessor.INSTANCE != null) {
             throw 'Singleton already constructed!';
         }
 
@@ -24,13 +24,13 @@ class SpeechProcesser {
      *
      * @returns {SpeechProcessor} the speech processor instance
      */
-    public static getInstance() : SpeechProcesser {
-        if (SpeechProcesser.INSTANCE == null) {
-            return new SpeechProcesser();
+    public static getInstance() : SpeechProcessor {
+        if (SpeechProcessor.INSTANCE == null) {
+            return new SpeechProcessor();
         }
 
-        return SpeechProcesser.INSTANCE;
+        return SpeechProcessor.INSTANCE;
     }
 }
 
-export = SpeechProcesser;
+export = SpeechProcessor;

### 2015-01-18 src/js/App.ts
Added pocketsphinx consumer

@@ -20,7 +20,7 @@ import BalloonGameState = require('./balloongame/BalloonGameState');
 class App extends Phaser.Game {
 
     constructor() {
-        super(800, 600, Phaser.AUTO, '', null);
+        super(1280, 720, Phaser.AUTO, '', null);
 
         // Setup states
         this.state.add("BootState", BootState);

### 2015-01-18 src/js/BootState.ts

@@ -28,9 +28,10 @@ class BootState extends Phaser.State {
         //  Phaser will automatically pause if the browser tab the game is in loses focus. Disable this
         this.stage.disableVisibilityChange = true;
 
+        this.scale.pageAlignHorizontally = true;
+
         if (this.game.device.desktop) {
             // Desktop Settings
-            this.scale.pageAlignHorizontally = true;
         } else {
             // Mobile settings
         }

### 2015-01-18 src/js/speechprocessing/AudioStorageConsumer.ts

@@ -14,7 +14,7 @@ class AudioStorageConsumer {
      */
     public getSamples() {
         // Flattened samples
-        return [].concat.apply([], this.samples);
+        return this.samples;
     }
 
     /**
@@ -29,6 +29,7 @@ class AudioStorageConsumer {
      * @param e The message posted
      */
     public postMessage(e : any) {
+        console.log('TO CONSUMERS: ');
         console.log(e);
         switch (e.command) {
             case 'process':

### 2015-01-18 src/js/speechprocessing/SpeechProcessor.ts

@@ -38,9 +38,10 @@ class SpeechProcessor {
 
     /**
      * Start recording sound. Does nothing if sound is already being recorded.
+     * @param callback The function to call when recording has started
      */
-    public startRecording() : void {
-        this.microphone.start();
+    public startRecording(callback) : void {
+        this.microphone.start(callback);
     }
 
     /**

### 2015-01-19 Proposal/proposal.tex
Capitals

@@
 \begin{enumerate}
-    \item Application scaffolding (game structure, menu, options) (week 4)
+    \item Application scaffolding (game structure, menu, options) (Week 4)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Simple game screen to connect to speech API for testing (week 4)
+    \item Simple game screen to connect to speech API for testing (Week 4)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Contact therapists and refine project goals / industry need (week 6)
+    \item Contact therapists and refine project goals / industry need (Week 6)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Web Audio API, Microphone capture, Data pipeline in javascript (week 6)
+    \item Web Audio API, Microphone capture, Data pipeline in javascript (Week 6)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Speech, phoneme recognition in javascript with pocketsphinx.js (week 6)
+    \item Speech, phoneme recognition in javascript with pocketsphinx.js (Week 6)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Progress tracking metrics related to confidence data on child performance (week 8)
+    \item Progress tracking metrics related to confidence data on child performance (Week 8)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Iterate specific progress tracking implementations with therapist feedback (week 8)
+    \item Iterate specific progress tracking implementations with therapist feedback (Week 8)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item More games that utilize javascript speech API defined in the above sections (week 10)
+    \item More games that utilize javascript speech API defined in the above sections (Week 10)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Polish everything, animations, graphics, sound etc. (week 10)
+    \item Polish everything, animations, graphics, sound etc. (Week 10)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Package up to apps and deliver to app store (week 10)
+    \item Package up to apps and deliver to app store (Week 10)
     \begin{enumerate}
@@
     \end{enumerate}
-    \item Write up / Poster (week 11)
+    \item Write up / Poster (Week 11)
 \end{enumerate}

### 2015-03-08 _cordova/platforms/android/assets/www/js/App.ts
fixed

@@ -1,0 +1,37 @@
+///<reference path="./def/phaser.d.ts" />
+import SpeechProcessor = require('./speechprocessing/SpeechProcessor');
+
+// Boot state
+import BootState = require('./BootState');
+
+// Menu states
+import MainMenuState = require('./menu/MainMenuState');
+import OptionMenuState = require('./menu/OptionMenuState');
+
+// Maze game states
+import MazeGameState = require('./mazegame/MazeGameState');
+
+// Balloon game states
+import BalloonGameState = require('./balloongame/BalloonGameState');
+
+/**
+ * Main Application class
+ */
+class App extends Phaser.Game {
+
+    constructor() {
+        super(1280, 720, Phaser.AUTO, '', null);
+
+        // Setup states
+        this.state.add("BootState", BootState);
+        this.state.add("MainMenuState", MainMenuState);
+        this.state.add("OptionMenuState", OptionMenuState);
+        this.state.add("BalloonGameState", BalloonGameState);
+        this.state.add("MazeGameState", MazeGameState);
+
+        // Start application
+        this.state.start("BootState");
+    }
+}
+
+export = App;

### 2015-03-08 _cordova/platforms/android/assets/www/js/BootState.ts

@@ -1,0 +1,64 @@
+///<reference path="./def/phaser.d.ts" />
+import SpeechProcessor = require('./speechprocessing/SpeechProcessor');
+import Server = require('./server/Server');
+
+/**
+ * The boot state of the Application
+ * This state is visited briefly before the game loads completely
+ */
+class BootState extends Phaser.State {
+    public preload() {
+        this.load.image('backButton', 'img/back-button.png');
+        this.load.image('menuBackground', 'img/menu-background.png');
+        this.load.image('balloonsBackground', 'img/balloons-background.png');
+        this.load.image('playButton', 'img/play-button.png');
+        this.load.image('upButton', 'img/up-button.png');
+        this.load.image('downButton', 'img/down-button.png');
+        this.load.image('settingsButton', 'img/settings-button.png');
+        this.load.image('combContainer', 'img/comb-container.png');
+        this.load.image('gameIconBalloons', 'img/game-icon-balloons.png');
+        this.load.image('gameIconMaze', 'img/game-icon-maze.png');
+        this.load.spritesheet('beeBig', 'img/bee-big.png', 128, 109, 2);
+        this.load.image('beeBasket', 'img/bee-basket.png');
+        this.load.image('balloon', 'img/balloon.png');
+        this.load.image('flower', 'img/flower-purple.png'); 
+        this.load.image('honey', 'img/honey.png');
+        this.load.image('wasp', 'img/buff-wasp.jpg');
+        this.load.spritesheet('fairy', 'img/princess.png', 65, 75, 2);
+        this.load.spritesheet('microphoneButton', 'img/microphone-button.png', 110, 110, 3);
+        this.load.audio('tada', 'sfx/ta-da.mp3');
+        this.load.audio('try-again', 'sfx/try-again.mp3');
+    }
+
+    public create() {
+        var wordStyle = { font: "45px Arial", fill: "#333333", align: "center" };
+        var text = this.game.add.text(this.world.width / 3, this.world.height / 10, "loading...", wordStyle);
+
+        // Cause the game to go fullscreen
+        this.game.scale.scaleMode = Phaser.ScaleManager.SHOW_ALL;
+        // Maximum touches allowed at once
+        this.input.maxPointers = 1;
+
+        //  Phaser will automatically pause if the browser tab the game is in loses focus. Disable this
+        this.stage.disableVisibilityChange = true;
+
+        this.scale.pageAlignHorizontally = true;
+
+        if (this.game.device.desktop) {
+            // Desktop Settings
+        } else {
[…]

### 2015-03-08 _cordova/platforms/android/assets/www/js/balloongame/BalloonGameState.ts

@@ -1,0 +1,236 @@
+///<reference path="../def/phaser.d.ts" />
+import MicrophoneButton = require('../common/MicrophoneButton');
+import HoneyCounter = require('../common/HoneyCounter');
+import SpeechProcessor = require('../speechprocessing/SpeechProcessor');
+
+
+/**
+ * The main balloon game state
+ */
+class BalloonGameState extends Phaser.State {
+    private background : Phaser.Sprite;
+    private bee : Phaser.Sprite;
+    private balloon : Phaser.Sprite;
+    private flower : Phaser.Sprite;
+    private honey : Phaser.Group;
+    private tada : Phaser.Sound;
+    private tryagain : Phaser.Sound;
+    private word : Phaser.Text;
+    private microphone : MicrophoneButton;
+    private speechProcessor : SpeechProcessor;
+    private honeyCounter : HoneyCounter;
+    private wasp : Phaser.Group;
+    private fairy : Phaser.Group;
+    private height : number;
+    private width : number;
+    private lastX : number;
+    private lost : boolean;
+    private lastHoneyX : number;
+    private honeyChain : number;
+    private micPause : boolean;
+    private gameOver : Phaser.Text;
+
+    public preload() {
+        this.speechProcessor = SpeechProcessor.getInstance();
+    }
+
+    public create() {
+        var firstWord = this.speechProcessor.getNextWord();
+        var wordStyle = { font: "45px Cambria", fill: "#333333", align: "center" };
+        var gameOverStyle = { font: "80px Cambria", fill: "#000000", align: "center" };
+        this.tada = this.game.add.audio('tada');
+        this.tryagain = this.game.add.audio('try-again');
+
+        this.height = this.world.height;
+        this.width = this.world.width;
+        this.lastX = this.width / 5;
+
+
+        this.background = this.game.add.sprite(0, 0, 'balloonsBackground');
+        this.flower = this.game.add.sprite(this.width * 4 / 5, this. height / 2, 'flower');
+        this.bee = this.game.add.sprite(this.width / 5, this.height / 2, 'beeBig');
+        this.bee.scale.x = 0.7;
+        this.bee.scale.y = 0.7;
+        var anim = this.bee.animations.add('fly');
+        anim.play(10, true);
+        this.game.physics.enable(this.bee, Phaser.Physics.ARCADE);
+        this.bee.body.immovable = true;
+        this.bee.body.velocity.x = 0;
[…]

### 2015-03-08 _cordova/platforms/android/assets/www/js/bootstrap.ts

@@ -1,0 +1,32 @@
+// require.js (our library that manages all these javascript files)
+// needs a "main file" to derive all dependencies from and execute.
+// This is that file.
+
+///<reference path="./def/phaser.d.ts" />
+
+import App = require('./App');
+
+declare var cordova : any;
+declare var PhoneGap : any;
+declare var phonegap : any;
+
+/**
+ * Determine whether the file loaded from PhoneGap or not
+ */
+function isPhoneGap() {
+    return (typeof cordova != "undefined"
+         || typeof PhoneGap != "undefined"
+         || typeof phonegap != "undefined")
+        && /^file:\/{3}[^\/]/i.test(window.location.href)
+        && /ios|iphone|ipod|ipad|android/i.test(navigator.userAgent);
+}
+
+function ready() {
+    new App();
+}
+
+if (isPhoneGap()) {
+    document.addEventListener("deviceready", ready, false);
+} else {
+    ready();
+}

### 2015-03-08 _cordova/platforms/android/assets/www/js/common/MicrophoneButton.ts

@@ -1,0 +1,79 @@
+///<reference path="../def/phaser.d.ts" />
+import SpeechProcessor = require('../speechprocessing/SpeechProcessor');
+
+/**
+ * Acts as a button for recording sound by interfacing with our speech processing singleton
+ * For use in all application games
+ */
+class MicrophoneButton extends Phaser.Button {
+    private speechProcessor : SpeechProcessor;
+    private isActive : boolean;
+    private isDisabled : boolean;
+    private clientResultCallback : Function;
+
+    private static DISABLED_FRAME : number = 2;
+    private static ACTIVE_FRAME : number = 1;
+    private static NORMAL_FRAME : number = 0;
+
+    /**
+     * Constructs a microphone button
+     *
+     * @param game The game context to attach the button to
+     * @param x The x coordinate to place the button
+     * @param y The y coordinate to place the button
+     * @param dataCallback A function callback that is executed on finishing recording with the data
+     */
+    constructor(game : Phaser.Game, x : number, y : number, dataCallback : Function) {
+        super(game, x, y, 'microphoneButton', this.onClickAction, this);
+        this.frame = MicrophoneButton.NORMAL_FRAME;
+        this.clientResultCallback = dataCallback;
+        this.isActive = false;
+        this.isDisabled = false;
+        this.speechProcessor = SpeechProcessor.getInstance();
+        game.add.existing(this);
+    }
+
+    /**
+     * Disables the button, disabling all functionality. If the microphone button is in the middle
+     * of recording, the recording will be thrown out.
+     */
+    public disable() {
+        this.frame = MicrophoneButton.DISABLED_FRAME;
+        this.isDisabled = true;
+    }
+
+    /**
+     * Enables the button, showing the current active state.
+     */
+    public enable() {
+        this.frame = this.isActive ? MicrophoneButton.ACTIVE_FRAME : MicrophoneButton.NORMAL_FRAME;
+        this.isDisabled = false;
+    }
+
+    /**
+     * Called on button click
+     */
+    private onClickAction() {
+        if (!this.isDisabled) {
+            if (this.isActive) {
+                this.isActive = false;
+                this.disable();
+                this.speechProcessor.stopRecording((result) => {
+                    this.clientResultCallback(result);
+                    this.enable();
+                });
+            } else {
+                this.disable();
+                this.speechProcessor.startRecording(() => {
+                    this.isActive = true;
+                    // Switch visual state and start processing
[…]

### 2015-03-08 _cordova/platforms/android/assets/www/js/mazegame/MazeGameState.ts

@@ -1,0 +1,15 @@
+///<reference path="../def/phaser.d.ts" />
+/**
+ * The main maze game state
+ */
+class MazeGameState extends Phaser.State {
+    public preload() {
+
+    }
+
+    public create() {
+
+    }
+}
+
+export = MazeGameState;

### 2015-03-08 _cordova/platforms/android/assets/www/js/menu/OptionMenuState.ts

@@ -1,0 +1,31 @@
+///<reference path="../def/phaser.d.ts" />
+
+import Server = require('../server/Server');
+
+/**
+ * The option menu of the application.
+ */
+class OptionMenuState extends Phaser.State {
+    private server : Server;
+    private keyText : Phaser.Text;
+    private back : Phaser.Button;
+
+    public preload() {
+        this.server = Server.getInstance();
+    }
+
+    public create() {
+        var key = this.server.getKey();
+        var wordStyle = { font: "45px Arial", fill: "#333333", align: "center" };
+        this.keyText = this.game.add.text(this.world.width / 3, this.world.height / 10, key, wordStyle);
+        this.back = this.add.button(
+            10, 10,
+            'backButton', () => { this.onClickBack(this.game.state); }, this);
+    }
+
+    private onClickBack(state) {
+        state.start('MainMenuState', true, false);
+    }
+}
+
+export = OptionMenuState;

### 2015-03-08 _cordova/platforms/android/assets/www/js/speechprocessing/Microphone.ts

@@ -1,0 +1,178 @@
+import AudioStorageConsumer = require('./AudioStorageConsumer');
+import RecognizerConsumer = require('./RecognizerConsumer');
+import SpeechSettings = require('./SpeechSettings');
+import WordBank = require('./WordBank');
+
+// Vanilla javascript / audio api declarations for typescript
+declare var AudioContext : any;
+declare var window : any;
+declare var navigator : any;
+declare var AudioRecorder : any;
+
+// Deal with prefixed APIs
+window.AudioContext = window.AudioContext || window.webkitAudioContext;
+navigator.getUserMedia = navigator.getUserMedia ||
+                         navigator.webkitGetUserMedia ||
+                         navigator.mozGetUserMedia;
+
+/**
+ * Manages communication with the device microphone
+ */
+class Microphone {
+    private currentlyRecording : boolean;
+    private audioContext : any;
+    private audioRecorder : any;
+    private clientReadyFunction : Function;
+    private clientResultFunction : Function;
+
+    private numberConsuming : number;
+
+    private storageConsumer : AudioStorageConsumer;
+    private recognizerConsumer : RecognizerConsumer;
+
+    private settings : SpeechSettings;
+    private wordBank : WordBank;
+
+    constructor(clientReadyFunction : Function, settings : SpeechSettings, wordBank : WordBank) {
+        this.settings = settings;
+        this.wordBank = wordBank;
+        this.currentlyRecording = false;
+        this.audioRecorder = null;
+        this.clientReadyFunction = clientReadyFunction;
+
+        try {
+            this.audioContext = new window.AudioContext();
+        } catch (e) {
+            console.log("Error initializing Web Audio");
+        }
+
+        // Get user permissions for audio capture
+        if (navigator.getUserMedia) {
+            navigator.getUserMedia({audio: true},
+                                    (stream) => {this.onInitAudio(stream)},
+                                    (e) => {console.log("No live audio input in this browser");});
+        } else {
+            throw "No web audio support in this browser";
+        }
+    }
+
+    /**
+     * Called when user grants permission to initialize audio capture
+     */
+    private onInitAudio(stream : any) {
+        var volume = this.audioContext.createGain();
+        var input = this.audioContext.createMediaStreamSource(stream);
+        input.connect(volume);
+        this.audioRecorder = new AudioRecorder(input, {volume : volume, worker : './js/vendor/audioRecorderWorker.js'});
+
+        this.spawnConsumers(() => {
+            this.clientReadyFunction();
+        });
+    }
+
[…]

### 2015-03-08 _cordova/platforms/android/assets/www/js/speechprocessing/SpeechProcessor.ts

@@ -1,0 +1,118 @@
+import SpeechSettings = require('./SpeechSettings');
+import Server = require('../server/Server');
+import Microphone = require('./Microphone');
+import WordBank = require('./WordBank');
+
+/**
+ * The speech processor singleton
+ * This acts as the central speech therapy API endpoint for the rest of the program
+ */
+class SpeechProcessor {
+    private static INSTANCE : SpeechProcessor = null;
+
+    private settings : SpeechSettings;
+    private microphone : Microphone;
+    private wordBank : WordBank;
+
+    private currentWord : string;
+
+    /**
+     * Should not be called directly. Use getInstance() instead.
+     */
+    constructor(callback ?: Function) {
+        if (SpeechProcessor.INSTANCE != null) {
+            throw 'Singleton already constructed!';
+        }
+
+        this.currentWord = null;
+
+        this.settings = new SpeechSettings();
+        this.wordBank = new WordBank();
+        this.wordBank.setWords(this.settings.getWordBank());
+
+        this.microphone = new Microphone(() => {
+            console.log('Microphone ready.');
+            if (callback) {
+                callback();
+            }
+        }, this.settings, this.wordBank);
+    }
+
+    /**
+     * Gets the singleton instance of the speech processor
+     * @param {Function?} callback The (optional) callback to call when the SpeechProcessor is fully constructed.
+     * @returns {SpeechProcessor} the speech processor instance
+     */
+    public static getInstance(callback ?: Function) : SpeechProcessor {
+        if (SpeechProcessor.INSTANCE == null) {
+            SpeechProcessor.INSTANCE = new SpeechProcessor(callback);
+        }
+
+        return SpeechProcessor.INSTANCE;
+    }
+
+    /**
+     * Start recording sound. Does nothing if sound is already being recorded.
+     * @param callback The function to call when recording has started
+     */
+    public startRecording(callback) : void {
+        this.microphone.start(callback);
+    }
+
+    /**
+     * Stop recording sound. Returns the sound recorded
+     */
+    public stopRecording(callback : Function) : any {
+        this.microphone.stop((result) => {
+            // Send recording to server
+            var server = Server.getInstance();
+            var pair = this.wordBank.getCurrentPair();
+            server.sendRecording(result[0], pair.right, this.getCorrectness(result));
+
+            // Continue the callback chain
+            callback(result);
+        });
+    }
+
+    /**
+     * Returns an integer representing correctness in the last word guess
[…]

### 2015-03-08 _cordova/platforms/android/assets/www/js/speechprocessing/SpeechSettings.ts

@@ -1,0 +1,95 @@
+/**
+ * Encapsulation of the speech settings specified by the user
+ */
+class SpeechSettings {
+    private static DEFAULT_SOUND : any = 'R';
+    private static DATA_MAP : any = {
+
+        /*
+        Global sphinx maps
+        (contain all words possible and their phonemes and recognition grammars)
+        */
+        sphinxWords : [
+            ["GREEN", "G R IY N"], ["GWEEN", "G W IY N"],
+            ["RABBIT", "R AE B AH T"], ["WABBIT", "W AE B AH T"],
+            ["AIR", "EH R"], ["AIW", "EH W"],
+            ["ARE", "AA R"], ["AWE", "AA W"],
+            ["BAR", "B AA R"], ["BAW", "B AA W"],
+            ["BEAR", "B EH R"], ["BEAW", "B EH W"],
+            ["BOAR", "B AO R"], ["BOAW", "B AO W"],
+            ["CAR", "K AA R"], ["CAW", "K AA W"],
+            ["CARE", "K EH R"], ["CAWE", "K EH W"]
+        ],
+
+        sphinxGrammars : [
+            {word : "GREEN", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "GWEEN"}, {from: 0, to: 1, word: "GREEN"}]}},
+            {word : "RABBIT", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "WABBIT"}, {from: 0, to: 1, word: "RABBIT"}]}},
+            {word : "AIR", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "AIW"}, {from: 0, to: 1, word: "AIR"}]}},
+            {word : "ARE", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "AWE"}, {from: 0, to: 1, word: "ARE"}]}},
+            {word : "BAR", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "BAW"}, {from: 0, to: 1, word: "BAR"}]}},
+            {word : "BEAR", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "BEAW"}, {from: 0, to: 1, word: "BEAR"}]}},
[…]

### 2015-03-08 _cordova/platforms/android/src/com/nickaaronryan/kimbee/CordovaApp.java

@@ -1,0 +1,35 @@
+/*
+       Licensed to the Apache Software Foundation (ASF) under one
+       or more contributor license agreements.  See the NOTICE file
+       distributed with this work for additional information
+       regarding copyright ownership.  The ASF licenses this file
+       to you under the Apache License, Version 2.0 (the
+       "License"); you may not use this file except in compliance
+       with the License.  You may obtain a copy of the License at
+
+         http://www.apache.org/licenses/LICENSE-2.0
+
+       Unless required by applicable law or agreed to in writing,
+       software distributed under the License is distributed on an
+       "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
+       KIND, either express or implied.  See the License for the
+       specific language governing permissions and limitations
+       under the License.
+ */
+
+package com.nickaaronryan.kimbee;
+
+import android.os.Bundle;
+import org.apache.cordova.*;
+
+public class CordovaApp extends CordovaActivity
+{
+    @Override
+    public void onCreate(Bundle savedInstanceState)
+    {
+        super.onCreate(savedInstanceState);
+        super.init();
+        // Set by <content src="index.html" /> in config.xml
+        loadUrl(launchUrl);
+    }
+}

### 2015-03-08 _cordova/www/js/common/DOMTextField.ts

@@ -1,0 +1,31 @@
+///<reference path="../def/phaser.d.ts" />
+
+/**
+ * Represents a text field in the game
+ * which is a DOM text field floated over the game
+ * and kept in context of the virtual pixel coordinates
+ */
+class DOMTextField {
+    private game : Phaser.Game;
+    private x : number;
+    private y : number;
+    private w : number;
+    private h : number;
+
+    constructor(game : Phaser.Game, x : number, y: number, w : number, h : number) {
+        this.game = game;
+        this.x = x;
+        this.y = y;
+        this.w = w;
+        this.h = w;
+
+        this.addToCanvas();
+    }
+
+
+    private addToCanvas() {
+        var parent = this.game.canvas.parentElement;
+    }
+}
+
+export = DOMTextField;

### 2015-03-08 _cordova/www/js/menu/MainMenuState.ts

@@ -1,0 +1,88 @@
+///<reference path="../def/phaser.d.ts" />
+/**
+ * The main menu of the application.
+ */
+class MainMenuState extends Phaser.State {
+    private static MINI_GAMES : any = [
+        {state : 'BalloonGameState', icon : 'gameIconBalloons'},
+        {state : 'MazeGameState', icon : 'gameIconMaze'}
+    ];
+
+    private play : Phaser.Button;
+    private settings : Phaser.Button;
+    private selectUp : Phaser.Button;
+    private selectDown : Phaser.Button;
+    private background : Phaser.Sprite;
+
+    private combContainer : Phaser.Sprite;
+
+    private gameIcon : Phaser.Sprite;
+
+    private bee : Phaser.Sprite;
+
+    private currentSelected : number;
+
+    public preload() {
+
+    }
+
+    public create() {
+        this.currentSelected = 0;
+        this.background = this.game.add.sprite(0, 0, 'menuBackground');
+        this.bee = this.game.add.sprite(970, 95, 'beeBig');
+
+        this.combContainer = this.game.add.sprite(this.world.centerX - 230, 370, 'combContainer');
+
+        this.selectUp = this.add.button(this.world.centerX - 200, 300, 'upButton', this.onClickSelectUp, this);
+        this.selectDown = this.add.button(this.world.centerX - 200, 480, 'downButton', this.onClickSelectDown, this);
+        this.play = this.add.button(
+                            this.world.centerX + 50, 370,
+                            'playButton', () => { this.onClickPlay(this.game.state); }, this);
+        this.settings = this.add.button(
+                            this.world.width - 50, this.world.height - 50,
+                            'settingsButton', this.onClickSettings, this);
+        // Animate the bee
+        var anim = this.bee.animations.add('fly');
+        anim.play(10, true);
+        this.game.add.tween(this.bee).to({y:115}, 350, Phaser.Easing.Linear.None, true, 0, 1000, true);
+
+
+        this.gameIcon = null;
+
+        this.updateSelectedGame();
+    }
+
+    private updateSelectedGame() {
+        var selectedMinigame = MainMenuState.MINI_GAMES[this.currentSelected];
+        if (this.gameIcon != null) {
+            this.gameIcon.destroy();
+            this.gameIcon = null;
+        }
+        this.gameIcon = this.add.sprite(this.world.centerX - 219, 381, selectedMinigame.icon);
+    }
+
[…]

### 2015-03-08 _cordova/www/js/server/Server.ts

@@ -1,0 +1,88 @@
+///<reference path="../def/jquery.d.ts" />
+declare var Hashids : any;
+
+/**
+ * The server API singleton
+ * This acts as the central server API endpoint for the rest of the app
+ */
+class Server {
+    private static URL : string = "/api/";
+
+    private static INSTANCE : Server = null;
+
+    private key : string;
+    private enabled : boolean;
+
+    /**
+     * Should not be called directly. Use getInstance() instead.
+     */
+    constructor() {
+        if (Server.INSTANCE != null) {
+            throw 'Singleton already constructed!';
+        }
+
+        this.enabled = true;
+
+        // Set the client token to a new generated token if one has not
+        // been generated yet.
+        var token : string = window.localStorage.getItem('token');
+        if (token) {
+            this.key = token;
+        } else {
+            var hash : any = new Hashids(Math.random() * 2147483647 + "");
+            this.key = hash.encode((new Date()).getTime());
+            window.localStorage.setItem('token', this.key);
+        }
+
+        console.log(this.key);
+    }
+
+    /**
+     * Gets the singleton instance of the API
+     * @returns {API} the speech processor instance
+     */
+    public static getInstance() : Server {
+        if (Server.INSTANCE == null) {
+            Server.INSTANCE = new Server();
+        }
+
+        return Server.INSTANCE;
+    }
+
+    /**
+     * Helper returns true if this client can send information to the server
+     * @returns {boolean} True if we can send, false otherwise
+     */
+    private canSend() : boolean {
+        return this.enabled && this.key != null;
+    }
+
+    /**
+     * Get the client key used by the application
+     * @return {string} The client key
+     */
+    public getKey() : string {
+        return this.key;
+    }
+
+    /**
+     * Sends a recording to the server
+     * @param {number[]} rawData The raw data of the recording
+     * @param {string} word The word they are saying
+     */
+    public sendRecording(rawData : any, word : string, correctness : number) : void {
+        if (!this.canSend()) return;
+
+        (<any> $).post(Server.URL + 'recording/add', {
+            token : this.key,
+            raw : rawData,
+            word : word,
+            correctness : correctness
+        }, function(data) {
+            console.log("Recording saved on server. Response:");
+            console.log(data);
+        });
+    }
+}
+
+export = Server;

### 2015-03-08 _cordova/www/js/speechprocessing/RecognizerConsumer.ts

@@ -1,0 +1,114 @@
+import SpeechSettings = require('./SpeechSettings');
+
+/**
+ * RecognizerConsumer is a consumer that recognizes hypothesis based on a model.
+ */
+class RecognizerConsumer {
+    private settings : SpeechSettings;
+    private worker : Worker;
+    private callbackIndex : number;
+    private callbackSequence : Function[];
+
+    private onStopped : Function;
+
+    private words : any;
+    private grammars : any;
+    private hypotheses : any[];
+
+    constructor(worker : Worker, settings : SpeechSettings, onStopped : Function) {
+        this.onStopped = onStopped;
+        this.worker = worker;
+        this.worker.onmessage = (e) => {
+            this.onWorkerMessage(e);
+        }
+
+
+        this.hypotheses = [];
+
+        this.settings = settings;
+        this.words = settings.getSphinxWords();
+        this.grammars = settings.getSphinxGrammars();
+    }
+
+    /**
+     * Initializes the worker, relies on the worker-message rely to
+     * simulate callbacks tracked by this class state.
+     * @param callback The function to be notified when ready
+     */
+    public initWorkerData(callback : Function) : void {
+        this.worker.postMessage({'command' : 'initialize'});
+        // Will execute these callbacks in sequence when worker responds to main UI thread after media loading.
+        this.callbackSequence = [this.loadWords];
+        for (var i = 0; i < this.grammars.length; i++) {
+            var closure = ((i) => {
+                return () => {
+                    this.loadGrammar(i);
+                };
+            })(i);
+            this.callbackSequence.push(closure);
+        }
+        this.callbackSequence.push(callback);
+        this.callbackIndex = 0;
+    }
+
+    /**
+     * Loads the words to recognize
+     */
+    private loadWords() : void {
+        // load words
+        this.worker.postMessage({'command' : 'addWords', 'data' : this.words});
+    }
+
+    /**
+     * Loads the ith grammar to recognize
+     */
+    private loadGrammar(i : number) : void {
+        this.worker.postMessage({'command' : 'addGrammar', 'data' : this.grammars[i].g});
+    }
+
+    /**
+     * Get the hypotheses stored by this recognizer consumer
+     * @returns The hypotheses stored.
+     */
+    public getHypotheses() : any[] {
+        return this.hypotheses;
+    }
+
+    /**
+     * Callback to deal with worker messages back to the main thread
+     * @param e The message sent to the main thread
[…]

### 2015-03-08 _cordova/www/js/speechprocessing/WordBank.ts

@@ -1,0 +1,55 @@
+/**
+ * WordBank is a managed collection of words to speak
+ */
+class WordBank {
+    private current : number;
+    private words : any[];
+
+    constructor() {
+        this.words = [];
+        this.current = 0;
+    }
+
+    /**
+     * Sets the current word bank
+     * @param wordBank The word bank to set
+     */
+    public setWords(wordBank : string[]) {
+        this.words = wordBank;
+        this.current = 0;
+    }
+
+    /**
+     * Gets the current (right/wrong) pair
+     * @returns {any|null} The pair, null if not found
+     */
+    public getCurrentPair() {
+        return this.words[this.current] || null;
+    }
+
+    /**
+     * Gets the current (right/wrong) index
+     * @returns {number} The index
+     */
+    public getCurrentIndex() {
+        return this.current;
+    }
+
+    /**
+     * Gets the next word to display, returns null if one is not
+     * available.
+     * @returns {string} The word
+     */
+    public next() : string {
+        if (this.words.length == 0) return null;
+
+        this.current++;
+        this.current %= this.words.length;
+
+        var pair = this.words[this.current];
+
+        return pair.right;
+    }
+}
+
+export = WordBank;

### 2015-03-08 Paper/paper.tex

\documentclass{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}

\usetikzlibrary{automata,positioning}

\topmargin=-0.30in
\evensidemargin=0in
\oddsidemargin=0.25in
\textwidth=6in
\textheight=8.80in
\headsep=0.25in

\linespread{1.1}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\renewcommand*\contentsname{Table of Contents}

\begin{document}

\vspace{0.65 in}
\begin{centering}
\LARGE{\textbf{Kimbee: A Speech Therapy \\Application For Children}}\\[7 pt]
\Large{Ryan Drapeau \hspace{30 pt} Nick Huynh \hspace{30 pt} Aaron Nech}\\[5 pt]
\large{\{drapeau, necha, huynick\}@cs.washington.edu}

\end{centering}

\vspace*{1.25 in}

\begin{centering}
\section*{Abstract}

\end{centering}

[ABSTRACT HERE]

\newpage

\section{Introduction}

\section{Background}

% CONTENT

\section{Conclusion}

\end{document}

### 2015-03-08 src/game/js/menu/MainMenuState.ts
fixed

@@ -33,8 +33,8 @@ class MainMenuState extends Phaser.State {
 
         this.combContainer = this.game.add.sprite(this.world.centerX - 230, 370, 'combContainer');
 
-        this.selectUp = this.add.button(this.world.centerX - 200, 300, 'upButton', this.onClickSelectUp, this);
-        this.selectDown = this.add.button(this.world.centerX - 200, 480, 'downButton', this.onClickSelectDown, this);
+        this.selectUp = this.add.button(this.world.centerX - 300, 390, 'upButton', this.onClickSelectUp, this);
+        this.selectDown = this.add.button(this.world.centerX - 100, 390, 'downButton', this.onClickSelectDown, this);
         this.play = this.add.button(
                             this.world.centerX + 50, 370,
                             'playButton', () => { this.onClickPlay(this.game.state); }, this);

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
fixed

@@ -17,6 +17,7 @@ class BalloonGameState extends Phaser.State {
     private tryagain : Phaser.Sound;
     private honeyPickup : Phaser.Sound;
     private word : Phaser.Text;
+    private fps : Phaser.Text;
     private microphone : MicrophoneButton;
     private speechProcessor : SpeechProcessor;
     private honeyCounter : HoneyCounter;
@@ -61,6 +62,7 @@ class BalloonGameState extends Phaser.State {
         this.game.physics.enable(this.bee, Phaser.Physics.ARCADE);
         this.bee.body.immovable = true;
         this.bee.body.velocity.x = 0;
+        this.fps = this.game.add.text(0, 0, "FPS: 60", wordStyle);
         this.word = this.game.add.text(this.width / 3, this.height / 10, "Now say: " + firstWord, wordStyle);
         this.word.visible = false;
         this.microphone = new MicrophoneButton(this.game, 20, 20, (res) => { this.onMicrophoneFinish(res);} );
@@ -226,6 +228,7 @@ class BalloonGameState extends Phaser.State {
     }
 
     public update() {
+        this.fps.setText("FPS: " + this.game.time.fps);
         if (this.game.input.mousePointer.isDown && !this.micPause) {
             if (this.game.input.mousePointer.y > this.bee.body.y) {
                 this.bee.body.velocity.y = this.height / 3;

### 2015-03-08 src/game/js/BootState.ts
fixed

@@ -23,7 +23,6 @@ class BootState extends Phaser.State {
         this.load.image('balloon', 'img/balloon.png');
         this.load.image('flower', 'img/flower-purple.png'); 
         this.load.image('honey', 'img/honey.png');
-        this.load.image('wasp', 'img/buff-wasp.jpg');
         this.load.spritesheet('fairy', 'img/princess.png', 65, 75, 2);
         this.load.spritesheet('microphoneButton', 'img/microphone-button.png', 110, 110, 3);
         this.load.spritesheet('wasp', 'img/buff-wasp.png', 274 / 2, 109, 2);

### 2015-03-08 src/game/js/BootState.ts
fixed

@@ -45,6 +45,8 @@ class BootState extends Phaser.State {
 
         this.scale.pageAlignHorizontally = true;
 
+        this.game.time.advancedTiming = true;
+
         if (this.game.device.desktop) {
             // Desktop Settings
         } else {

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
fixed

@@ -229,7 +229,8 @@ class BalloonGameState extends Phaser.State {
     }
 
     public update() {
-        this.fps.setText("FPS: " + this.game.time.fps);
+        var txt = 
+        this.fps.setText("GAME OBJ: " + this.game.time.fps);
         if (this.game.input.mousePointer.isDown && !this.micPause) {
             if (this.game.input.mousePointer.y > this.bee.body.bottom) {
                 this.bee.body.velocity.y = this.height / 3;

### 2015-03-08 Paper/paper.tex

@@
-\documentclass{article}
+% This is "sig-alternate.tex" V2.0 May 2012
+% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
+%
+% This example file demonstrates the use of the 'sig-alternate.cls'
+% V2.5 LaTeX2e document class file. It is for those submitting
+% articles to ACM Conference Proceedings WHO DO NOT WISH TO
+% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
+% The 'sig-alternate.cls' file will produce a similar-looking,
+% albeit, 'tighter' paper resulting in, invariably, fewer pages.
+%
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V2.5) produces:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) NO page numbers
+%
+% as against the acm_proc_article-sp.cls file which
+% DOES NOT produce 1) thru' 3) above.
+%
+% Using 'sig-alternate.cls' you have control, however, from within
+% the source .tex file, over both the CopyrightYear
+% (defaulted to 200X) and the ACM Copyright Data
+% (defaulted to X-XXXXX-XX-X/XX/XX).
+% e.g.
+% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
+% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
+%
+% ---------------------------------------------------------------------------------------------------------------
+% This .tex source is an example which *does* use
+% the .bib file (from which the .bbl file % is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission, you *NEED* to 'insert'
+% your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% ================= IF YOU HAVE QUESTIONS =======================
+% Questions regarding the SIGS styles, SIGS policies and
+% procedures, Conferences etc. should be sent to
+% Adrienne Griscti (griscti@acm.org)
+%
+% Technical questions _only_ to
+% Gerald Murray (murray@hq.acm.org)
+% ===============================================================
+%
+% For tracking purposes - this is V2.0 - May 2012
 
-\usepackage{fancyhdr}
-\usepackage{extramarks}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amsfonts}
-\usepackage{tikz}
-\usepackage{graphicx}
-\usepackage{enumitem}
-\usepackage[plain]{algorithm}
-\usepackage{algpseudocode}
-\usepackage[normalem]{ulem}
-\usepackage{hyperref}
-\usepackage{xcolor}
-\usepackage{caption}
-
-\usetikzlibrary{automata,positioning}
-
-\topmargin=-0.30in
-\evensidemargin=0in
-\oddsidemargin=0.25in
-\textwidth=6in
-\textheight=8.80in
-\headsep=0.25in
-
-\linespread{1.1}
-
-\renewcommand\headrulewidth{0.4pt}
-\renewcommand\footrulewidth{0.4pt}
-
-\renewcommand*\contentsname{Table of Contents}
+\documentclass{sig-alternate}
 
 \begin{document}
+%
+% --- Author Metadata here ---
+\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+% --- End of Author Metadata ---
 
-\vspace{0.65 in}
-\begin{centering}
-\LARGE{\textbf{Kimbee: A Speech Therapy \\Application For Children}}\\[7 pt]
-\Large{Ryan Drapeau \hspace{30 pt} Nick Huynh \hspace{30 pt} Aaron Nech}\\[5 pt]
-\large{\{drapeau, necha, huynick\}@cs.washington.edu}
+\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
+Format\titlenote{(Produces the permission block, and
+copyright information). For use with
+SIG-ALTERNATE.CLS. Supported by ACM.}}
+\subtitle{[Extended Abstract]
+\titlenote{A full version of this paper is available as
+\textit{Author's Guide to Preparing ACM SIG Proceedings Using
+\LaTeX$2_\epsilon$\ and BibTeX} at
+\texttt{www.acm.org/eaddress.htm}}}
+%
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
 
-\end{centering}
+\numberofauthors{8} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
+%
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+\alignauthor
+Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
+       \affaddr{Institute for Clarity in Documentation}\\
+       \affaddr{1932 Wallamaloo Lane}\\
+       \affaddr{Wallamaloo, New Zealand}\\
+       \email{trovato@corporation.com}
+% 2nd. author
+\alignauthor
+G.K.M. Tobin\titlenote{The secretary disavows
+any knowledge of this author's actions.}\\
+       \affaddr{Institute for Clarity in Documentation}\\
+       \affaddr{P.O. Box 1212}\\
+       \affaddr{Dublin, Ohio 43017-6221}\\
+       \email{webmaster@marysville-ohio.com}
+% 3rd. author
+\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
+one who did all the really hard work.}\\
+       \affaddr{The Th{\o}rv{\"a}ld Group}\\
+       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+       \affaddr{Hekla, Iceland}\\
+       \email{larst@affiliation.org}
+\and  % use '\and' if you need 'another row' of author names
+% 4th. author
+\alignauthor Lawrence P. Leipuner\\
+       \affaddr{Brookhaven Laboratories}\\
+       \affaddr{Brookhaven National Lab}\\
+       \affaddr{P.O. Box 5000}\\
+       \email{lleipuner@researchlabs.org}
+% 5th. author
+\alignauthor Sean Fogarty\\
+       \affaddr{NASA Ames Research Center}\\
+       \affaddr{Moffett Field}\\
+       \affaddr{California 94035}\\
+       \email{fogartys@amesres.org}
+% 6th. author
+\alignauthor Charles Palmer\\
+       \affaddr{Palmer Research Laboratories}\\
+       \affaddr{8600 Datapoint Drive}\\
+       \affaddr{San Antonio, Texas 78229}\\
+       \email{cpalmer@prl.com}
+}
+% There's nothing stopping you putting the seventh, eighth, etc.
+% author on the opening page (as the 'third row') but we ask,
+% for aesthetic reasons that you place these 'additional authors'
+% in the \additional authors block, viz.
+\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
+email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
+(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
+\date{30 July 1999}
+% Just remember to make sure that the TOTAL number of authors
+% is the number that will appear on the first page PLUS the
+% number that will appear in the \additionalauthors section.
 
-\vspace*{1.25 in}
+\maketitle
+\begin{abstract}
+This paper provides a sample of a \LaTeX\ document which conforms,
+somewhat loosely, to the formatting guidelines for
+ACM SIG Proceedings. It is an {\em alternate} style which produces
+a {\em tighter-looking} paper and was designed in response to
+concerns expressed, by authors, over page-budgets.
+It complements the document \textit{Author's (Alternate) Guide to
+Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
+This source file has been written with the intention of being
+compiled under \LaTeX$2_\epsilon$\ and BibTeX.
 
-\begin{centering}
-\section*{Abstract}
+The developers have tried to include every imaginable sort
+of ``bells and whistles", such as a subtitle, footnotes on
+title, subtitle and authors, as well as in the text, and
+every optional component (e.g. Acknowledgments, Additional
+Authors, Appendices), not to mention examples of
+equations, theorems, tables and figures.
 
-\end{centering}
+To make best use of this sample document, run it through \LaTeX\
+and BibTeX, and compare this source code with the printed
+output produced by the dvi file. A compiled PDF version
+is available on the web page to help you with the
+`look and feel'.
+\end{abstract}
 
-[ABSTRACT HERE]
+% A category with the (minimum) three required fields
+\category{H.4}{Information Systems Applications}{Miscellaneous}
+%A category including the fourth, optional field follows...
+\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-\newpage
+\terms{Theory}
+
+\keywords{ACM proceedings, \LaTeX, text tagging}
 
 \section{Introduction}
+The \textit{proceedings} are the records of a conference.
+ACM seeks to give these conference by-products a uniform,
+high-quality appearance.  To do this, ACM has some rigid
+requirements for the format of the proceedings documents: there
+is a specified format (balanced  double columns), a specified
+set of fonts (Arial or Helvetica and Times Roman) in
+certain specified sizes (for instance, 9 point for body copy),
+a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
+the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
+and (1.9 cm [.75"]) left and right; specified column width
+(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
 
-\section{Background}
+The good news is, with only a handful of manual
+settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
+and {\texttt{\char'134 alignauthor}} commands, you have
+already used; another, {\texttt{\char'134 balancecolumns}}, will
+be used in your very last run of \LaTeX\ to ensure
+balanced column heights on the last page.}, the \LaTeX\ document
+class file handles all of this for you.
 
-% CONTENT
+The remainder of this document is concerned with showing, in
+the context of an ``actual'' document, the \LaTeX\ commands
+specifically available for denoting the structure of a
+proceedings paper, rather than with giving rigorous descriptions
+or explanations of such commands.
 
-\section{Conclusion}
+\section{The {\secit Body} of The Paper}
+Typically, the body of a paper is organized
+into a hierarchical structure, with numbered or unnumbered
+headings for sections, subsections, sub-subsections, and even
+smaller sections.  The command \texttt{{\char'134}section} that
+precedes this paragraph is part of such a
+hierarchy.\footnote{This is the second footnote.  It
+starts a series of three footnotes that add nothing
+informational, but just give an idea of how footnotes work
+and look. It is a wordy one, just so you see
+how a longish one plays out.} \LaTeX\ handles the numbering
+and placement of these headings for you, when you use
+the appropriate heading commands around the titles
+of the headings.  If you want a sub-subsection or
+smaller part to be unnumbered in your output, simply append an
+asterisk to the command name.  Examples of both
+numbered and unnumbered headings will appear throughout the
+balance of this sample document.
 
+Because the entire article is contained in
+the \textbf{document} environment, you can indicate the
+start of a new paragraph with a blank line in your
+input file; that is why this sentence forms a separate paragraph.
+
+\subsection{Type Changes and {\subsecit Special} Characters}
+We have already seen several typeface changes in this sample.  You
+can indicate italicized words or phrases in your text with
+the command \texttt{{\char'134}textit}; emboldening with the
+command \texttt{{\char'134}textbf}
+and typewriter-style (for instance, for computer code) with
+\texttt{{\char'134}texttt}.  But remember, you do not
+have to indicate typestyle changes when such changes are
+part of the \textit{structural} elements of your
+article; for instance, the heading of this subsection will
+be in a sans serif\footnote{A third footnote, here.
+Let's make this a rather short one to
+see how it looks.} typeface, but that is handled by the
+document class file. Take care with the use
+of\footnote{A fourth, and last, footnote.}
+the curly braces in typeface changes; they mark
+the beginning and end of
+the text that is to be in the different typeface.
+
+You can use whatever symbols, accented characters, or
+non-English characters you need anywhere in your document;
+you can find a complete list of what is
+available in the \textit{\LaTeX\
+User's Guide}\cite{Lamport:LaTeX}.
+
+\subsection{Math Equations}
+You may want to display math equations in three distinct styles:
+inline, numbered or non-numbered display.  Each of
+the three are discussed in the next sections.
+
+\subsubsection{Inline (In-text) Equations}
+A formula that appears in the running text is called an
+inline or in-text formula.  It is produced by the
+\textbf{math} environment, which can be
+invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
+construction or with the short form \texttt{\$. . .\$}. You
+can use any of the symbols and structures,
+from $\alpha$ to $\omega$, available in
+\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
+few examples of in-text equations in context. Notice how
+this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
+set here in in-line math style, looks slightly different when
+set in display style.  (See next section).
+
+\subsubsection{Display Equations}
+A numbered display equation -- one set off by vertical space
+from the text and centered horizontally -- is produced
+by the \textbf{equation} environment. An unnumbered display
+equation is produced by the \textbf{displaymath} environment.
+
+Again, in either environment, you can use any of the symbols
+and structures available in \LaTeX; this section will just
+give a couple of examples of display equations in context.
+First, consider the equation, shown as an inline equation above:
+\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
+Notice how it is formatted somewhat differently in
+the \textbf{displaymath}
+environment.  Now, we'll enter an unnumbered equation:
+\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
+and follow it with another numbered equation:
+\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
+just to demonstrate \LaTeX's able handling of numbering.
+
+\subsection{Citations}
+Citations to articles \cite{bowman:reasoning,
+clark:pct, braams:babel, herlihy:methodology},
+conference proceedings \cite{clark:pct} or
+books \cite{salas:calculus, Lamport:LaTeX} listed
+in the Bibliography section of your
+article will occur throughout the text of your article.
+You should use BibTeX to automatically produce this bibliography;
+you simply need to insert one of several citation commands with
+a key of the item cited in the proper location in
+the \texttt{.tex} file \cite{Lamport:LaTeX}.
+The key is a short reference you invent to uniquely
+identify each work; in this sample document, the key is
+the first author's surname and a
+word from the title.  This identifying key is included
+with each item in the \texttt{.bib} file for your article.
+
+The details of the construction of the \texttt{.bib} file
+are beyond the scope of this sample document, but more
+information can be found in the \textit{Author's Guide},
+and exhaustive details in the \textit{\LaTeX\ User's
+Guide}\cite{Lamport:LaTeX}.
+
+This article shows only the plainest form
+of the citation command, using \texttt{{\char'134}cite}.
+This is what is stipulated in the SIGS style specifications.
+No other citation format is endorsed or supported.
+
+\subsection{Tables}
+Because tables cannot be split across pages, the best
+placement for them is typically the top of the page
+nearest their initial cite.  To
+ensure this proper ``floating'' placement of tables, use the
+environment \textbf{table} to enclose the table's contents and
+the table caption.  The contents of the table itself must go
+in the \textbf{tabular} environment, to
+be aligned properly in rows and columns, with the desired
+horizontal and vertical rules.  Again, detailed instructions
+on \textbf{tabular} material
+is found in the \textit{\LaTeX\ User's Guide}.
+
+Immediately following this sentence is the point at which
+Table 1 is included in the input file; compare the
+placement of the table here with the table in the printed
+dvi output of this document.
+
+\begin{table}
+\centering
+\caption{Frequency of Special Characters}
+\begin{tabular}{|c|c|l|} \hline
+Non-English or Math&Frequency&Comments\\ \hline
+\O & 1 in 1,000& For Swedish names\\ \hline
+$\pi$ & 1 in 5& Common in math\\ \hline
+\$ & 4 in 5 & Used in business\\ \hline
+$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+\hline\end{tabular}
+\end{table}
+
+To set a wider table, which takes up the whole width of
+the page's live area, use the environment
+\textbf{table*} to enclose the table's contents and
+the table caption.  As with a single-column table, this wide
+table will ``float" to a location deemed more desirable.
+Immediately following this sentence is the point at which
+Table 2 is included in the input file; again, it is
+instructive to compare the placement of the
+table here with the table in the printed dvi
+output of this document.
+
+\begin{table*}
+\centering
+\caption{Some Typical Commands}
+\begin{tabular}{|c|c|l|} \hline
+Command&A Number&Comments\\ \hline
+\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
+\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
+\texttt{{\char'134}table}& 300 & For tables\\ \hline
+\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
+\end{table*}
+% end the environment with {table*}, NOTE not {table}!
+
+\subsection{Figures}
+Like tables, figures cannot be split across pages; the
+best placement for them
+is typically the top or the bottom of the page nearest
+their initial cite.  To ensure this proper ``floating'' placement
+of figures, use the environment
+\textbf{figure} to enclose the figure and its caption.
+
+This sample document contains examples of \textbf{.eps}
+and \textbf{.ps} files to be displayable with \LaTeX.  More
+details on each of these is found in the \textit{Author's Guide}.
+
+\begin{figure}
+\centering
+\epsfig{file=fly.eps}
+\caption{A sample black and white graphic (.eps format).}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=fly.eps, height=1in, width=1in}
+\caption{A sample black and white graphic (.eps format)
+that has been resized with the \texttt{epsfig} command.}
+\end{figure}
+
+As was the case with tables, you may want a figure
+that spans two columns.  To do this, and still to
+ensure proper ``floating'' placement of tables, use the environment
+\textbf{figure*} to enclose the figure and its caption.
+and don't forget to end the environment with
+{figure*}, not {figure}!
+
+\begin{figure*}
+\centering
+\epsfig{file=flies.eps}
+\caption{A sample black and white graphic (.eps format)
+that needs to span two columns of text.}
+\end{figure*}
+
+Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
+used; use
+the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
+commands as appropriate for the different file types.
+
+\begin{figure}
+\centering
+\psfig{file=rosette.ps, height=1in, width=1in,}
+\caption{A sample black and white graphic (.ps format) that has
+been resized with the \texttt{psfig} command.}
+\vskip -6pt
+\end{figure}
+
+\subsection{Theorem-like Constructs}
+Other common constructs that may occur in your article are
+the forms for logical constructs like theorems, axioms,
+corollaries and proofs.  There are
+two forms, one produced by the
+command \texttt{{\char'134}newtheorem} and the
+other by the command \texttt{{\char'134}newdef}; perhaps
+the clearest and easiest way to distinguish them is
+to compare the two in the output of this sample document:
+
+This uses the \textbf{theorem} environment, created by
+the\linebreak\texttt{{\char'134}newtheorem} command:
+\newtheorem{theorem}{Theorem}
+\begin{theorem}
+Let $f$ be continuous on $[a,b]$.  If $G$ is
+an antiderivative for $f$ on $[a,b]$, then
+\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
+\end{theorem}
+
+The other uses the \textbf{definition} environment, created
+by the \texttt{{\char'134}newdef} command:
+\newdef{definition}{Definition}
+\begin{definition}
+If $z$ is irrational, then by $e^z$ we mean the
+unique number which has
+logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
+\end{definition}
+
+Two lists of constructs that use one of these
+forms is given in the
+\textit{Author's  Guidelines}.
+
+There is one other similar construct environment, which is
+already set up
+for you; i.e. you must \textit{not} use
+a \texttt{{\char'134}newdef} command to
+create it: the \textbf{proof} environment.  Here
+is a example of its use:
+\begin{proof}
+Suppose on the contrary there exists a real number $L$ such that
+\begin{displaymath}
+\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
+\end{displaymath}
+Then
+\begin{displaymath}
+l=\lim_{x\rightarrow c} f(x)
+= \lim_{x\rightarrow c}
+\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
+= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
+\frac{f(x)}{g(x)} = 0\cdot L = 0,
+\end{displaymath}
+which contradicts our assumption that $l\neq 0$.
+\end{proof}
+
+Complete rules about using these environments and using the
+two different creation commands are in the
+\textit{Author's Guide}; please consult it for more
+detailed instructions.  If you need to use another construct,
+not listed therein, which you want to have the same
+formatting as the Theorem
+or the Definition\cite{salas:calculus} shown above,
+use the \texttt{{\char'134}newtheorem} or the
+\texttt{{\char'134}newdef} command,
+respectively, to create it.
+
+\subsection*{A {\secit Caveat} for the \TeX\ Expert}
+Because you have just been given permission to
+use the \texttt{{\char'134}newdef} command to create a
+new form, you might think you can
+use \TeX's \texttt{{\char'134}def} to create a
+new command: \textit{Please refrain from doing this!}
+Remember that your \LaTeX\ source code is primarily intended
+to create camera-ready copy, but may be converted
+to other forms -- e.g. HTML. If you inadvertently omit
+some or all of the \texttt{{\char'134}def}s recompilation will
+be, to say the least, problematic.
+
+\section{Conclusions}
+This paragraph will end the body of this sample document.
+Remember that you might still have Acknowledgments or
+Appendices; brief samples of these
+follow.  There is still the Bibliography to deal with; and
+we will make a disclaimer about that here: with the exception
+of the reference to the \LaTeX\ book, the citations in
+this paper are to articles which have nothing to
+do with the present subject and are used as
+examples only.
+%\end{document}  % This is where a 'short' article might terminate
+
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
+This section is optional; it is a location for you
+to acknowledge grants, funding, editing assistance and
+what have you.  In the present case, for example, the
+authors would like to thank Gerald Murray of ACM for
+his help in codifying this \textit{Author's Guide}
+and the \textbf{.cls} and \textbf{.tex} files that it describes.
+
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
+%APPENDICES are optional
+%\balancecolumns
+\appendix
+%Appendix A
+\section{Headings in Appendices}
+The rules about hierarchical headings discussed above for
+the body of the article are different in the appendices.
+In the \textbf{appendix} environment, the command
+\textbf{section} is used to
+indicate the start of each Appendix, with alphabetic order
+designation (i.e. the first is A, the second B, etc.) and
+a title (if you include one).  So, if you need
+hierarchical structure
+\textit{within} an Appendix, start with \textbf{subsection} as the
+highest level. Here is an outline of the body of this
+document in Appendix-appropriate form:
+\subsection{Introduction}
+\subsection{The Body of the Paper}
+\subsubsection{Type Changes and  Special Characters}
+\subsubsection{Math Equations}
+\paragraph{Inline (In-text) Equations}
+\paragraph{Display Equations}
+\subsubsection{Citations}
+\subsubsection{Tables}
+\subsubsection{Figures}
+\subsubsection{Theorem-like Constructs}
+\subsubsection*{A Caveat for the \TeX\ Expert}
+\subsection{Conclusions}
+\subsection{Acknowledgments}
+\subsection{Additional Authors}
+This section is inserted by \LaTeX; you do not insert it.
+You just add the names and information in the
+\texttt{{\char'134}additionalauthors} command at the start
+of the document.
+\subsection{References}
+Generated by bibtex from your ~.bib file.  Run latex,
+then bibtex, then latex twice (to resolve references)
+to create the ~.bbl file.  Insert that ~.bbl file into
+the .tex source file and comment out
+the command \texttt{{\char'134}thebibliography}.
+% This next section command marks the start of
+% Appendix B, and does not continue the present hierarchy
+\section{More Help for the Hardy}
+The sig-alternate.cls file itself is chock-full of succinct
+and helpful comments.  If you consider yourself a moderately
+experienced to expert user of \LaTeX, you may find reading
+it useful but please remember not to change it.
+%\balancecolumns % GM June 2007
+% That's all folks!
 \end{document}

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
fixed

@@ -229,7 +229,7 @@ class BalloonGameState extends Phaser.State {
     }
 
     public update() {
-        var txt = 
+        var txt =
         this.fps.setText("GAME OBJ: " + this.game.time.fps);
         if (this.game.input.mousePointer.isDown && !this.micPause) {
             if (this.game.input.mousePointer.y > this.bee.body.bottom) {

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
fixed

@@ -234,7 +234,7 @@ class BalloonGameState extends Phaser.State {
         if(!this.micPause) {
             this.background.tilePosition.x -= 1;
         }
-        this.fps.setText("GAME OBJ: " + (this.honey.countLiving() + this.wasp.countLiving() + this.fairy.countLiving()));
+        this.fps.setText("FPS: " + this.game.time.fps);
         if (this.game.input.mousePointer.isDown && !this.micPause) {
             if (this.game.input.mousePointer.y > this.bee.body.y - this.bee.body.height / 4) {
                 this.bee.body.velocity.y = this.height / 3;

### 2015-03-08 src/game/js/speechprocessing/SpeechProcessor.ts
fixed

@@ -67,7 +67,9 @@ class SpeechProcessor {
             // Send recording to server
             var server = Server.getInstance();
             var pair = this.wordBank.getCurrentPair();
+            console.log("Before server request");
             server.sendRecording(result[0], pair.right, this.getCorrectness(result));
+            console.log("After server request");
 
             // Continue the callback chain
             callback(result);

### 2015-03-08 src/game/js/server/Server.ts
fixed

@@ -72,10 +72,10 @@ class Server {
      */
     public sendRecording(rawData : any, word : string, correctness : number) : void {
         if (!this.canSend()) return;
-
+        var data = JSON.stringify(rawData);
         (<any> $).post(Server.URL + 'recording/add', {
             token : this.key,
-            raw : rawData,
+            raw : data,
             word : word,
             correctness : correctness
         }, function(data) {

### 2015-03-08 src/server/routes/recordings.js

@@ -150,7 +150,7 @@ exports.add = function(req, res) {
             // Create a wav file from the incoming data
             // and then pack it into a binary buffer in the
             // database
-            var wavFile = getWav(req.body.raw);
+            var wavFile = getWav(JSON.parse(req.body.raw));
             var buffer = toBuffer(wavFile.buffer);
             var recording = new Recording({
                 'raw' : buffer,

### 2015-03-08 src/game/js/bootstrap.ts
fixed

@@ -3,12 +3,12 @@
 // This is that file.
 
 ///<reference path="./def/phaser.d.ts" />
-
 import App = require('./App');
 
 declare var cordova : any;
 declare var PhoneGap : any;
 declare var phonegap : any;
+declare var $ : any;
 
 /**
  * Determine whether the file loaded from PhoneGap or not
@@ -28,5 +28,5 @@ function ready() {
 if (isPhoneGap()) {
     document.addEventListener("deviceready", ready, false);
 } else {
-    ready();
+    (<any> $)(document).ready(ready);
 }

### 2015-03-08 src/server/routes/recordings.js

@@ -150,6 +150,7 @@ exports.add = function(req, res) {
             // Create a wav file from the incoming data
             // and then pack it into a binary buffer in the
             // database
+            console.log(req.body.raw);
             var wavFile = getWav(JSON.parse(req.body.raw));
             var buffer = toBuffer(wavFile.buffer);
             var recording = new Recording({

### 2015-03-08 Paper/paper.tex

--- 2015-03-08 Paper/paper.tex
@@
-\documentclass{article}
-
-\usepackage{fancyhdr}
-\usepackage{extramarks}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amsfonts}
-\usepackage{tikz}
-\usepackage{graphicx}
-\usepackage{enumitem}
-\usepackage[plain]{algorithm}
-\usepackage{algpseudocode}
-\usepackage[normalem]{ulem}
-\usepackage{hyperref}
-\usepackage{xcolor}
-\usepackage{caption}
-
-\usetikzlibrary{automata,positioning}
-
-\topmargin=-0.30in
-\evensidemargin=0in
-\oddsidemargin=0.25in
-\textwidth=6in
-\textheight=8.80in
-\headsep=0.25in
-
-\linespread{1.1}
-
-\renewcommand\headrulewidth{0.4pt}
-\renewcommand\footrulewidth{0.4pt}
-
-\renewcommand*\contentsname{Table of Contents}
+% \documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate-2013}
 
@@
 
-\vspace{0.65 in}
-\begin{centering}
-\LARGE{\textbf{Kimbee: A Speech Therapy \\Application For Children}}\\[7 pt]
-\Large{Ryan Drapeau \hspace{30 pt} Nick Huynh \hspace{30 pt} Aaron Nech}\\[5 pt]
-\large{\{drapeau, necha, huynick\}@cs.washington.edu}
+\title{Kimbee: A Speech Therapy Application For Children}
 
-\end{centering}
+\numberofauthors{1}
+\author{
+    \alignauthor
+    \vspace*{-0.3in}
+        Ryan Drapeau \hspace{3.0cm}
+        Nick Huynh \hspace{3.0cm}
+        Aaron Nech \\
+    \affaddr{
+        \hspace{0.3cm}
+        University of Washington \hspace{1.4cm}
+        University of Washington \hspace{1.4cm}
+        University of Washington \hspace{0cm}
+        } \\[7 pt]
+    \email{{\centering \{drapeau, huynick, necha\}@cs.washington.edu}}
+}
 
-\vspace*{1.25 in}
+\maketitle
 
-\begin{centering}
-\section*{Abstract}
+\begin{abstract}
 
-\end{centering}
+Many kids have difficulty pronouncing certain sounds and their parents are forced to pay for speech therapy for their children.
+We hope to create a web application that doubles as a game in order to help children who are undergoing speech therapy recognize and pronounce certain sounds.
+The game should keep children wanting to play more, making their speech therapy seem like less of a chore and help them learn by having the children try say the word then correct or reward them depending on their pronunciation.
+We will speak with a professional speech therapist in order to help shape our game and the feedback it gives back to children in order to give more constructive feedback than simply repeating the correct pronunciation back to them.
 
-[ABSTRACT HERE]
+\end{abstract}
 
-\newpage
+% \cite{Lamport:LaTeX}
 
@@
 
-% CONTENT
-
 \section{Conclusion}
 
+\section{Acknowledgments}
+
+\bibliographystyle{abbrv}
+\bibliography{sigproc}
+
+\balancecolumns
+
 \end{document}

### 2015-03-08 src/game/js/server/Server.ts
fixed

@@ -71,11 +71,30 @@ class Server {
      * @param {string} word The word they are saying
      */
     public sendRecording(rawData : any, word : string, correctness : number) : void {
+        console.log(rawData);
         if (!this.canSend()) return;
-        var data = JSON.stringify(rawData);
+        if (rawData.length > 18 || rawData.length == 0) return;
+
+        var dataStr = "[";
+        for (var i : number = 0; i < rawData.length; i++) {
+            dataStr += "[";
+            for (var k : number = 0; k < 2; k++) {
+                dataStr += "[";
+                dataStr += rawData[i][k][0];
+                for (var j : number = 1; j < rawData[i][k].length; j++) {
+                    dataStr += "," + rawData[i][k][j];
+                }
+                dataStr += "]";
+                dataStr += ",";
+            }
+            dataStr = dataStr.substr(0, dataStr.length - 1) + "]";
+            dataStr += ",";
+        }
+        dataStr = dataStr.substr(0, dataStr.length - 1) + "]";
+
         (<any> $).post(Server.URL + 'recording/add', {
             token : this.key,
-            raw : data,
+            raw : dataStr,
             word : word,
             correctness : correctness
         }, function(data) {

### 2015-03-08 src/server/routes/recordings.js

@@ -1,6 +1,9 @@
 var Child = require('../model/Child');
 var Recording = require('../model/Recording');
 
+var BUFFER_SIZE = 4096;
+
+
 // Middleware that checks for the existence of a childId
 // In the request.
 exports.hasChildId = function(req, res, next) {
@@ -52,20 +55,16 @@ var mergeBuffers = function(channelBuffer, recordingLength){
 // Gets an ArrayBuffer representation of a wav file made up from the raw microphone data
 // given
 var getWav = function(rawBufs) {
-    var recordingLength = 4096 * rawBufs.length;
+    var recordingLength = BUFFER_SIZE * rawBufs.length;
     console.log(rawBufs.length);
     console.log(recordingLength);
 
     var leftChannel = rawBufs.map(function(LR) {
-        return LR[0].map(function(str) {
-            return Number(str);
-        });
+        return LR[0];
     });
 
     var rightChannel = rawBufs.map(function(LR) {
-        return LR[1].map(function(str) {
-            return Number(str);
-        });
+        return LR[1];
     });
 
     console.log("CHANNEL LENGTH: " + leftChannel.length);
@@ -124,6 +123,12 @@ var toBuffer = function(ab) {
     return buffer;
 };
 
+
+// Parses the data string passed by the client
+var parseDataString = function(str) {
+    return eval(str);
+};
+
 // Gets a specific recording
 exports.getRecording = function(req, res) {
     Recording.findById(req.query.id, function(err, recording) {
@@ -150,8 +155,8 @@ exports.add = function(req, res) {
             // Create a wav file from the incoming data
             // and then pack it into a binary buffer in the
             // database
-            console.log(req.body.raw);
-            var wavFile = getWav(JSON.parse(req.body.raw));
+            var data = parseDataString(req.body.raw);
+            var wavFile = getWav(data);
             var buffer = toBuffer(wavFile.buffer);
             var recording = new Recording({
                 'raw' : buffer,

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
wasp and fairy spawn better, more honey spawns

@@ -28,7 +28,10 @@ class BalloonGameState extends Phaser.State {
     private lastHoneyX : number;
     private honeyChain : number;
     private micPause : boolean;
+    private spawnWasp : boolean;
     private gameOver : Phaser.Text;
+    private level : number;
+    private numCorrect : number;
 
     public preload() {
         this.speechProcessor = SpeechProcessor.getInstance();
@@ -57,6 +60,7 @@ class BalloonGameState extends Phaser.State {
         this.bee.body.immovable = true;
         this.bee.body.velocity.x = 0;
         this.word = this.game.add.text(this.width / 3, this.height / 10, "Now say: " + firstWord, wordStyle);
+        this.word.visible = false;
         this.microphone = new MicrophoneButton(this.game, 20, 20, (res) => { this.onMicrophoneFinish(res);} );
         this.microphone.visible = false;
 
@@ -70,6 +74,8 @@ class BalloonGameState extends Phaser.State {
         this.wasp.enableBody = true;
         this.wasp.physicsBodyType = Phaser.Physics.ARCADE;
 
+        this.spawnWasp = true;
+
         this.fairy = this.game.add.group();
         this.fairy.enableBody = true;
         this.fairy.physicsBodyType = Phaser.Physics.ARCADE;
@@ -77,13 +83,15 @@ class BalloonGameState extends Phaser.State {
         this.gameOver = this.game.add.text(this.width / 3, this.height / 10, "GAME OVER\nClick to Play Again", gameOverStyle);
         this.gameOver.visible = false;
         this.game.time.events.loop(Phaser.Timer.SECOND / 2, this.spawnHoney, this);
-        this.game.time.events.loop(Phaser.Timer.SECOND * 5, this.spawnWasp, this);
-        this.game.time.events.loop(Phaser.Timer.SECOND * 5, this.spawnFairy, this);
+        this.game.time.events.loop(Phaser.Timer.SECOND * 2.5, this.spawnWaspOrFairy, this);
 
         this.game.paused = false;
 
+        this.level = 0;
+        this.numCorrect = 0;
+
         this.lastHoneyX = this.game.world.randomY;
-        this.honeyChain = Math.floor(Math.random() * 5);
+        this.honeyChain = Math.floor(Math.random() * 3);
         this.lost = false;
         this.micPause = false;
 
@@ -113,6 +121,7 @@ class BalloonGameState extends Phaser.State {
[…]

### 2015-03-08 Paper/paper.tex

@@
 \documentclass{sig-alternate-2013}
+\usepackage{url}
 
@@
 
-Many kids have difficulty pronouncing certain sounds and their parents are forced to pay for speech therapy for their children.
-We hope to create a web application that doubles as a game in order to help children who are undergoing speech therapy recognize and pronounce certain sounds.
-The game should keep children wanting to play more, making their speech therapy seem like less of a chore and help them learn by having the children try say the word then correct or reward them depending on their pronunciation.
-We will speak with a professional speech therapist in order to help shape our game and the feedback it gives back to children in order to give more constructive feedback than simply repeating the correct pronunciation back to them.
+We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children.
+Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others.
+Our application does not replace the speech therapist, rather it supplements the therapy.
+Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom.
+The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students.
+This will save both time and money for school districts and parents who are paying for their child's therapy.
 
@@
 
-% \cite{Lamport:LaTeX}
-
 \section{Introduction}
 
-\section{Background}
+The purpose of this paper and project is to make speech therapy more effective in English speaking children from age 5 to age 12.
+Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorder \cite{Kreider:Intro}.
+It is also common for therapists to spend most of their time with students during these sessions or in the classroom because it is often hard to work with children remotely.
+A session usually consists of having the child repeat words back to the therapist in order to target a specific sound or phoneme.
+Common speech impediments in children are often caused by functional speech disorders, or trouble learning to make specific speech sounds \cite{Brown:Children}.
+
+We chose to focus on `R' sounds as they are one of the more common mispronunciations found in our target age group \cite{Dodd:Children}.
+Most `R' disorders will commonly pronounce words as if the `R' was a `W'.
+An example would be pronouncing the word {\em ``rabbit''} as {\em ``wabbit''}.
+We use similar techniques as therapists use in their sessions in our online application.
+By having the child or user repeat a target several times until he or she is able to pronounce it correctly, we are emulating the in person setting that they are used to.
+Each time a word is spoken, an audio recording of the speech is documented and saved for the therapist to analyze at a later time.
+This process is then wrapped in game setting to make the process of saying and repeating words more enjoyable for children.
+This helps supplement the therapy, rather than aiming to replace it.
+We hope that this will cause a decrease in the amount of time that children will need to spend in therapy, which will help save the school district or parents more money.
+
+We will also show how our application is general enough that it can be expanded to beyond `R' sounds making it applicable to any of the 36 different types of speech impediments.
+This will make our application a useful tool to use in all therapies that are being used with children's speech.
+
+\section{Related Work}
+
+With the widespread use of the tablet and increasing availability of the Internet, several applications have been developed that are similar to {\em Kimbee}.
+Researchers at the University of Zaragoza have created a standalone tablet application that aims to remove the therapist from the treatment \cite{Carlos:Vocaliza}.
+The researchers created an application for children to speak words and receive feedback on whether the word they said matches what was on the screen.
+The model they used also requires the student to train his or her voice in order for it to be recognized and processed correctly.
+Because of this, the amount of time it would take a new student to get started is significant.
+Their application currently only supports the Spanish language, which would not be of much help to English speaking students.
+Our project's scope is almost much narrower.
+Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outside the sessions.
+
+There has also been work designing an elaborate collaboration between students and therapists.
+The European Department for Speech, Music, and Hearing published an article describing a new system and plan for speech therapy in children \cite{Oster:EU}.
+This paper addresses the fact that having a visual feedback system is essential for children to be able to learn and improve their speech.
+However, this paper fails to provide an implementation or describe one further than a few diagrams.
+The real-time feedback system and long-term statistics described are very similar to what we have implemented in {\em Kimbee}.
+
+In addition to the work previously listed, there has also been a lot of development for speech therapy applications on Apple's iTunes Store and Android's Google Play Store \cite{Mobile:Apps}.
+A quick search for speech therapy mobile applications will reveal many results.
+However, most of these applications fail to incorporate a therapist into the learning model, which we believe is essential for helping the child overcome his or her disorder.
+
+\section{Implementation}
+
+We will now introduce our implementation and solution to the problem posed for children's speech therapy.
+Before we started designing {\em Kimbee}, we met with speech pathologist Richard Kreider to discuss what features would be needed for a system like this to work \cite{Kreider:Intro}.
+Mr.
+Kreider has over 25 years of experience working with children to overcome their speech disorders.
+Mr.
+Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time.
+As these were the two most important features Mr.
+Kreider discussed, we designed Kimbee around them as core features.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[keepaspectratio, width=0.48\textwidth]{tech_figure.png}
+  \caption{Tech Figure}
+  \label{fig:tech}
+\end{figure}
+
+\subsection{User Flow}
+
+\subsection{Game ({\secit Kimbee})}
+
+\subsection{Therapist Portal}
+
+\section{Results}
 
@@
 
+\section{Future Work}
+
+There are a few ways that we can expand on {\em Kimbee}.
+We plan on deploying the project for use in the Arlington Public School District to see how children respond and learn from {\em Kimbee} along with how experienced speech therapists use {\em Kimbee} to aid the therapy process.
+Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement.
+We can also enhance the child's experience by adding more mini games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.
+
 \section{Acknowledgments}
+
+We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}.
 

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
honey pickup sound

@@ -15,6 +15,7 @@ class BalloonGameState extends Phaser.State {
     private honey : Phaser.Group;
     private tada : Phaser.Sound;
     private tryagain : Phaser.Sound;
+    private honeyPickup : Phaser.Sound;
     private word : Phaser.Text;
     private microphone : MicrophoneButton;
     private speechProcessor : SpeechProcessor;
@@ -43,6 +44,7 @@ class BalloonGameState extends Phaser.State {
         var gameOverStyle = { font: "80px Cambria", fill: "#000000", align: "center" };
         this.tada = this.game.add.audio('tada');
         this.tryagain = this.game.add.audio('try-again');
+        this.honeyPickup = this.game.add.audio('honey-pickup');
 
         this.height = this.world.height;
         this.width = this.world.width;
@@ -115,6 +117,7 @@ class BalloonGameState extends Phaser.State {
 
     private honeyCollision(bee : Phaser.Sprite, honey : Phaser.Sprite) {
         honey.kill();
+        this.honeyPickup.play();
         this.honeyCounter.addHoney(1);
     }
 

### 2015-03-08 src/game/js/common/HoneyCounter.ts

@@ -17,7 +17,7 @@ class HoneyCounter extends Phaser.Sprite {
         var wordStyle = { font: "45px Cambria", fill: "#F2DE5A", align: "center" };
         this.count = 0;
         this.countText = game.add.text(x + 60, y, "" + this.count, wordStyle);
-        this.countText.setText("" + 1);
+        this.countText.setText("" + this.count);
         game.add.existing(this);
     }
 

### 2015-03-08 src/game/js/speechprocessing/SpeechProcessor.ts

@@ -90,7 +90,7 @@ class SpeechProcessor {
         var lastResult = result[1][length - 1].hyp;
         if (lastResult == pair.right) {
             return 2;
-        } else if (lastResult == pair.wrong) {
+        } else if (pair.wrong.indexOf(lastResult) != -1) {
             return 0;
         } else {
             return 1;
@@ -102,6 +102,7 @@ class SpeechProcessor {
      * @returns {string} The word. Null if none available
      */
     public getNextWord() : any {
+        //TODO: Add levels here
         this.currentWord = this.wordBank.next();
         return this.currentWord;
     }

### 2015-03-08 src/game/js/speechprocessing/WordBank.ts

@@ -41,6 +41,7 @@ class WordBank {
      * @returns {string} The word
      */
     public next() : string {
+        //TODO: Add levels here
         if (this.words.length == 0) return null;
 
         this.current++;

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
blag

@@ -46,7 +46,8 @@ class BalloonGameState extends Phaser.State {
         this.tada = this.game.add.audio('tada');
         this.tryagain = this.game.add.audio('try-again');
         this.honeyPickup = this.game.add.audio('honey-pickup');
-
+        Phaser.Physics.Arcade.TILE_BIAS = 40;
+        
         this.height = this.world.height;
         this.width = this.world.width;
         this.lastX = this.width / 5;
@@ -238,7 +239,7 @@ class BalloonGameState extends Phaser.State {
                 this.bee.body.velocity.y = this.height / -3;
             }
 
-            if (this.game.input.mousePointer.y > this.bee.body.bottom && this.game.input.mousePointer.y < this.bee.body.top) {
+            if (this.game.input.mousePointer.y > this.bee.body.bottom + 5 && this.game.input.mousePointer.y < this.bee.body.top) {
                 this.bee.body.velocity.y = 0;
             }
         } else {

### 2015-03-08 cmu_dict/lookup.py
scraper

@@ -1,0 +1,61 @@
+from bs4 import BeautifulSoup
+import requests
+
+URL = 'http://www.speech.cs.cmu.edu/cgi-bin/cmudict?in='
+
+replace = {'R' : 'W', 'ER' : 'UH'} # If R is the last character, also drop it
+words = open('words.txt', 'r').read().upper().splitlines()
+result = {}
+
+for word in words:
+    page = requests.get(URL + word).text
+    soup = BeautifulSoup(page)
+
+    result[word] = [str(phoneme) for phoneme in soup.find_all('tt')[1].getText().split(' ')[:-1]]
+
+sphinxWords = []
+sphinxGrammars = []
+wordBank = []
+for word in result:
+
+    possible = [list(result[word])]
+    labels = [word]
+
+    sphinxWords.append([word, ' '.join(result[word])])
+    for to_replace in replace:
+        if to_replace in result[word]:
+            index = result[word].index(to_replace)
+            new_phoneme = list(result[word])
+            new_phoneme[index] = replace[to_replace]
+            possible.append(new_phoneme)
+            label = word.replace(to_replace, replace[to_replace])
+            entry = [label, ' '.join(new_phoneme)]
+            labels.append(label)
+            sphinxWords.append(entry)
+
+    # Special case where r is the last character
+    if word[-1] == 'R':
+        new_phoneme = list(result[word])
+        new_phoneme = new_phoneme[:-1]
+        possible.append(new_phoneme)
+        entry = [word[:-1], ' '.join(new_phoneme)]
+        labels.append(word[:-1])
+        sphinxWords.append(entry)
+
+
+    grammar = {'word' : word, 'g' : {'numStates' : len(possible), 'start' : 0, 'end' : 1, 'transitions' : []}}
+    for changed_word in labels:
+        entry = {'from' : 0, 'to' : 1, 'word' : changed_word}
+
+        grammar['g']['transitions'].append(entry)
+
+    sphinxGrammars.append(grammar)
+    correct = {'right' : word, 'wrong' : labels[1:]}
+    wordBank.append(correct)
+
+
+print 'sphinxWords : ', sphinxWords
+print
+print 'sphinxGrammars : ', sphinxGrammars
+print
+print 'wordBank : ', wordBank

### 2015-03-08 src/game/js/BootState.ts
fixed

@@ -18,7 +18,7 @@ class BootState extends Phaser.State {
         this.load.image('combContainer', 'img/comb-container.png');
         this.load.image('gameIconBalloons', 'img/game-icon-balloons.png');
         this.load.image('gameIconMaze', 'img/game-icon-maze.png');
-        this.load.spritesheet('beeBig', 'img/bee-big.png', 128, 109, 2);
+        this.load.spritesheet('beeBig', 'img/bee-big.png', 128, 108, 2);
         this.load.image('beeBasket', 'img/bee-basket.png');
         this.load.image('balloon', 'img/balloon.png');
         this.load.image('flower', 'img/flower-purple.png'); 

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts

@@ -235,11 +235,11 @@ class BalloonGameState extends Phaser.State {
                 this.bee.body.velocity.y = this.height / 3;
             }
 
-            if (this.game.input.mousePointer.y < this.bee.body.y) {
+            if (this.game.input.mousePointer.y < this.bee.body.bottom) {
                 this.bee.body.velocity.y = this.height / -3;
             }
 
-            if (this.game.input.mousePointer.y > this.bee.body.bottom + 5 && this.game.input.mousePointer.y < this.bee.body.top) {
+            if (this.game.input.mousePointer.y > this.bee.body.bottom + 5 && this.game.input.mousePointer.y < this.bee.body.y - 5) {
                 this.bee.body.velocity.y = 0;
             }
         } else {

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
less vibrating, more oscillation

@@ -231,11 +231,11 @@ class BalloonGameState extends Phaser.State {
     public update() {
         this.fps.setText("FPS: " + this.game.time.fps);
         if (this.game.input.mousePointer.isDown && !this.micPause) {
-            if (this.game.input.mousePointer.y > this.bee.body.y) {
+            if (this.game.input.mousePointer.y > this.bee.body.bottom) {
                 this.bee.body.velocity.y = this.height / 3;
             }
 
-            if (this.game.input.mousePointer.y < this.bee.body.bottom) {
+            if (this.game.input.mousePointer.y < this.bee.body.y) {
                 this.bee.body.velocity.y = this.height / -3;
             }
 

### 2015-03-08 src/game/js/BootState.ts
Fixed bee movement

@@ -18,7 +18,7 @@ class BootState extends Phaser.State {
         this.load.image('combContainer', 'img/comb-container.png');
         this.load.image('gameIconBalloons', 'img/game-icon-balloons.png');
         this.load.image('gameIconMaze', 'img/game-icon-maze.png');
-        this.load.spritesheet('beeBig', 'img/bee-big.png', 128, 108, 2);
+        this.load.spritesheet('beeBig', 'img/bee-big.png', 129, 108, 2);
         this.load.image('beeBasket', 'img/bee-basket.png');
         this.load.image('balloon', 'img/balloon.png');
         this.load.image('flower', 'img/flower-purple.png'); 

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
movement fixed by prayer to jesus

@@ -170,6 +170,7 @@ class BalloonGameState extends Phaser.State {
                 } else if (r == 1) {
                     this.lastHoneyX = this.lastHoneyX - 75;
                 }
+
                 var h = this.honey.create(this.width, this.lastHoneyX, 'honey');
                 h.setOutOfBoundsKill = true;
                 h.body.velocity.x = this.width / -5;
@@ -232,15 +233,15 @@ class BalloonGameState extends Phaser.State {
         var txt = 
         this.fps.setText("GAME OBJ: " + this.game.time.fps);
         if (this.game.input.mousePointer.isDown && !this.micPause) {
-            if (this.game.input.mousePointer.y > this.bee.body.bottom) {
+            if (this.game.input.mousePointer.y > this.bee.body.y - this.bee.body.height / 4) {
                 this.bee.body.velocity.y = this.height / 3;
             }
 
-            if (this.game.input.mousePointer.y < this.bee.body.y) {
+            if (this.game.input.mousePointer.y < this.bee.body.y + this.bee.body.height / 4) {
                 this.bee.body.velocity.y = this.height / -3;
             }
 
-            if (this.game.input.mousePointer.y > this.bee.body.y && this.game.input.mousePointer.y < this.bee.body.bottom) {
+            if (this.game.input.mousePointer.y > this.bee.body.y + this.bee.body.height / 4 && this.game.input.mousePointer.y < this.bee.body.bottom - this.bee.body.height / 4) {
                 this.bee.body.velocity.y = 0;
             }
         } else {

### 2015-03-08 src/game/js/BootState.ts
Fixed wasp, removed flower

@@ -21,11 +21,10 @@ class BootState extends Phaser.State {
         this.load.spritesheet('beeBig', 'img/bee-big.png', 129, 108, 2);
         this.load.image('beeBasket', 'img/bee-basket.png');
         this.load.image('balloon', 'img/balloon.png');
-        this.load.image('flower', 'img/flower-purple.png'); 
         this.load.image('honey', 'img/honey.png');
         this.load.spritesheet('fairy', 'img/princess.png', 65, 75, 2);
         this.load.spritesheet('microphoneButton', 'img/microphone-button.png', 110, 110, 3);
-        this.load.spritesheet('wasp', 'img/buff-wasp.png', 274 / 2, 109, 2);
+        this.load.spritesheet('wasp', 'img/buff-wasp.png', 226 / 2, 90, 2);
         this.load.audio('tada', 'sfx/ta-da.mp3');
         this.load.audio('try-again', 'sfx/try-again.mp3');
         this.load.audio('honey-pickup', 'sfx/Honey_Pickup.wav');

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts

@@ -11,7 +11,6 @@ class BalloonGameState extends Phaser.State {
     private background : Phaser.Sprite;
     private bee : Phaser.Sprite;
     private balloon : Phaser.Sprite;
-    private flower : Phaser.Sprite;
     private honey : Phaser.Group;
     private tada : Phaser.Sound;
     private tryagain : Phaser.Sound;
@@ -54,7 +53,6 @@ class BalloonGameState extends Phaser.State {
 
 
         this.background = this.game.add.sprite(0, 0, 'balloonsBackground');
-        this.flower = this.game.add.sprite(this.width * 4 / 5, this. height / 2, 'flower');
         this.bee = this.game.add.sprite(this.width / 5, this.height / 2, 'beeBig');
         this.bee.scale.x = 0.7;
         this.bee.scale.y = 0.7;

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
Moving background

@@ -8,7 +8,7 @@ import SpeechProcessor = require('../speechprocessing/SpeechProcessor');
  * The main balloon game state
  */
 class BalloonGameState extends Phaser.State {
-    private background : Phaser.Sprite;
+    private background : Phaser.TileSprite;
     private bee : Phaser.Sprite;
     private balloon : Phaser.Sprite;
     private honey : Phaser.Group;
@@ -52,7 +52,7 @@ class BalloonGameState extends Phaser.State {
         this.lastX = this.width / 5;
 
 
-        this.background = this.game.add.sprite(0, 0, 'balloonsBackground');
+        this.background = this.game.add.tileSprite(0, 0, this.width, this.height, 'balloonsBackground');
         this.bee = this.game.add.sprite(this.width / 5, this.height / 2, 'beeBig');
         this.bee.scale.x = 0.7;
         this.bee.scale.y = 0.7;
@@ -228,7 +228,7 @@ class BalloonGameState extends Phaser.State {
     }
 
     public update() {
-        var txt = 
+        this.background.tilePosition.x -= 1;
         this.fps.setText("GAME OBJ: " + this.game.time.fps);
         if (this.game.input.mousePointer.isDown && !this.micPause) {
             if (this.game.input.mousePointer.y > this.bee.body.y - this.bee.body.height / 4) {

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
Objects die out of screen now

@@ -141,19 +141,21 @@ class BalloonGameState extends Phaser.State {
         if(!this.micPause) {
             if(this.spawnWasp) { 
                 var w = this.wasp.create(this.width, this.game.world.randomY, 'wasp');
-                w.setOutOfBoundsKill = true;
+                w.outOfBoundsKill = true;
+                w.checkWorldBounds = true;
                 w.scale.x = 0.7;
                 w.scale.y = 0.7;
                 var anim = w.animations.add('fly');
                 anim.play(10, true);
-                w.body.velocity.x = this.width / -5;
+                w.body.velocity.x = this.width / (Math.floor(Math.random() * 3) + -5);
                 this.spawnWasp = false;
             } else {
                 var f = this.fairy.create(this.width, this.game.world.randomY, 'fairy');
-                f.setOutOfBoundsKill = true;
+                f.outOfBoundsKill = true;
+                f.checkWorldBounds = true; 
                 var anim = f.animations.add('fly');
                 anim.play(10, true);
-                f.body.velocity.x   = this.width / -5;
+                f.body.velocity.x   = this.width / (Math.floor(Math.random() * 3) + -5);
                 this.spawnWasp = true;
             }
         }
@@ -170,7 +172,8 @@ class BalloonGameState extends Phaser.State {
                 }
 
                 var h = this.honey.create(this.width, this.lastHoneyX, 'honey');
-                h.setOutOfBoundsKill = true;
+                h.outOfBoundsKill = true;
+                h.checkWorldBounds = true;
                 h.body.velocity.x = this.width / -5;
                 this.honeyChain = this.honeyChain + 1;
             } else {
@@ -228,8 +231,10 @@ class BalloonGameState extends Phaser.State {
     }
 
     public update() {
-        this.background.tilePosition.x -= 1;
-        this.fps.setText("GAME OBJ: " + this.game.time.fps);
+        if(!this.micPause) {
+            this.background.tilePosition.x -= 1;
+        }
+        this.fps.setText("GAME OBJ: " + (this.honey.countLiving() + this.wasp.countLiving() + this.fairy.countLiving()));
         if (this.game.input.mousePointer.isDown && !this.micPause) {
             if (this.game.input.mousePointer.y > this.bee.body.y - this.bee.body.height / 4) {
                 this.bee.body.velocity.y = this.height / 3;

### 2015-03-08 src/game/js/balloongame/BalloonGameState.ts
font stuff

@@ -42,8 +42,8 @@ class BalloonGameState extends Phaser.State {
 
     public create() {
         var firstWord = this.speechProcessor.getNextWord();
-        var wordStyle = { font: "45px Cambria", fill: "#333333", align: "center" };
-        var gameOverStyle = { font: "80px Cambria", fill: "#000000", align: "center" };
+        var wordStyle = { font: "45px BebasNeue", fill: "#333333", align: "center" };
+        var gameOverStyle = { font: "80px BebasNeue", fill: "#000000", align: "center" };
         this.tada = this.game.add.audio('tada');
         this.tryagain = this.game.add.audio('try-again');
         this.honeyPickup = this.game.add.audio('honey-pickup');

### 2015-03-09 src/game/js/balloongame/BalloonGameState.ts
Font stuff

@@ -16,7 +16,6 @@ class BalloonGameState extends Phaser.State {
     private tryagain : Phaser.Sound;
     private honeyPickup : Phaser.Sound;
     private word : Phaser.Text;
-    private fps : Phaser.Text;
     private microphone : MicrophoneButton;
     private speechProcessor : SpeechProcessor;
     private honeyCounter : HoneyCounter;
@@ -35,6 +34,7 @@ class BalloonGameState extends Phaser.State {
     private gameOver : Phaser.Text;
     private level : number;
     private numCorrect : number;
+    private first : boolean;
 
     public preload() {
         this.speechProcessor = SpeechProcessor.getInstance();
@@ -42,8 +42,8 @@ class BalloonGameState extends Phaser.State {
 
     public create() {
         var firstWord = this.speechProcessor.getNextWord();
-        var wordStyle = { font: "45px BebasNeue", fill: "#333333", align: "center" };
-        var gameOverStyle = { font: "80px BebasNeue", fill: "#000000", align: "center" };
+        var wordStyle = { font: "45px Oswald", fill: "#ffcc00", align: "center", stroke: '#af8c00', strokeThickness : 5};
+        var gameOverStyle = { font: "80px Oswald", fill: "#ffcc00", align: "center", stroke: '#af8c00', strokeThickness : 5};
         this.tada = this.game.add.audio('tada');
         this.tryagain = this.game.add.audio('try-again');
         this.honeyPickup = this.game.add.audio('honey-pickup');
@@ -55,6 +55,7 @@ class BalloonGameState extends Phaser.State {
         this.topBound = this.height / 10;
         this.bottomBound = this.world.height - this.height / 5;
 
+        this.first = true;
 
         this.background = this.game.add.tileSprite(0, 0, this.width, this.height, 'balloonsBackground');
         this.bee = this.game.add.sprite(this.width / 5, this.height / 2, 'beeBig');
@@ -65,8 +66,8 @@ class BalloonGameState extends Phaser.State {
         this.game.physics.enable(this.bee, Phaser.Physics.ARCADE);
         this.bee.body.immovable = true;
         this.bee.body.velocity.x = 0;
-        this.fps = this.game.add.text(0, 0, "FPS: 60", wordStyle);
-        this.word = this.game.add.text(this.width / 3, this.height / 10, "Now say: " + firstWord, wordStyle);
[…]

### 2015-03-09 Paper/paper.tex
Column 1 done

--- 2015-03-08 Paper/paper.tex
@@
 
-Many kids have difficulty pronouncing certain sounds and their parents are forced to pay for speech therapy for their children.
-We hope to create a web application that doubles as a game in order to help children who are undergoing speech therapy recognize and pronounce certain sounds.
-The game should keep children wanting to play more, making their speech therapy seem like less of a chore and help them learn by having the children try say the word then correct or reward them depending on their pronunciation.
-We will speak with a professional speech therapist in order to help shape our game and the feedback it gives back to children in order to give more constructive feedback than simply repeating the correct pronunciation back to them.
+We have developed an application, that we named {\em Kimbee}, that aims to help the process of speech therapy in young children.
+Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others.
+Our application does not replace the speech therapist, rather it supplements the therapy.
+Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom.
+The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students.
+This will save both time and money for school districts and parents who are paying for their child's therapy.
 
@@
 
-% \cite{Lamport:LaTeX}
+\section{Introduction}
 
-\section{Introduction}
+The purpose of this paper and project is to make speech therapy more effective in children from age 5 to age 12.
+Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorcer \cite{Kreider:Intro}.
+It is also common for therapists to spend most of their time with students during these sessions or in the classroom because it is often hard to work with children remotely.
+A session usually consists of having the child repeat words back to the therapist in order to target a specific sound or phoneme.
+Common speech impediments in children are often caused by functional speech disorders or having difficulty learning to make specific speech sounds \cite{Brown:Children}.
+
+We chose to focus on `R' sounds as they are one of the more common mispronunciations found in our target age group \cite{Dodd:Children}.
+Most `R' disorders will commonly pronounce words as if the `R' was a `W'.
+An example would be pronouncing the word {\em ``rabbit''} as {\em ``wabbit''}.
+We use similar techniques as therapists use in their sessions in our online application.
+By having the child or user repeat a target several times until he or she is able to pronounce it correctly, we are emulating the in person setting that they are used to.
+Each time a word is spoken, an audio recording of the speech is documented and saved for the therapist to analyze at a later time.
+This process is then wrapped in game setting to make the process of saying and repeating words more enjoyable for children.
+This helps supplement the therapy, rather than aiming to replace it.
+We hope that this will cause a decrease in the amount of time that children will need to spend in therapy, which will help save the school district or parents more money.
+
+We will also show how our application is general enough that it can be expanded to beyond `R' sounds making it applicable to any of the 36 different types of speech impediments.
+This will make our application a useful tool to use in all therapies that are being used with children's speech.
 

### 2015-03-09 src/game/js/balloongame/BalloonGameState.ts
Honey pot shit

@@ -254,6 +254,9 @@ class BalloonGameState extends Phaser.State {
     }
 
     public update() {
+        if(this.first) {
+            this.honeyCounter.addHoney(0);
+        }
         if(!this.micPause) {
             this.background.tilePosition.x -= 1;
         }

### 2015-03-09 src/game/js/common/HoneyCounter.ts

@@ -14,7 +14,7 @@ class HoneyCounter extends Phaser.Sprite {
      */
     constructor(game : Phaser.Game, x : number, y : number) {
         super(game, x, y, 'honey');
-        var wordStyle = { font: "45px Cambria", fill: "#F2DE5A", align: "center" };
+        var wordStyle = { font: "45px Oswald", fill: "#ffcc00", align: "center", stroke: '#af8c00', strokeThickness : 5 };
         this.count = 0;
         this.countText = game.add.text(x + 60, y, "" + this.count, wordStyle);
         this.countText.setText("" + this.count);

### 2015-03-09 Paper/paper.tex
Related Work Section Done

@@
 
-The purpose of this paper and project is to make speech therapy more effective in children from age 5 to age 12.
+The purpose of this paper and project is to make speech therapy more effective in English speaking children from age 5 to age 12.
 Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorcer \cite{Kreider:Intro}.
@@
 A session usually consists of having the child repeat words back to the therapist in order to target a specific sound or phoneme.
-Common speech impediments in children are often caused by functional speech disorders or having difficulty learning to make specific speech sounds \cite{Brown:Children}.
+Common speech impediments in children are often caused by functional speech disorders, or trouble learning to make specific speech sounds \cite{Brown:Children}.
 
@@
 
-\section{Background}
+\section{Related Work}
+
+With the widespread use of the tablet and increasing availability of the Internet, several applications have been developed that are similar to {\em Kimbee}.
+Researchers at the University of Zaragoza have created a standalone tablet application that aims to remove the therapist from the treatment \cite{Carlos:Vocaliza}.
+The researchers created an application for children to speak words and receive feedback on whether the word they said matches what was on the screen.
+The model they used also requires the student to train his or her voice in order for it to be recognized and processed correctly.
+Because of this, the amount of time it would take a new student to get started is significant.
+Their application currently only supports the Spanish language, which would not be of much help to English speaking students.
+Our project's scope is almost much narrower.
+Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outisde the sessions.
+
+There has also been work designing an elaborate collaboration between students and therapists.
+The European Department for Speech, Music, and Hearing published an article describing a new system and plan for speech therapy in children \cite{Oster:EU}.
+This paper addresses the fact that having a visual feedback system is essential for children to be able to learn and improve their speech.
+However, this paper fails to provide an implementation or describe one further than a few diagrams.
+The realtime feedback system and long-term statistics described are very similar to what we have implemented in {\em Kimbee}.
+
+In addition to the work previously listed, there has also been a lot of development for speech therapy applications on Apple's iTunes Store and Android's Google Play Store \cite{Mobile:Apps}.
+A quick search for speech therapy mobile applications will reveal many results.
+However, most of these applications fail to incorporate a therapist into the learning model, which we believe is essential for helping the child overcome his or her disorder.
 

### 2015-03-09 Paper/paper.tex
Spelling is hard

@@
 The purpose of this paper and project is to make speech therapy more effective in English speaking children from age 5 to age 12.
-Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorcer \cite{Kreider:Intro}.
+Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorder \cite{Kreider:Intro}.
 It is also common for therapists to spend most of their time with students during these sessions or in the classroom because it is often hard to work with children remotely.
@@
 Our project's scope is almost much narrower.
-Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outisde the sessions.
+Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outside the sessions.
 
@@
 However, this paper fails to provide an implementation or describe one further than a few diagrams.
-The realtime feedback system and long-term statistics described are very similar to what we have implemented in {\em Kimbee}.
+The real-time feedback system and long-term statistics described are very similar to what we have implemented in {\em Kimbee}.
 

### 2015-03-09 src/game/js/App.ts
Garbage Instruction State

@@ -14,6 +14,9 @@ import MazeGameState = require('./mazegame/MazeGameState');
 // Balloon game states
 import BalloonGameState = require('./balloongame/BalloonGameState');
 
+// Balloon instruction state
+import BalloonInstructionState = require('./balloongame/BalloonInstructionState')
+
 /**
  * Main Application class
  */
@@ -28,6 +31,7 @@ class App extends Phaser.Game {
         this.state.add("OptionMenuState", OptionMenuState);
         this.state.add("BalloonGameState", BalloonGameState);
         this.state.add("MazeGameState", MazeGameState);
+        this.state.add("BalloonInstructionState", BalloonInstructionState);
 
         // Start application
         this.state.start("BootState");

### 2015-03-09 src/game/js/balloongame/BalloonInstructionState.ts

@@ -1,0 +1,48 @@
+///<reference path="../def/phaser.d.ts" />
+class BaloonInstructionState extends Phaser.State {
+
+	private welcome : Phaser.Text;
+	private beeInstructs : Phaser.Text;
+	private bee : Phaser.Sprite;
+	private honeyInstruct:Phaser.Text;
+	private honeyInstruct2 : Phaser.Text;
+	private honey : Phaser.Sprite;
+	private glowingHoneyInstruct: Phaser.Text;
+	private glowingHoney : Phaser.Sprite;
+	private glowingHoneyInstruct2 : Phaser.Text;
+	private glowingHoneyInstruct3 : Phaser.Text;
+	private wasp : Phaser.Sprite;
+	private waspInstruct : Phaser.Text;
+	private height : number;
+    private width : number;
+
+
+	public create() {
+			this.height = this.world.height;
+        	this.width = this.world.width;
+			var wordStyle = { font: "30px Oswald", fill: "#ffcc00", align: "center", stroke: '#af8c00', strokeThickness: 5 };
+        	var welcomeStyle = { font: "80px Oswald", fill: "#ffcc00", align: "center", stroke: '#af8c00', strokeThickness: 5 };
+        	this.welcome = this.game.add.text(this.width / 2, this.height / 20, "Welcome to Kimbee!", welcomeStyle);
+        	this.welcome.anchor.x = 0.5;
+        	this.bee = this.game.add.sprite(this.width / 8, this.height / 5, 'beeBig');
+        	this.bee.scale.x = 0.7;
+        	this.bee.scale.y = 0.7;
+        	this.glowingHoney = this.game.add.sprite(this.width / 8, this.height * 3 / 5, 'fairy');
+        	this.wasp = this.game.add.sprite(this.width / 8, this.height * 4 / 5, 'wasp');
+        	this.beeInstructs = this.game.add.text(this.width / 5, this.bee.y, "This is Kimbee. Help Kimbee collect", wordStyle);
+        	this.honey = this.game.add.sprite(this.beeInstructs.x + this.beeInstructs.width, this.height / 5, 'honey');
+        	this.honeyInstruct2 = this.game.add.text(this.honey.x + this.honey.width, this.height / 5, "by moving her up and down.", wordStyle);
+        	this.glowingHoneyInstruct = this.game.add.text(this.width / 5, this.height * 3 / 5, "This is a special kind of honey. When you", wordStyle);
[…]

### 2015-03-09 Paper/paper.tex
acknowledgements

@@
 
-We have developed an application, that we named {\em Kimbee}, that aims to help the process of speech therapy in young children.
+We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children.
 Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others.
@@
 
+We'd like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished.
+
 \bibliographystyle{abbrv}

### 2015-03-09 Paper/paper.tex
Implementation Section
Paper edits

@@
 We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children.
-Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others.
-Our application does not replace the speech therapist, rather it supplements the therapy.
+Speech therapy is often expensive for schools and parents to maintain, especially when children take abnorbmally long amounts of time to overcome their impediments.
+Our application does not replace the speech therapist rather it supplements the therapy.
 Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom.
-The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students.
+The therapist can then monitor the child's progress through our application and use this information to identify a child's problems and tailor the therapy to them.
 This will save both time and money for school districts and parents who are paying for their child's therapy.
@@
 The purpose of this paper and project is to make speech therapy more effective in English speaking children from age 5 to age 12.
+Common speech impediments in children are often caused by functional speech disorders, or trouble learning to make specific speech sounds \cite{Brown:Children}.
 Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorder \cite{Kreider:Intro}.
-It is also common for therapists to spend most of their time with students during these sessions or in the classroom because it is often hard to work with children remotely.
-A session usually consists of having the child repeat words back to the therapist in order to target a specific sound or phoneme.
-Common speech impediments in children are often caused by functional speech disorders, or trouble learning to make specific speech sounds \cite{Brown:Children}.
+Speech therapists only get to work with a child for as little as half an hour a week where the child repeat words back to the therapist in order to target a specific sound or phoneme.
+With only short sessions like these, remote practice would be very beneficial to a child if they had a way to receive feedback and if a therapist could track a child's progress.
 
 We chose to focus on `R' sounds as they are one of the more common mispronunciations found in our target age group \cite{Dodd:Children}.
-Most `R' disorders will commonly pronounce words as if the `R' was a `W'.
+Most `R' disorders will commonly pronounce words as if the `R' is a `W'.
 An example would be pronouncing the word {\em ``rabbit''} as {\em ``wabbit''}.
@@
 By having the child or user repeat a target several times until he or she is able to pronounce it correctly, we are emulating the in person setting that they are used to.
-Each time a word is spoken, an audio recording of the speech is documented and saved for the therapist to analyze at a later time.
+Each time a word is spoken an audio recording of the speech is documented and saved for the therapist to analyze at a later time.
 This process is then wrapped in game setting to make the process of saying and repeating words more enjoyable for children.
-This helps supplement the therapy, rather than aiming to replace it.
+This helps supplement the therapy rather than aiming to replace it.
 We hope that this will cause a decrease in the amount of time that children will need to spend in therapy, which will help save the school district or parents more money.
@@
 Their application currently only supports the Spanish language, which would not be of much help to English speaking students.
-Our project's scope is almost much narrower.
+Our project's scope is much narrower.
 Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outside the sessions.
@@
 However, most of these applications fail to incorporate a therapist into the learning model, which we believe is essential for helping the child overcome his or her disorder.
+
+\section{Implementation}
 

### 2015-03-09 Paper/paper.tex
More Work

@@
 
+We will now introduce our implementation and solution to the problem posed for children's speech therapy.
+Before we started designing {\em Kimbee}, we met with speech pathologist Richard Kreider to discuss what features would be needed for a system like this to work \cite{Kreider:Intro}.
+Mr.
+Kreider has over 25 years of experience working with children to overcome their speech disorders.
+Mr.
+Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time.
+As these were the two most important features Mr.
+Kreider discussed, we designed Kimbee around them as core features.
+
+\subsection{Game ({\secit Kimbee})}
+
+\subsection{Therapist Portal}
+
+\section{Results}
+
 \section{Conclusion}
+
+\section{Future Work}
 
@@
 
-We'd like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished.
+We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}.
 

### 2015-03-09 Paper/paper.tex
1 line remove
push

--- 2015-03-09 Paper/paper.tex
@@
 
+\section{Implementation}
+
+We will now introduce our implementation and solution to the problem posed for children's speech therapy.
+Before we started designing {\em Kimbee}, we met with speech pathologist Richard Kreider to discuss what features would be needed for a system like this to work \cite{Kreider:Intro}.
+Mr.
+Kreider has over 25 years of experience working with children to overcome their speech disorders.
+Mr.
+Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time.
+As these were the two most important features Mr.
+Kreider discussed, we designed Kimbee around them as core features.
+
+\subsection{Game ({\secit Kimbee})}
+
+\subsection{Therapist Portal}
+
+\section{Results}
+
 \section{Conclusion}
+
+\section{Future Work}
 

### 2015-03-09 Paper/paper.tex
Future Work

@@
 
+There are a few ways that we can expand on {\em Kimbee}.
+We plan on deploying the project for use in the Arlington Public School District to see how children respond and learn from {\em Kimbee} along with how experienced speech therapists use {\em Kimbee} to aid the therapy process.
+Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement.
+We can also enhance the child's experience by adding more mini games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.
+
 \section{Acknowledgments}

### 2015-03-09 Paper/paper.tex
Figure Fixing

@@
         University of Washington \hspace{0cm}
-        } \\[7 pt]
+        } \\[3 pt]
     \email{{\centering \{drapeau, huynick, necha\}@cs.washington.edu}}
@@
 
-\subsection{Game ({\secit Kimbee})}
+\begin{figure*}[t]
+  \centering
+  \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
+  \vspace{-26 pt}
+  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data. Right: The game interface.}
+  \label{fig:user}
+\end{figure*}
 
-\subsection{Therapist Portal}
+\subsection{User Flow}
+
+We will first describe the flow a typical user would take when using this application.
+The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see.
+
+\subsubsection{Game (Kimbee)}
+
+[User Flow Game Here]
+
+\subsubsection{Therapist Portal}
+
+[User Flow Therapist Portal Here]
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
+  \caption{Left: AAA. Middle: BBB. Right: CCC.}
+  \label{fig:tech}
+\end{figure*}
+
+\subsection{Implementation Details}
+
+We will now discuss the implementation details of each of the systems that make up {\em Kimbee}.
+
+\subsubsection{Game (Kimbee)}
+
+[Game Implementation Details Here]
+
+\subsubsection{Therapist Portal}
+
+[Therapist Portal Implementation Details Here]
 
@@
 
-\section{Conclusion}
+[Results Here]
 
@@
 Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement.
-We can also enhance the child's experience by adding more mini games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.
+We can also enhance the child's experience by adding more mini-games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.
+
+\section{Conclusion}
+
+[Conclusion Here]
 

### 2015-03-09 src/game/js/speechprocessing/SpeechSettings.ts
i'm a formatting genius 8))

@@ -9,44 +9,359 @@ class SpeechSettings {
         Global sphinx maps
         (contain all words possible and their phonemes and recognition grammars)
         */
-        sphinxWords : [
-            ["GREEN", "G R IY N"], ["GWEEN", "G W IY N"],
-            ["RABBIT", "R AE B AH T"], ["WABBIT", "W AE B AH T"],
-            ["AIR", "EH R"], ["AIW", "EH W"],
-            ["ARE", "AA R"], ["AWE", "AA W"],
-            ["BAR", "B AA R"], ["BAW", "B AA W"],
-            ["BEAR", "B EH R"], ["BEAW", "B EH W"],
-            ["BOAR", "B AO R"], ["BOAW", "B AO W"],
-            ["CAR", "K AA R"], ["CAW", "K AA W"],
-            ["CARE", "K EH R"], ["CAWE", "K EH W"]
-        ],
+        sphinxWords :  [['REPAIR', 'R IH P EH R'], ['WEPAIW', 'W IH P EH R'], ['REPAI', 'R IH P EH'], 
+                    ['MINORITY', 'M AY N AO R AH T IY'], ['MINOWITY', 'M AY N AO W AH T IY'], 
+                    ['SORROW', 'S AA R OW'], ['SOWWOW', 'S AA W OW'], 
+                    ['RYE', 'R AY'], ['WYE', 'W AY'], 
+                    ['EXPIRE', 'IH K S P AY R'], ['EXPIWE', 'IH K S P AY W'], 
+                    ['RECYCLE', 'R IY S AY K AH L'], ['WECYCLE', 'W IY S AY K AH L'], 
+                    ['RAVEN', 'R EY V AH N'], ['WAVEN', 'W EY V AH N'], 
+                    ['RAG', 'R AE G'], ['WAG', 'W AE G'], 
+                    ['RAN', 'R AE N'], ['WAN', 'W AE N'], 
+                    ['RAM', 'R AE M'], ['WAM', 'W AE M'], 
+                    ['RIP', 'R IH P'], ['WIP', 'W IH P'], 
+                    ['WRENCH', 'R EH N CH'], ['WWENCH', 'W EH N CH'], 
+                    ['ATTIRE', 'AH T AY ER'], ['ATTIRE', 'AH T AY UH'], 
+                    ['RIB', 'R IH B'], ['WIB', 'W IH B'], 
[…]

### 2015-03-09 Paper/paper.tex
fixed

@@
   \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
-  \caption{Left: AAA. Middle: BBB. Right: CCC.}
+  \caption{Left: The Therapist Portal, the user system of the therapist.
+Middle: The Central Server, hosts the recordings and facilitates interactions.
+Right: The Kimbee Game, interactive game that allows practice of speech for children.
+}
   \label{fig:tech}
@@
 We will now discuss the implementation details of each of the systems that make up {\em Kimbee}.
+This project is made up of many components.
+In particular we will discuss the three main systems: the Server, the Game, and the Therapist Portal.
+From a high level, the Game and the Therapist Portal are thinly interconnected to the Server via HyperText Transfer Protocol (HTTP).
 
 \subsubsection{Game (Kimbee)}
-
-[Game Implementation Details Here]
 

### 2015-03-09 Paper/paper.tex
fixed

@@
 We will first describe the flow a typical user would take when using this application.
-The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see.
+The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see after the child has played the game.
 
@@
   \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
-  \caption{Left: The Therapist Portal, the user system of the therapist.
+  \caption{\normalfont Left: The Therapist Portal, the user system of the therapist.
 Middle: The Central Server, hosts the recordings and facilitates interactions.
@@
 
-\subsubsection{Game (Kimbee)}
+\subsubsection{Component 1}
 
-\subsubsection{Therapist Portal}
+\subsubsection{Component 2}
 
-[Therapist Portal Implementation Details Here]
+\subsubsection{Component 3}
 

### 2015-03-09 Paper/paper.tex

@@
 
-\section{Implementation}
+\section{Design}
 
@@
 
-\subsection{Implementation Details}
+\section{Implementation Details}
 
@@
 
+\subsection{Game ({\secit Kimbee})}
+
+The Game is the system that the children interact with to practice speech.
+Since this system also performs speech processing to determine speech correctness, there are many interacting components.
+From a high level, the major sub systems are: the Phaser Game Implementation, the Speech Processing System, and the Server Application Programming Interface (API).
+We target this project toward web technologies to allow wide distribution and adoption.
+From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay.
+This required us to explore various new web technologies including Webworkers for multithreading and the UserMedia HTML5 API.
+
+\subsubsection{Platform choice}
+Since we want this project to work on as many devices as possible, we target emerging web technologies that work seamlessly across all devices with a web browser component.
+The web technology stack is advanced enough to handle our needs: there is a JavaScript port of the popular speech processing library CMU Sphinx, and we now have access to the user's microphone via UserMedia HTML5 API.
+After creating our project in the browser, we then can translate it to native applications via Apache Cordova, a web distribution technology based on embeddeding a web component inside a native application container on mobile devices.
+
+\subsubsection{Phaser Game Implementation}
+The Game component of the Kimbee system encompasses the view and control of the application: The main menu, the game play, and rendering.
+This is what the children interact with to practice speech.
+The game is implemented with the Phaser Game Framework.
+Which represents screens of the game into states.
+States are linked together in meaningful ways.
+For example, the Main Menu State links to the Option Menu State via a Phaser Framework Button.
+It also provides image animation, tweening, and collision support.
+To create our microphone button, we extend the Phaser Framework Button and implement connections to the speech processing component while preserving button functionality through inheritance.
+
+\subsection{Therapist Portal}
+
+[High Level Overview of Therapist Portal (tech)]
+
 \subsubsection{Component 1}
-
-\subsubsection{Component 2}
-
-\subsubsection{Component 3}
 

### 2015-03-09 Paper/paper.tex

@@
 
-\section{Design}
+\section{Application Design}
 
@@
   \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
-  \vspace{-26 pt}
-  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data. Right: The game interface.}
+  \vspace{-22 pt}
+  \caption{\normalfont Left: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource.
+Right: The flow diagram showing how therapists and children exchange data through the game and the portal.}
   \label{fig:user}
@@
 
-We will first describe the flow a typical user would take when using this application.
 The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see after the child has played the game.
+This will follow the example that the therapist has assigned {\em Kimbee} as homework for the child to do at home outside of the session.
+When the game is launched for the first time, a unique identification string is generated as a token for the child.
+This token should then be sent to the therapist allowing them to track the progress of the student.
+It is suggested that this first launch and setup take place in an in-person session with the therapist to alleviate any technical problems that may arise.
 
-\subsubsection{Game (Kimbee)}
+\subsubsection{Gameplay}
 
-[User Flow Game Here]
+The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}.
+Children simply tap the screen to make their character, a bee, move along the y-axis of the screen.
+Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end.
+Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed.
+This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.
+The difficulty of the text increases over time to simulate the treatment that the child would receive during a therapist session \cite{Rosenbek:Treatment}.
+If the system succeeds in verifying that the child spoke the text correctly, then the currency is added to the child's score.
+If the child fails to correctly pronounce the phrase or if the system fails to recognize the audio, then the child is asked to try again in order to continue.
+To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game \cite{Kreider:Intro}.
 
-\subsubsection{Therapist Portal}
+After every challenge, the audio spoken by the child is encoded and sent to the central data server, see Figure \ref{fig:user} for a diagram of this.
+These data can be examined and reviewed in the therapist portal.
+
+\subsubsection{Therapist Review}
 
 [User Flow Therapist Portal Here]
+
+\subsection{Currency}
 
@@
   \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
+  \vspace{-23 pt}
   \caption{\normalfont Left: The Therapist Portal, the user system of the therapist.

### 2015-03-09 Paper/paper.tex
fixed

@@
 \subsection{Game ({\secit Kimbee})}
-
-The Game is the system that the children interact with to practice speech.
+The Game or Kimbee system, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech.
 Since this system also performs speech processing to determine speech correctness, there are many interacting components.
-From a high level, the major sub systems are: the Phaser Game Implementation, the Speech Processing System, and the Server Application Programming Interface (API).
+From a high level, the major sub systems are: the {\em Phaser Game Implementation}, the {\em Speech Processing Component}, and the {\em Server Application Programming Interface (API)}.
 We target this project toward web technologies to allow wide distribution and adoption.
 From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay.
-This required us to explore various new web technologies including Webworkers for multithreading and the UserMedia HTML5 API.
+This required us to explore various new web technologies including HTML5 Web Workers for multithreading and the UserMedia HTML5 API.
 
@@
 \subsubsection{Phaser Game Implementation}
-The Game component of the Kimbee system encompasses the view and control of the application: The main menu, the game play, and rendering.
+The {\em Phaser Game Implementation} of the Kimbee system encompasses the view and control of the application: The main menu, the game play, and rendering.
 This is what the children interact with to practice speech.
@@
 To create our microphone button, we extend the Phaser Framework Button and implement connections to the speech processing component while preserving button functionality through inheritance.
+
+\subsubsection{Speech Processing Component}
+The {\em Speech Processing Component} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}.
+Requests are made through an API Singleton that is constructed on game load.
+These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data.
+Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers.
+When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads.
+Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
+\begin{enumerate}
+  \item
+    Web Workers are initalized to start processing the audio stream in parallel.
+  \item
+    Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
+  \item
+    Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
+\end{enumerate}
+Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}.
+The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx Component} to iterate a best guess for the correctness of the child's speech.
+
+\subsubsection{CMU Sphinx Component}
 

### 2015-03-09 Paper/paper.tex
fixed

@@
 
-We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children.
+We have developed an application named {\em Kimbee} that aims to help improve the process of speech therapy in young children.
 Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others.
@@
 
-\subsubsection{Gameplay}
+\subsubsection{Gameplay\label{sec:gameplay_flow}}
 
@@
 This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.
+
 The difficulty of the text increases over time to simulate the treatment that the child would receive during a therapist session \cite{Rosenbek:Treatment}.
@@
 If the child fails to correctly pronounce the phrase or if the system fails to recognize the audio, then the child is asked to try again in order to continue.
-To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game \cite{Kreider:Intro}.
+To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game.
 
@@
 
-[User Flow Therapist Portal Here]
+The therapist is responsible for tailoring lesson plans for each session with his or her students.
+Currently, this involves taking detailed notes during every session to document and track the progress of each student over time \cite{Kreider:Intro}.
+The goal of the Therapist Portal is to improve and simplify this process to increase the quality of treatment given to the student.
+As described in section \ref{sec:gameplay_flow}, every recording that each child produces will be sent to the central server.
+These recordings are then sent to Therapist Portal and listed for every student under the therapist.
+Additional data is sent down with each recording to help the therapist focus on words that the student had trouble speaking.
+For example, whether the child said the word or phrase correctly is included with the recording allowing the therapist to filter the recordings.
+
+After listening to all of the recordings that the child produced for homework, the therapist will have a good idea for where the student currently is in terms of progress.
 
@@
 
-\subsubsection{Speech Processing Component}
-The {\em Speech Processing Component} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}.
+\subsubsection{Speech Processing}
+The {\em Speech Processing} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}.
 Requests are made through an API Singleton that is constructed on game load.
@@
 Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}.
-The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx Component} to iterate a best guess for the correctness of the child's speech.
+The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx} to iterate a best guess for the correctness of the child's speech.
 
-\subsubsection{CMU Sphinx Component}
+\subsubsection{CMU Sphinx}
+CMU Sphinx\cite{CMU:Sphinx} is a speech processing library.
+There is a JavaScript port that allows audio recognition in the browser.
+Our {\em Speech Processing} component utilizes this JavaScript port to do audio recognition in the browser without server assistance.
+To deduce correct child speech we utilize this library creating target word and invalid word pairs.
+For example, when targeting `R' sounds, we can use CMU Sphinx to recognize the target word `Rabbit' or a invalid word `Wabbit.' With a large dictionary of words this has been effective in distinguishing replacements caused by speech disorders.
+
+\subsubsection{Server Application Programming Interface}
+The {\em Server Application Programming Interface} is what connects the Kimbee system to our central recording server.
+Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present.
+A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device.
+This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.
 
@@
 
-[High Level Overview of Therapist Portal (tech)]
+\subsubsection{Connection to Child Audio}
+
+\subsubsection{Playing of Audio}
+
+\subsubsection{Caching System}
 

### 2015-03-09 Paper/paper.tex
fixed

@@
 The Game or Kimbee system, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech.
+It is written in TypeScript and compiled to optimized JavaScript.
 Since this system also performs speech processing to determine speech correctness, there are many interacting components.
@@
 
+\subsection{Central Server}
+The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Kimbee Game} instances and the {\em Therapist Portal}.
+It is written in Node JS and stores data in a MongoDB instance.
+We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.
+
+\subsubsection{Data Models}
+  The server has three data models: recordings, children, and therapists.
+Recordings are the encoded microphone encodings and recognition data from the {\em Kimbee Game} instances.
+They are tied to a particular game instance via a unique token generated by the {\em Kimbee Game}.
+Children are models created by therapists to effectively ``hook into'' recordings.
+They specify a name for the child, and their token obtained from their {\em Kimbee Game} instance.
+Future recordings are then relayed to the therapist from this particular {\em Kimbee Game} instance.
+Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.
+
+\subsubsection{Audio Encoding \& Recording Storage}
+  When a audio file is recieved by a {\em Kimbee Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
+This file is then compressed and stored into the database as a recording.
+The recognition data (whether the {\em Kimbee Game} instance thinks the recording was correct) and the target word are also stored with the recording model.
+
+\subsubsection{Therapist Portal Application Programming Interface}
+  The server exposes a set of APIs for the {\em Therapist Portal} to utilize.
+This includes functionality to retrieve recordings for a particular child owned by the therapist record, retrieve the authenticated therapist record, authenticate therapists, and register therapists.
+This functionality is used via a HTTP interface with the {\em Central Server}.
+
 \subsection{Therapist Portal}
@@
 \subsubsection{Caching System}
-
-\subsubsection{Component 1}
 

### 2015-03-09 Paper/paper.tex

@@
 \section{Related Work}
+\label{sec:related}
 
@@
 After listening to all of the recordings that the child produced for homework, the therapist will have a good idea for where the student currently is in terms of progress.
+With this new information, the therapist will be able to start of the next in-person session with a more focused lesson plan.
 
 \subsection{Currency}
+
+As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children.
+We wanted to have an application that children would see less as homework, and more of a game.
+This was the underlying motivation for making {\em Kimbee} a game.
+In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}.
+We were able to create this using the honey collected as a currency.
+We also added the dynamic scoring of the honey, with the collection of the pots and completion of the challenges.
+
+Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}.
+For example, Mr.
+Kreider rewards children with small toys after they do well on a set of phrases.
+A reward system could be implemented where the currency is the honey from {\em Kimbee}.
+This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time.
+As this was only a quarter long project, this is left as future work.
 
@@
 Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
+\vspace{-3 pt}
 \begin{enumerate}
-  \item
-    Web Workers are initalized to start processing the audio stream in parallel.
-  \item
-    Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
-  \item
-    Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
+  \item Web Workers are initalized to start processing the audio stream in parallel.
+  \vspace{-6 pt}
+  \item Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
+  \vspace{-6 pt}
+  \item Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
 \end{enumerate}
+\vspace{-3 pt}
 Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}.
@@
 \subsubsection{CMU Sphinx}
-CMU Sphinx\cite{CMU:Sphinx} is a speech processing library.
+CMU Sphinx is a speech processing library \cite{CMU:Sphinx}.
 There is a JavaScript port that allows audio recognition in the browser.

### 2015-03-09 Paper/paper.tex

@@
 
-[Results Here]
+Upon the completion of {\em Kimbee}, we met with Mr.
+Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}.
+His reaction was very positive.
+He found no real flaws with the application and expressed that it would be very useful for children and his work with the children he works with.
+He did have suggestions for the future that are listed below under section \ref{sec:future_work}.
+Unfortunately we did not have time to test our application with actual children and track the results but we are confident that {\em Kimbee} can be used in a real world setting.
 
 \section{Future Work}
+\label{sec:future_work}
 

### 2015-03-09 Paper/paper.tex
fixed

@@
 \subsection{Game ({\secit Kimbee})}
-The Game or Kimbee system, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech.
+The {\em Game}, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech.
 It is written in TypeScript and compiled to optimized JavaScript.
@@
 \subsubsection{Phaser Game Implementation}
-The {\em Phaser Game Implementation} of the Kimbee system encompasses the view and control of the application: The main menu, the game play, and rendering.
+The {\em Phaser Game Implementation} of the {\em Game} encompasses the view and control of the application: The main menu, the game play, and rendering.
 This is what the children interact with to practice speech.
@@
 \subsubsection{Speech Processing}
-The {\em Speech Processing} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}.
+The {\em Speech Processing} of the {\em Game} handles all audio processing and speech related requests from the {\em Phaser Game Implementation}.
 Requests are made through an API Singleton that is constructed on game load.
@@
 \subsubsection{Server Application Programming Interface}
-The {\em Server Application Programming Interface} is what connects the Kimbee system to our central recording server.
+The {\em Server Application Programming Interface} is what connects the {\em Game} to our central recording server.
 Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present.

### 2015-03-09 Paper/paper.tex
fixed

@@
 \subsection{Central Server}
-The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Kimbee Game} instances and the {\em Therapist Portal}.
+The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Game} instances and the {\em Therapist Portal}.
 It is written in Node JS and stores data in a MongoDB instance.
@@
   The server has three data models: recordings, children, and therapists.
-Recordings are the encoded microphone encodings and recognition data from the {\em Kimbee Game} instances.
-They are tied to a particular game instance via a unique token generated by the {\em Kimbee Game}.
+Recordings are the microphone encodings and recognition data from the {\em Game} instances.
+They are tied to a particular game instance via a unique token generated by the {\em Game}.
 Children are models created by therapists to effectively ``hook into'' recordings.
-They specify a name for the child, and their token obtained from their {\em Kimbee Game} instance.
-Future recordings are then relayed to the therapist from this particular {\em Kimbee Game} instance.
+They specify a name for the child, and their token obtained from their {\em Game} instance.
+Future recordings are then relayed to the therapist from this particular {\em Game} instance.
 Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.
@@
 \subsubsection{Audio Encoding \& Recording Storage}
-  When a audio file is recieved by a {\em Kimbee Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
+  When a audio file is recieved by a {\em Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
 This file is then compressed and stored into the database as a recording.
-The recognition data (whether the {\em Kimbee Game} instance thinks the recording was correct) and the target word are also stored with the recording model.
+The recognition data (whether the {\em Game} instance thinks the recording was correct) and the target word are also stored with the recording model.
 

### 2015-03-09 Paper/paper.tex

@@
 
-\subsubsection{Server Application Programming Interface}
-The {\em Server Application Programming Interface} is what connects the {\em Game} to our central recording server.
+\subsubsection{Server API}
+The {\em Server API} is what connects the {\em Game} to our central recording server.
 Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present.
@@
 
-\subsubsection{Therapist Portal Application Programming Interface}
+\subsubsection{Therapist Portal API}
   The server exposes a set of APIs for the {\em Therapist Portal} to utilize.

### 2015-03-09 Paper/paper.tex
fixed
Components

@@
 
-We have developed an application named {\em Kimbee} that aims to help improve the process of speech therapy in young children.
+We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children.
 Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others.
@@
 \section{Related Work}
-\label{sec:related}
 
@@
 
-\section{Application Design}
+\section{Implementation}
 
@@
   \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
-  \vspace{-22 pt}
-  \caption{\normalfont Left: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource.
-Right: The flow diagram showing how therapists and children exchange data through the game and the portal.}
+  \vspace{-26 pt}
+  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data. Right: The game interface.}
   \label{fig:user}
@@
 
+We will first describe the flow a typical user would take when using this application.
 The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see after the child has played the game.
-This will follow the example that the therapist has assigned {\em Kimbee} as homework for the child to do at home outside of the session.
-When the game is launched for the first time, a unique identification string is generated as a token for the child.
-This token should then be sent to the therapist allowing them to track the progress of the student.
-It is suggested that this first launch and setup take place in an in-person session with the therapist to alleviate any technical problems that may arise.
 
-\subsubsection{Gameplay\label{sec:gameplay_flow}}
+\subsubsection{Game (Kimbee)}
 
-The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}.
-Children simply tap the screen to make their character, a bee, move along the y-axis of the screen.
-Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end.
-Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed.
-This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.
+[User Flow Game Here]
 
-The difficulty of the text increases over time to simulate the treatment that the child would receive during a therapist session \cite{Rosenbek:Treatment}.
-If the system succeeds in verifying that the child spoke the text correctly, then the currency is added to the child's score.
-If the child fails to correctly pronounce the phrase or if the system fails to recognize the audio, then the child is asked to try again in order to continue.
-To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game.
+\subsubsection{Therapist Portal}
 
-After every challenge, the audio spoken by the child is encoded and sent to the central data server, see Figure \ref{fig:user} for a diagram of this.
-These data can be examined and reviewed in the therapist portal.
-
-\subsubsection{Therapist Review}
-
-The therapist is responsible for tailoring lesson plans for each session with his or her students.
-Currently, this involves taking detailed notes during every session to document and track the progress of each student over time \cite{Kreider:Intro}.
-The goal of the Therapist Portal is to improve and simplify this process to increase the quality of treatment given to the student.
-As described in section \ref{sec:gameplay_flow}, every recording that each child produces will be sent to the central server.
-These recordings are then sent to Therapist Portal and listed for every student under the therapist.
-Additional data is sent down with each recording to help the therapist focus on words that the student had trouble speaking.
-For example, whether the child said the word or phrase correctly is included with the recording allowing the therapist to filter the recordings.
-
-After listening to all of the recordings that the child produced for homework, the therapist will have a good idea for where the student currently is in terms of progress.
-With this new information, the therapist will be able to start of the next in-person session with a more focused lesson plan.
-
-\subsection{Currency}
-
-As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children.
-We wanted to have an application that children would see less as homework, and more of a game.
-This was the underlying motivation for making {\em Kimbee} a game.
-In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}.
-We were able to create this using the honey collected as a currency.
-We also added the dynamic scoring of the honey, with the collection of the pots and completion of the challenges.
-
-Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}.
-For example, Mr.
-Kreider rewards children with small toys after they do well on a set of phrases.
-A reward system could be implemented where the currency is the honey from {\em Kimbee}.
-This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time.
-As this was only a quarter long project, this is left as future work.
+[User Flow Therapist Portal Here]
 
@@
   \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
-  \vspace{-23 pt}
   \caption{\normalfont Left: The Therapist Portal, the user system of the therapist.
@@
 
-\section{Implementation Details}
+\subsection{Implementation Details}
 
@@
 
-\subsection{Game ({\secit Kimbee})}
-The {\em Game}, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech.
-It is written in TypeScript and compiled to optimized JavaScript.
-Since this system also performs speech processing to determine speech correctness, there are many interacting components.
-From a high level, the major sub systems are: the {\em Phaser Game Implementation}, the {\em Speech Processing Component}, and the {\em Server Application Programming Interface (API)}.
-We target this project toward web technologies to allow wide distribution and adoption.
-From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay.
-This required us to explore various new web technologies including HTML5 Web Workers for multithreading and the UserMedia HTML5 API.
+\subsubsection{Component 1}
 
-\subsubsection{Platform choice}
-Since we want this project to work on as many devices as possible, we target emerging web technologies that work seamlessly across all devices with a web browser component.
-The web technology stack is advanced enough to handle our needs: there is a JavaScript port of the popular speech processing library CMU Sphinx, and we now have access to the user's microphone via UserMedia HTML5 API.
-After creating our project in the browser, we then can translate it to native applications via Apache Cordova, a web distribution technology based on embeddeding a web component inside a native application container on mobile devices.
+\subsubsection{Component 2}
 
-\subsubsection{Phaser Game Implementation}
-The {\em Phaser Game Implementation} of the {\em Game} encompasses the view and control of the application: The main menu, the game play, and rendering.
-This is what the children interact with to practice speech.
-The game is implemented with the Phaser Game Framework.
-Which represents screens of the game into states.
-States are linked together in meaningful ways.
-For example, the Main Menu State links to the Option Menu State via a Phaser Framework Button.
-It also provides image animation, tweening, and collision support.
-To create our microphone button, we extend the Phaser Framework Button and implement connections to the speech processing component while preserving button functionality through inheritance.
+\subsubsection{Component 3}
 
-\subsubsection{Speech Processing}
-The {\em Speech Processing} of the {\em Game} handles all audio processing and speech related requests from the {\em Phaser Game Implementation}.
-Requests are made through an API Singleton that is constructed on game load.
-These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data.
-Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers.
-When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads.
-Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
-\vspace{-3 pt}
-\begin{enumerate}
-  \item Web Workers are initalized to start processing the audio stream in parallel.
-  \vspace{-6 pt}
-  \item Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
-  \vspace{-6 pt}
-  \item Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
-\end{enumerate}
-\vspace{-3 pt}
-Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}.
-The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx} to iterate a best guess for the correctness of the child's speech.
-
-\subsubsection{CMU Sphinx}
-CMU Sphinx is a speech processing library \cite{CMU:Sphinx}.
-There is a JavaScript port that allows audio recognition in the browser.
-Our {\em Speech Processing} component utilizes this JavaScript port to do audio recognition in the browser without server assistance.
-To deduce correct child speech we utilize this library creating target word and invalid word pairs.
-For example, when targeting `R' sounds, we can use CMU Sphinx to recognize the target word `Rabbit' or a invalid word `Wabbit.' With a large dictionary of words this has been effective in distinguishing replacements caused by speech disorders.
-
-\subsubsection{Server API}
-The {\em Server API} is what connects the {\em Game} to our central recording server.
-Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present.
-A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device.
-This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.
-
-\subsection{Central Server}
-The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Game} instances and the {\em Therapist Portal}.
-It is written in Node JS and stores data in a MongoDB instance.
-We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.
-
-\subsubsection{Data Models}
-  The server has three data models: recordings, children, and therapists.
-Recordings are the microphone encodings and recognition data from the {\em Game} instances.
-They are tied to a particular game instance via a unique token generated by the {\em Game}.
-Children are models created by therapists to effectively ``hook into'' recordings.
-They specify a name for the child, and their token obtained from their {\em Game} instance.
-Future recordings are then relayed to the therapist from this particular {\em Game} instance.
-Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.
-
-\subsubsection{Audio Encoding \& Recording Storage}
-  When a audio file is recieved by a {\em Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
-This file is then compressed and stored into the database as a recording.
-The recognition data (whether the {\em Game} instance thinks the recording was correct) and the target word are also stored with the recording model.
-
-\subsubsection{Therapist Portal API}
-  The server exposes a set of APIs for the {\em Therapist Portal} to utilize.
-This includes functionality to retrieve recordings for a particular child owned by the therapist record, retrieve the authenticated therapist record, authenticate therapists, and register therapists.
-This functionality is used via a HTTP interface with the {\em Central Server}.
-
-\subsection{Therapist Portal}
-
-\subsubsection{Connection to Child Audio}
-
-\subsubsection{Playing of Audio}
-
-\subsubsection{Caching System}
+[Therapist Portal Implementation Details Here]
 
@@
 
-Upon the completion of {\em Kimbee}, we met with Mr.
-Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}.
-His reaction was very positive.
-He found no real flaws with the application and expressed that it would be very useful for children and his work with the children he works with.
-He did have suggestions for the future that are listed below under section \ref{sec:future_work}.
-Unfortunately we did not have time to test our application with actual children and track the results but we are confident that {\em Kimbee} can be used in a real world setting.
+[Results Here]
 
 \section{Future Work}
-\label{sec:future_work}
 

### 2015-03-09 Paper/paper.tex
Aaron
Bib adjustments and section 3.1.1

@@
 
-\section{Implementation}
+\section{Application Design}
 
@@
   \vspace{-26 pt}
-  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data. Right: The game interface.}
+  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data through the game and the portal.
+Right: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource along the way.}
   \label{fig:user}
@@
 
-We will first describe the flow a typical user would take when using this application.
 The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see after the child has played the game.
+This will follow the example that the therapist has assigned {\em Kimbee} as homework for the child to do at home outside of the session.
+When the game is launched for the first time, a unique identification string is generated as a token for the child.
+This token should then be sent to the therapist allowing them to track the progress of the student.
+It is suggested that this first launch and setup take place in an in-person session with the therapist to alleviate any technical problems that may arise.
 
@@
 
-[User Flow Game Here]
+The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}.
+Children simply tap the screen to make their character, a bee, move along the y-axis of the screen.
+Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end.
+Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed.
+This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.
+The difficulty of the text increases over time to simulate the treatment that the child would receive during a therapist session \cite{Rosenbek:Treatment}.
+If the system succeeds in verifying that the child spoke the text correctly, then the currency is added to the child's score.
+If the child fails to correctly pronounce the phrase or if the system fails to recognize the audio, then the child is asked to try again in order to continue.
+To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game \cite{Kreider:Intro}.
+
+After every challenge, the audio spoken by the child is encoded and sent to the central data server, see Figure \ref{fig:user} for a diagram of this.
 
@@
 [User Flow Therapist Portal Here]
+
+\subsection{Currency}
 
@@
 
+\subsection{Game ({\secit Kimbee})}
+
+[High Level Overview of Game (tech)]
+
 \subsubsection{Component 1}
 
-\subsubsection{Component 2}
+[Component 1 Details]
 
-\subsubsection{Component 3}
+\subsection{Therapist Portal}
 
-[Therapist Portal Implementation Details Here]
+[High Level Overview of Therapist Portal (tech)]
+
+\subsubsection{Component 1}
+
+[Component 1 Details]
 

### 2015-03-09 Paper/paper.tex
Figure Adjustments

@@
   \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
-  \vspace{-26 pt}
-  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data through the game and the portal.
-Right: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource along the way.}
+  \vspace{-22 pt}
+  \caption{\normalfont Left: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource.
+Right: The flow diagram showing how therapists and children exchange data through the game and the portal.}
   \label{fig:user}
@@
 
-\subsubsection{Game (Kimbee)}
+\subsubsection{Gameplay}
 
@@
 After every challenge, the audio spoken by the child is encoded and sent to the central data server, see Figure \ref{fig:user} for a diagram of this.
+These data can be examined and reviewed in the therapist portal.
 
-\subsubsection{Therapist Portal}
+\subsubsection{Therapist Review}
 
@@
   \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
+  \vspace{-22 pt}
   \caption{\normalfont Left: The Therapist Portal, the user system of the therapist.

### 2015-03-09 Paper/paper.tex
spacing
Gamplay

@@
   \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
-  \vspace{-22 pt}
+  \vspace{-23 pt}
   \caption{\normalfont Left: The Therapist Portal, the user system of the therapist.
@@
 \subsection{Game ({\secit Kimbee})}
+The Game or Kimbee system, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech.
+Since this system also performs speech processing to determine speech correctness, there are many interacting components.
+From a high level, the major sub systems are: the {\em Phaser Game Implementation}, the {\em Speech Processing Component}, and the {\em Server Application Programming Interface (API)}.
+We target this project toward web technologies to allow wide distribution and adoption.
+From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay.
+This required us to explore various new web technologies including HTML5 Web Workers for multithreading and the UserMedia HTML5 API.
 
-[High Level Overview of Game (tech)]
+\subsubsection{Platform choice}
+Since we want this project to work on as many devices as possible, we target emerging web technologies that work seamlessly across all devices with a web browser component.
+The web technology stack is advanced enough to handle our needs: there is a JavaScript port of the popular speech processing library CMU Sphinx, and we now have access to the user's microphone via UserMedia HTML5 API.
+After creating our project in the browser, we then can translate it to native applications via Apache Cordova, a web distribution technology based on embeddeding a web component inside a native application container on mobile devices.
 
-\subsubsection{Component 1}
+\subsubsection{Phaser Game Implementation}
+The {\em Phaser Game Implementation} of the Kimbee system encompasses the view and control of the application: The main menu, the game play, and rendering.
+This is what the children interact with to practice speech.
+The game is implemented with the Phaser Game Framework.
+Which represents screens of the game into states.
+States are linked together in meaningful ways.
+For example, the Main Menu State links to the Option Menu State via a Phaser Framework Button.
+It also provides image animation, tweening, and collision support.
+To create our microphone button, we extend the Phaser Framework Button and implement connections to the speech processing component while preserving button functionality through inheritance.
 
-[Component 1 Details]
+\subsubsection{Speech Processing Component}
+The {\em Speech Processing Component} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}.
+Requests are made through an API Singleton that is constructed on game load.
+These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data.
+Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers.
+When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads.
+Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
+\begin{enumerate}
+  \item
+    Web Workers are initalized to start processing the audio stream in parallel.
+  \item
+    Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
+  \item
+    Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
+\end{enumerate}
+Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}.
+The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx Component} to iterate a best guess for the correctness of the child's speech.
+
+\subsubsection{CMU Sphinx Component}
 
@@
 \subsubsection{Component 1}
-
-[Component 1 Details]
 

### 2015-03-09 Paper/paper.tex
Citation

@@
 Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}.
-The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx Component} to iterate a best guess for the correctness of the child's speech.
+The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx} to iterate a best guess for the correctness of the child's speech.
 
-\subsubsection{CMU Sphinx Component}
+\subsubsection{CMU Sphinx}
+
+CITATION FOR AARON \cite{CMU:Sphinx}.
 

### 2015-03-09 Paper/paper.tex
More citations

@@
 After listening to all of the recordings that the child produced for homework, the therapist will have a good idea for where the student currently is in terms of progress.
+With this new information, the therapist will be able to start of the next in-person session with a more focused lesson plan.
 
 \subsection{Currency}
+
+As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children.
+We wanted to have an application that children would see less as homework, and more of a game.
+This was the underlying motivation for making {\em Kimbee} a game.
+In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}.
 
@@
 \subsubsection{CMU Sphinx}
+CMU Sphinx\cite{CMU:Sphinx} is a speech processing library.
+There is a JavaScript port that allows audio recognition in the browser.
+Our {\em Speech Processing} component utilizes this JavaScript port to do audio recognition in the browser without server assistance.
+To deduce correct child speech we utilize this library creating target word and invalid word pairs.
+For example, when targeting `R' sounds, we can use CMU Sphinx to recognize the target word `Rabbit' or a invalid word `Wabbit.' With a large dictionary of words this has been effective in distinguishing replacements caused by speech disorders.
 
-CITATION FOR AARON \cite{CMU:Sphinx}.
+\subsubsection{Server Application Programming Interface}
+The {\em Server Application Programming Interface} is what connects the Kimbee system to our central recording server.
+Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present.
+A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device.
+This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.
 

### 2015-03-09 Paper/paper.tex
Currency section complete

@@
 In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}.
+We were able to create this using the honey collected as a currency.
+We also added the dynamic scoring of the honey, with the collection of the pots and completion of the challenges.
+
+Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}.
+For example, Mr.
+Kreider rewards children with small toys after they do well on a set of phrases.
+A reward system could be implemented where the currency is the honey from {\em Kimbee}.
+This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time.
+As this was only a quarter long project, this is left as future work.
 

### 2015-03-09 Paper/paper.tex
Spelling

@@
 
-\subsubsection{Server Application Programming Interface}
+\subsubsection{Server API}
 The {\em Server Application Programming Interface} is what connects the Kimbee system to our central recording server.
@@
 This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.
+
+\subsection{Central Server}
+The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Kimbee Game} instances and the {\em Therapist Portal}.
+It is written in Node JS and stores data in a MongoDB instance.
+We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.
+
+\subsubsection{Data Models}
+  The server has three data models: recordings, children, and therapists.
+Recordings are the encoded microphone encodings and recognition data from the {\em Kimbee Game} instances.
+They are tied to a particular game instance via a unique token generated by the {\em Kimbee Game}.
+Children are models created by therapists to effectively ``hook into'' recordings.
+They specify a name for the child, and their token obtained from their {\em Kimbee Game} instance.
+Future recordings are then relayed to the therapist from this particular {\em Kimbee Game} instance.
+Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.
+
+\subsubsection{Audio Encoding \& Recording Storage}
+  When a audio file is recieved by a {\em Kimbee Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
+This file is then compressed and stored into the database as a recording.
+The recognition data, whether the {\em Kimbee Game} instance thinks the recording was correct, and the target word are also stored with the recording model.
+
+\subsubsection{Therapist Portal API}
+  The server exposes a set of APIs for the {\em Therapist Portal} to utilize.
+This includes functionality to retrieve recordings for a particular child owned by the therapist record, retrieve the authenticated therapist record, authenticate therapists, and register therapists.
+This functionality is used via a HTTP interface with the {\em Central Server}.
 

### 2015-03-09 Paper/paper.tex

@@
 \subsubsection{Server API}
-The {\em Server Application Programming Interface} is what connects the Kimbee system to our central recording server.
+The {\em Server API} is what connects the {\em Game} to our central recording server.
 Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present.

### 2015-03-09 Paper/paper.tex
Therapist portal

@@
 \subsubsection{Audio Encoding \& Recording Storage}
-  When a audio file is recieved by a {\em Kimbee Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
+  When a audio file is recieved by a {\em Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
 This file is then compressed and stored into the database as a recording.
-The recognition data, whether the {\em Kimbee Game} instance thinks the recording was correct, and the target word are also stored with the recording model.
+The recognition data (whether the {\em Game} instance thinks the recording was correct) and the target word are also stored with the recording model.
 
@@
 \subsection{Therapist Portal}
+
+The {\em Therapist Portal}, see Figure \ref{fig:tech}, is the application the therapist will use to track his or her student's progress and listen to the student's audio recordings.
+It is written in Javascript using the jQuery library with Bootstrap for the design elements and look of the page.
 

### 2015-03-09 Paper/paper.tex
Conclusion

@@
 It is written in Node JS and stores data in a MongoDB instance.
-We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.
+We also do audio encoding to create playable audio files from child microphone data obtained from {\em Game} instances.
 
@@
 
-[Conclusion Here]
+To conclude, {\em Kimbee} is an application which uses speech recognition to help children and speech therapists better remedy speech impediments.
+While it currently only focuses on `R' to `W' sounds, it can be further expanded to supplement therapy by giving a therapist the recordings of a child in a remote setting and by giving a child the opportunity to practice more than the short time period allotted weekly.
+By giving children an enjoyable speech therapy tool we hope to save money the money of both schools and parents while simultaneously giving children a better education by helping them overcome their speech impediment as quickly as possible.
 

### 2015-03-09 Paper/paper.tex
Conclusion

@@
 
-To conclude, {\em Kimbee} is an application which uses speech recognition to help children and speech therapists better remedy speech impediments.
+{\em Kimbee} is an application which uses speech recognition to help children and speech therapists better remedy speech impediments.
 While it currently only focuses on `R' to `W' sounds, it can be further expanded to supplement therapy by giving a therapist the recordings of a child in a remote setting and by giving a child the opportunity to practice more than the short time period allotted weekly.
-By giving children an enjoyable speech therapy tool we hope to save money the money of both schools and parents while simultaneously giving children a better education by helping them overcome their speech impediment as quickly as possible.
+By giving children an enjoyable speech therapy tool we hope to save the money of both schools and parents while simultaneously giving children a better education by helping them overcome their speech impediment as quickly as possible.
 

### 2015-03-09 Paper/paper.tex
final

@@
 This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time.
-As this was only a quarter long project, this is left as future work.
+As this was only a quarter long project, this is left as future work.\label{sec:currency}
 
@@
 \subsection{Therapist Portal}
-
 The {\em Therapist Portal}, see Figure \ref{fig:tech}, is the application the therapist will use to track his or her student's progress and listen to the student's audio recordings.
@@
 \subsubsection{Connection to Child Audio}
-
-\subsubsection{Playing of Audio}
+When the portal is launched, the data for all of the children under the therapist is downloaded through a HTTP GET request to the central server.
+The data is returned as a JSON object a short amount of time after the page is loaded.
+The WAV files for each recording are not downloaded at this time because of the significant size of each file.
+Instead, each recording is lazy instantiated and only requested when the user clicks play.
+A unique ID represents each audio recording and if clicked, a request will be made to the central server for the WAV file of the recording.
+When this request returns with the audio, the data is injected into the DOM through a HTML audio tag and then played.
 
 \subsubsection{Caching System}
+
+Before any request for a recording is made, a cache is first checked to see if the recording is already on the client.
+If a cache miss occurs, then the request will be made.
+If a cache hit occurs, then the audio will be immediately injected into the DOM and played.
+This system allows the therapist to replay the same audio recording multiple times without having to make a significant number of requests.
+A system for pre-fetching was discussed but never implemented; we leave this as future work.
 
@@
 His reaction was very positive.
-He found no real flaws with the application and expressed that it would be very useful for children and his work with the children he works with.
+He found no real flaws with the application and expressed that it would be very useful for children to work with.
+He wants us to continue consulting and working with him in the future as he thought that {\em Kimbee} was very promising.
 He did have suggestions for the future that are listed below under section \ref{sec:future_work}.
@@
 We can also enhance the child's experience by adding more mini-games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.
+The token and currency system described at the end of section \ref{sec:currency} is also left as future work.
 
@@
 We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}.
+We would also like to thank Bruce Hemingway and the TA for helping us throughout the project with guidance and feedback.
 

### 2015-03-09 Paper/paper.tex
Names are hard
Proofread

@@
 Researchers at the University of Zaragoza have created a standalone tablet application that aims to remove the therapist from the treatment \cite{Carlos:Vocaliza}.
-The researchers created an application for children to speak words and receive feedback on whether the word they said matches what was on the screen.
+The researchers created an application for children to speak words and receive feedback on whether the word they said matches the correct pronunciation of what was on the screen.
 The model they used also requires the student to train his or her voice in order for it to be recognized and processed correctly.
@@
 Before we started designing {\em Kimbee}, we met with speech pathologist Richard Kreider to discuss what features would be needed for a system like this to work \cite{Kreider:Intro}.
-Mr.
 Kreider has over 25 years of experience working with children to overcome their speech disorders.
-Mr.
 Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time.
-As these were the two most important features Mr.
-Kreider discussed, we designed Kimbee around them as core features.
+As these were the two most important features Kreider discussed, we designed Kimbee around them as core features.
 
@@
 Children simply tap the screen to make their character, a bee, move along the y-axis of the screen.
-Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end.
-Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed.
+Collecting honey causes their score to increase and colliding with an enemy wasp causes the game to end.
+Interleaved with the enemy wasps and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed.
 This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.
@@
 As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children.
-We wanted to have an application that children would see less as homework, and more of a game.
+We wanted to have an application that children would see less as homework and more of a game.
 This was the underlying motivation for making {\em Kimbee} a game.
@@
 Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}.
-For example, Mr.
-Kreider rewards children with small toys after they do well on a set of phrases.
+For example, Kreider rewards children with small toys after they do well on a set of phrases.
 A reward system could be implemented where the currency is the honey from {\em Kimbee}.
@@
 This is what the children interact with to practice speech.
-The game is implemented with the Phaser Game Framework.
-Which represents screens of the game into states.
+The game is implemented with the Phaser Game Framework  which represents screens of the game into states.
 States are linked together in meaningful ways.
@@
 Children are models created by therapists to effectively ``hook into'' recordings.
-They specify a name for the child, and their token obtained from their {\em Game} instance.
+They specify a name for the child and their token obtained from their {\em Game} instance.
 Future recordings are then relayed to the therapist from this particular {\em Game} instance.
@@
 
-Upon the completion of {\em Kimbee}, we met with Mr.
-Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}.
+Upon the completion of {\em Kimbee}, we met with Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}.
 His reaction was very positive.
@@
 We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}.
-We would also like to thank Bruce Hemingway and the TA for helping us throughout the project with guidance and feedback.
+We would also like to thank Bruce Hemingway and Hanchuan Li for helping us throughout the project with guidance and feedback.
 

### 2015-03-09 src/game/js/speechprocessing/RecognizerConsumer.ts
fixed

@@ -56,6 +56,7 @@ class RecognizerConsumer {
      */
     private loadWords() : void {
         // load words
+        console.log("ADDING WORDS");
         this.worker.postMessage({'command' : 'addWords', 'data' : this.words});
     }
 
@@ -63,6 +64,7 @@ class RecognizerConsumer {
      * Loads the ith grammar to recognize
      */
     private loadGrammar(i : number) : void {
+        console.log("ADDING GRAMMAR " + i);
         this.worker.postMessage({'command' : 'addGrammar', 'data' : this.grammars[i].g});
     }
 

### 2015-03-10 src/game/js/balloongame/BalloonGameState.ts
levels

@@ -34,6 +34,7 @@ class BalloonGameState extends Phaser.State {
     private gameOver : Phaser.Text;
     private level : number;
     private numCorrect : number;
+    private numWrong : number;
     private first : boolean;
 
     public preload() {
@@ -41,7 +42,7 @@ class BalloonGameState extends Phaser.State {
     }
 
     public create() {
-        var firstWord = this.speechProcessor.getNextWord();
+        var firstWord = this.speechProcessor.getNextWord(1);
         var wordStyle = { font: "45px Oswald", fill: "#ffcc00", align: "center", stroke: '#af8c00', strokeThickness : 5};
         var gameOverStyle = { font: "80px Oswald", fill: "#ffcc00", align: "center", stroke: '#af8c00', strokeThickness : 5};
         this.tada = this.game.add.audio('tada');
@@ -85,7 +86,7 @@ class BalloonGameState extends Phaser.State {
         this.spawnWasp = true;
 
         this.fairy = this.game.add.group();
-        this.fairy.enableBody = true;
+        this.fairy.enableBody = true;       
         this.fairy.physicsBodyType = Phaser.Physics.ARCADE;
 
         this.gameOver = this.game.add.text(this.width / 2, this.height / 10, "GAME OVER\nClick to Play Again", gameOverStyle);
@@ -96,8 +97,9 @@ class BalloonGameState extends Phaser.State {
 
         this.game.paused = false;
 
-        this.level = 0;
+        this.level = 1;
         this.numCorrect = 0;
+        this.numWrong = 0;
 
         this.lastHoneyX = this.game.world.randomY;
         this.honeyChain = Math.floor(Math.random() * 3);
@@ -109,7 +111,16 @@ class BalloonGameState extends Phaser.State {
 
     private onCorrect() {
         this.tada.play();
-        var nextWord = this.speechProcessor.getNextWord();
+        this.numWrong = 0;
+        if(this.numCorrect == 3) {
+            if(this.level != 4) {
+                this.level = this.level + 1;
+            }
+            this.numCorrect = 0;
+        } else {
+            this.numCorrect = this.numCorrect + 1;
+        }
+        var nextWord = this.speechProcessor.getNextWord(this.level);
         this.word.setText("Now say: " + nextWord);
         this.word.visible = false;
         this.game.paused = false;
@@ -119,6 +130,14 @@ class BalloonGameState extends Phaser.State {
     }
 
     private onWrong() {
+        if(this.numCorrect == -3) {
+            if(this.level != 1) {
[…]

### 2015-03-10 src/game/js/speechprocessing/SpeechProcessor.ts

@@ -103,9 +103,8 @@ class SpeechProcessor {
      * Gets the next word in the bank
      * @returns {string} The word. Null if none available
      */
-    public getNextWord() : any {
-        //TODO: Add levels here
-        this.currentWord = this.wordBank.next();
+    public getNextWord(level : number) : any {
+        this.currentWord = this.wordBank.next(level);
         return this.currentWord;
     }
 

### 2015-03-10 src/game/js/speechprocessing/SpeechSettings.ts

@@ -27,19 +27,20 @@ class SpeechSettings {
                     ['RAY', 'R EY'], ['WAY', 'W EY'], 
                     ['FORUM', 'F AO R AH M'], ['FOWUM', 'F AO W AH M'], 
                     ['RADIANT', 'R EY D IY AH N T'], ['WADIANT', 'W EY D IY AH N T'], 
-                    ['REDUCERADIAL', ''], 
-                    ['CURRENT', 'K ER AH N T'], ['CURRENT', 'K UH AH N T'], 
+                    ['REDUCE', 'R IH D UW S'], ['WEDUCE', 'W IH D UW S'],
+                    ['RADIAL', 'R EY D IY AH L'], ['WADIAL', 'W EY D IY AH L'],
+                    ['CURRENT', 'K ER AH N T'], ['CUWWENT', 'K UH W AH N T'], 
                     ['BEFORE', 'B IH F AO R'], ['BEFOWE', 'B IH F AO W'], 
                     ['ROOT', 'R UW T'], ['WOOT', 'W UW T'], 
                     ['AWARE', 'AH W EH R'], ['AWAWE', 'AH W EH W'], 
                     ['ADMIRE', 'AE D M AY R'], ['ADMIWE', 'AE D M AY W'], 
                     ['MATURE', 'M AH CH UH R'], ['MATUWE', 'M AH CH UH W'], 
-                    ['ROSE', 'R OW Z'], ['WOSE', 'W OW Z'], ['RICE', 'R AY S'], 
-                    ['WICE', 'W AY S'], ['MEMOIR', 'M EH M W AA R'], 
-                    ['MEMOIW', 'M EH M W AA W'], ['MEMOI', 'M EH M W AA'], 
+                    ['ROSE', 'R OW Z'], ['WOSE', 'W OW Z'], 
+                    ['RICE', 'R AY S'], ['WICE', 'W AY S'], 
+                    ['MEMOIR', 'M EH M W AA R'], ['MEMOIW', 'M EH M W AA W'], ['MEMOI', 'M EH M W AA'], 
                     ['JUROR', 'JH UH R ER'], ['JUWOW', 'JH UH W ER'], ['JUROR', 'JH UH R UH'], ['JURO', 'JH UH R'], 
                     ['INDOOR', 'IH N D AO R'], ['INDOOW', 'IH N D AO W'], ['INDOO', 'IH N D AO'], 
[…]

### 2015-03-10 src/game/js/speechprocessing/WordBank.ts

@@ -40,7 +40,7 @@ class WordBank {
      * available.
      * @returns {string} The word
      */
-    public next() : string {
+    public next(level : number) : string {
         //TODO: Add levels here
         if (this.words.length == 0) return null;
 
@@ -48,6 +48,11 @@ class WordBank {
         this.current %= this.words.length;
 
         var pair = this.words[this.current];
+        while(pair.level != level) {
+            this.current++;
+            this.current %= this.words.length;
+            var pair = this.words[this.current];
+        }
 
         return pair.right;
     }

### 2015-03-10 _cordova/platforms/android/assets/www/js/BootState.ts
fixed

@@ -1,64 +1,0 @@
-///<reference path="./def/phaser.d.ts" />
-import SpeechProcessor = require('./speechprocessing/SpeechProcessor');
-import Server = require('./server/Server');
-
-/**
- * The boot state of the Application
- * This state is visited briefly before the game loads completely
- */
-class BootState extends Phaser.State {
-    public preload() {
-        this.load.image('backButton', 'img/back-button.png');
-        this.load.image('menuBackground', 'img/menu-background.png');
-        this.load.image('balloonsBackground', 'img/balloons-background.png');
-        this.load.image('playButton', 'img/play-button.png');
-        this.load.image('upButton', 'img/up-button.png');
-        this.load.image('downButton', 'img/down-button.png');
-        this.load.image('settingsButton', 'img/settings-button.png');
-        this.load.image('combContainer', 'img/comb-container.png');
-        this.load.image('gameIconBalloons', 'img/game-icon-balloons.png');
-        this.load.image('gameIconMaze', 'img/game-icon-maze.png');
-        this.load.spritesheet('beeBig', 'img/bee-big.png', 128, 109, 2);
-        this.load.image('beeBasket', 'img/bee-basket.png');
-        this.load.image('balloon', 'img/balloon.png');
-        this.load.image('flower', 'img/flower-purple.png'); 
-        this.load.image('honey', 'img/honey.png');
-        this.load.image('wasp', 'img/buff-wasp.jpg');
-        this.load.spritesheet('fairy', 'img/princess.png', 65, 75, 2);
-        this.load.spritesheet('microphoneButton', 'img/microphone-button.png', 110, 110, 3);
-        this.load.audio('tada', 'sfx/ta-da.mp3');
-        this.load.audio('try-again', 'sfx/try-again.mp3');
-    }
-
-    public create() {
-        var wordStyle = { font: "45px Arial", fill: "#333333", align: "center" };
-        var text = this.game.add.text(this.world.width / 3, this.world.height / 10, "loading...", wordStyle);
-
-        // Cause the game to go fullscreen
-        this.game.scale.scaleMode = Phaser.ScaleManager.SHOW_ALL;
-        // Maximum touches allowed at once
-        this.input.maxPointers = 1;
-
-        //  Phaser will automatically pause if the browser tab the game is in loses focus. Disable this
-        this.stage.disableVisibilityChange = true;
-
-        this.scale.pageAlignHorizontally = true;
-
-        if (this.game.device.desktop) {
-            // Desktop Settings
-        } else {
[…]

### 2015-03-10 _cordova/platforms/android/assets/www/js/common/MicrophoneButton.ts

@@ -1,79 +1,0 @@
-///<reference path="../def/phaser.d.ts" />
-import SpeechProcessor = require('../speechprocessing/SpeechProcessor');
-
-/**
- * Acts as a button for recording sound by interfacing with our speech processing singleton
- * For use in all application games
- */
-class MicrophoneButton extends Phaser.Button {
-    private speechProcessor : SpeechProcessor;
-    private isActive : boolean;
-    private isDisabled : boolean;
-    private clientResultCallback : Function;
-
-    private static DISABLED_FRAME : number = 2;
-    private static ACTIVE_FRAME : number = 1;
-    private static NORMAL_FRAME : number = 0;
-
-    /**
-     * Constructs a microphone button
-     *
-     * @param game The game context to attach the button to
-     * @param x The x coordinate to place the button
-     * @param y The y coordinate to place the button
-     * @param dataCallback A function callback that is executed on finishing recording with the data
-     */
-    constructor(game : Phaser.Game, x : number, y : number, dataCallback : Function) {
-        super(game, x, y, 'microphoneButton', this.onClickAction, this);
-        this.frame = MicrophoneButton.NORMAL_FRAME;
-        this.clientResultCallback = dataCallback;
-        this.isActive = false;
-        this.isDisabled = false;
-        this.speechProcessor = SpeechProcessor.getInstance();
-        game.add.existing(this);
-    }
-
-    /**
-     * Disables the button, disabling all functionality. If the microphone button is in the middle
-     * of recording, the recording will be thrown out.
-     */
-    public disable() {
-        this.frame = MicrophoneButton.DISABLED_FRAME;
-        this.isDisabled = true;
-    }
-
-    /**
-     * Enables the button, showing the current active state.
-     */
-    public enable() {
-        this.frame = this.isActive ? MicrophoneButton.ACTIVE_FRAME : MicrophoneButton.NORMAL_FRAME;
-        this.isDisabled = false;
-    }
-
-    /**
-     * Called on button click
-     */
-    private onClickAction() {
-        if (!this.isDisabled) {
-            if (this.isActive) {
-                this.isActive = false;
-                this.disable();
-                this.speechProcessor.stopRecording((result) => {
-                    this.clientResultCallback(result);
-                    this.enable();
-                });
-            } else {
-                this.disable();
-                this.speechProcessor.startRecording(() => {
-                    this.isActive = true;
-                    // Switch visual state and start processing
[…]

### 2015-03-10 _cordova/platforms/android/assets/www/js/mazegame/MazeGameState.ts

@@ -1,15 +1,0 @@
-///<reference path="../def/phaser.d.ts" />
-/**
- * The main maze game state
- */
-class MazeGameState extends Phaser.State {
-    public preload() {
-
-    }
-
-    public create() {
-
-    }
-}
-
-export = MazeGameState;

### 2015-03-10 _cordova/platforms/android/assets/www/js/menu/MainMenuState.ts

@@ -1,88 +1,0 @@
-///<reference path="../def/phaser.d.ts" />
-/**
- * The main menu of the application.
- */
-class MainMenuState extends Phaser.State {
-    private static MINI_GAMES : any = [
-        {state : 'BalloonGameState', icon : 'gameIconBalloons'},
-        {state : 'MazeGameState', icon : 'gameIconMaze'}
-    ];
-
-    private play : Phaser.Button;
-    private settings : Phaser.Button;
-    private selectUp : Phaser.Button;
-    private selectDown : Phaser.Button;
-    private background : Phaser.Sprite;
-
-    private combContainer : Phaser.Sprite;
-
-    private gameIcon : Phaser.Sprite;
-
-    private bee : Phaser.Sprite;
-
-    private currentSelected : number;
-
-    public preload() {
-
-    }
-
-    public create() {
-        this.currentSelected = 0;
-        this.background = this.game.add.sprite(0, 0, 'menuBackground');
-        this.bee = this.game.add.sprite(970, 95, 'beeBig');
-
-        this.combContainer = this.game.add.sprite(this.world.centerX - 230, 370, 'combContainer');
-
-        this.selectUp = this.add.button(this.world.centerX - 200, 300, 'upButton', this.onClickSelectUp, this);
-        this.selectDown = this.add.button(this.world.centerX - 200, 480, 'downButton', this.onClickSelectDown, this);
-        this.play = this.add.button(
-                            this.world.centerX + 50, 370,
-                            'playButton', () => { this.onClickPlay(this.game.state); }, this);
-        this.settings = this.add.button(
-                            this.world.width - 50, this.world.height - 50,
-                            'settingsButton', this.onClickSettings, this);
-        // Animate the bee
-        var anim = this.bee.animations.add('fly');
-        anim.play(10, true);
-        this.game.add.tween(this.bee).to({y:115}, 350, Phaser.Easing.Linear.None, true, 0, 1000, true);
-
-
-        this.gameIcon = null;
-
-        this.updateSelectedGame();
-    }
-
-    private updateSelectedGame() {
-        var selectedMinigame = MainMenuState.MINI_GAMES[this.currentSelected];
-        if (this.gameIcon != null) {
-            this.gameIcon.destroy();
-            this.gameIcon = null;
-        }
-        this.gameIcon = this.add.sprite(this.world.centerX - 219, 381, selectedMinigame.icon);
-    }
-
[…]

### 2015-03-10 _cordova/platforms/android/assets/www/js/speechprocessing/SpeechProcessor.ts

@@ -1,118 +1,0 @@
-import SpeechSettings = require('./SpeechSettings');
-import Server = require('../server/Server');
-import Microphone = require('./Microphone');
-import WordBank = require('./WordBank');
-
-/**
- * The speech processor singleton
- * This acts as the central speech therapy API endpoint for the rest of the program
- */
-class SpeechProcessor {
-    private static INSTANCE : SpeechProcessor = null;
-
-    private settings : SpeechSettings;
-    private microphone : Microphone;
-    private wordBank : WordBank;
-
-    private currentWord : string;
-
-    /**
-     * Should not be called directly. Use getInstance() instead.
-     */
-    constructor(callback ?: Function) {
-        if (SpeechProcessor.INSTANCE != null) {
-            throw 'Singleton already constructed!';
-        }
-
-        this.currentWord = null;
-
-        this.settings = new SpeechSettings();
-        this.wordBank = new WordBank();
-        this.wordBank.setWords(this.settings.getWordBank());
-
-        this.microphone = new Microphone(() => {
-            console.log('Microphone ready.');
-            if (callback) {
-                callback();
-            }
-        }, this.settings, this.wordBank);
-    }
-
-    /**
-     * Gets the singleton instance of the speech processor
-     * @param {Function?} callback The (optional) callback to call when the SpeechProcessor is fully constructed.
-     * @returns {SpeechProcessor} the speech processor instance
-     */
-    public static getInstance(callback ?: Function) : SpeechProcessor {
-        if (SpeechProcessor.INSTANCE == null) {
-            SpeechProcessor.INSTANCE = new SpeechProcessor(callback);
-        }
-
-        return SpeechProcessor.INSTANCE;
-    }
-
-    /**
-     * Start recording sound. Does nothing if sound is already being recorded.
-     * @param callback The function to call when recording has started
-     */
-    public startRecording(callback) : void {
-        this.microphone.start(callback);
-    }
-
-    /**
-     * Stop recording sound. Returns the sound recorded
-     */
-    public stopRecording(callback : Function) : any {
-        this.microphone.stop((result) => {
-            // Send recording to server
-            var server = Server.getInstance();
-            var pair = this.wordBank.getCurrentPair();
-            server.sendRecording(result[0], pair.right, this.getCorrectness(result));
-
-            // Continue the callback chain
-            callback(result);
-        });
-    }
-
-    /**
-     * Returns an integer representing correctness in the last word guess
[…]

### 2015-03-10 _cordova/platforms/android/assets/www/js/speechprocessing/SpeechSettings.ts

@@ -1,95 +1,0 @@
-/**
- * Encapsulation of the speech settings specified by the user
- */
-class SpeechSettings {
-    private static DEFAULT_SOUND : any = 'R';
-    private static DATA_MAP : any = {
-
-        /*
-        Global sphinx maps
-        (contain all words possible and their phonemes and recognition grammars)
-        */
-        sphinxWords : [
-            ["GREEN", "G R IY N"], ["GWEEN", "G W IY N"],
-            ["RABBIT", "R AE B AH T"], ["WABBIT", "W AE B AH T"],
-            ["AIR", "EH R"], ["AIW", "EH W"],
-            ["ARE", "AA R"], ["AWE", "AA W"],
-            ["BAR", "B AA R"], ["BAW", "B AA W"],
-            ["BEAR", "B EH R"], ["BEAW", "B EH W"],
-            ["BOAR", "B AO R"], ["BOAW", "B AO W"],
-            ["CAR", "K AA R"], ["CAW", "K AA W"],
-            ["CARE", "K EH R"], ["CAWE", "K EH W"]
-        ],
-
-        sphinxGrammars : [
-            {word : "GREEN", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "GWEEN"}, {from: 0, to: 1, word: "GREEN"}]}},
-            {word : "RABBIT", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "WABBIT"}, {from: 0, to: 1, word: "RABBIT"}]}},
-            {word : "AIR", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "AIW"}, {from: 0, to: 1, word: "AIR"}]}},
-            {word : "ARE", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "AWE"}, {from: 0, to: 1, word: "ARE"}]}},
-            {word : "BAR", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "BAW"}, {from: 0, to: 1, word: "BAR"}]}},
-            {word : "BEAR", g : {numStates: 2, start: 0, end: 1, transitions: [{from: 0, to: 1, word: "BEAW"}, {from: 0, to: 1, word: "BEAR"}]}},
[…]

### 2015-03-10 _cordova/www/js/App.ts

@@ -1,37 +1,0 @@
-///<reference path="./def/phaser.d.ts" />
-import SpeechProcessor = require('./speechprocessing/SpeechProcessor');
-
-// Boot state
-import BootState = require('./BootState');
-
-// Menu states
-import MainMenuState = require('./menu/MainMenuState');
-import OptionMenuState = require('./menu/OptionMenuState');
-
-// Maze game states
-import MazeGameState = require('./mazegame/MazeGameState');
-
-// Balloon game states
-import BalloonGameState = require('./balloongame/BalloonGameState');
-
-/**
- * Main Application class
- */
-class App extends Phaser.Game {
-
-    constructor() {
-        super(1280, 720, Phaser.AUTO, '', null);
-
-        // Setup states
-        this.state.add("BootState", BootState);
-        this.state.add("MainMenuState", MainMenuState);
-        this.state.add("OptionMenuState", OptionMenuState);
-        this.state.add("BalloonGameState", BalloonGameState);
-        this.state.add("MazeGameState", MazeGameState);
-
-        // Start application
-        this.state.start("BootState");
-    }
-}
-
-export = App;

### 2015-03-10 _cordova/www/js/common/HoneyCounter.ts

@@ -1,35 +1,0 @@
-///<reference path="../def/phaser.d.ts" />
-
-class HoneyCounter extends Phaser.Sprite {
-	private count : number;
-	private countText : Phaser.Text;
-
-	/**
-     * Constructs a honey counter
-     *
-     * @param game The game context to attach the button to
-     * @param x The x coordinate to place the honey counter
-     * @param y The y coordinate to place the honey counter
-
-     */
-    constructor(game : Phaser.Game, x : number, y : number) {
-        super(game, x, y, 'honey');
-        var wordStyle = { font: "45px Cambria", fill: "#F2DE5A", align: "center" };
-        this.count = 0;
-        this.countText = game.add.text(x + 60, y, "" + this.count, wordStyle);
-        this.countText.setText("" + 1);
-        game.add.existing(this);
-    }
-
-    /*
-	 * Adds num to the current count of the honey counter
-	 *
-	 * @param num the number to add to the honey counter
-    */
-    public addHoney(num : number) {
-    	this.count = this.count + num;	
-    	this.countText.setText("" + this.count);
-    }
-}
-
-export = HoneyCounter;

### 2015-03-10 _cordova/www/js/menu/OptionMenuState.ts

@@ -1,31 +1,0 @@
-///<reference path="../def/phaser.d.ts" />
-
-import Server = require('../server/Server');
-
-/**
- * The option menu of the application.
- */
-class OptionMenuState extends Phaser.State {
-    private server : Server;
-    private keyText : Phaser.Text;
-    private back : Phaser.Button;
-
-    public preload() {
-        this.server = Server.getInstance();
-    }
-
-    public create() {
-        var key = this.server.getKey();
-        var wordStyle = { font: "45px Arial", fill: "#333333", align: "center" };
-        this.keyText = this.game.add.text(this.world.width / 3, this.world.height / 10, key, wordStyle);
-        this.back = this.add.button(
-            10, 10,
-            'backButton', () => { this.onClickBack(this.game.state); }, this);
-    }
-
-    private onClickBack(state) {
-        state.start('MainMenuState', true, false);
-    }
-}
-
-export = OptionMenuState;

### 2015-03-10 _cordova/www/js/speechprocessing/RecognizerConsumer.ts

@@ -1,114 +1,0 @@
-import SpeechSettings = require('./SpeechSettings');
-
-/**
- * RecognizerConsumer is a consumer that recognizes hypothesis based on a model.
- */
-class RecognizerConsumer {
-    private settings : SpeechSettings;
-    private worker : Worker;
-    private callbackIndex : number;
-    private callbackSequence : Function[];
-
-    private onStopped : Function;
-
-    private words : any;
-    private grammars : any;
-    private hypotheses : any[];
-
-    constructor(worker : Worker, settings : SpeechSettings, onStopped : Function) {
-        this.onStopped = onStopped;
-        this.worker = worker;
-        this.worker.onmessage = (e) => {
-            this.onWorkerMessage(e);
-        }
-
-
-        this.hypotheses = [];
-
-        this.settings = settings;
-        this.words = settings.getSphinxWords();
-        this.grammars = settings.getSphinxGrammars();
-    }
-
-    /**
-     * Initializes the worker, relies on the worker-message rely to
-     * simulate callbacks tracked by this class state.
-     * @param callback The function to be notified when ready
-     */
-    public initWorkerData(callback : Function) : void {
-        this.worker.postMessage({'command' : 'initialize'});
-        // Will execute these callbacks in sequence when worker responds to main UI thread after media loading.
-        this.callbackSequence = [this.loadWords];
-        for (var i = 0; i < this.grammars.length; i++) {
-            var closure = ((i) => {
-                return () => {
-                    this.loadGrammar(i);
-                };
-            })(i);
-            this.callbackSequence.push(closure);
-        }
-        this.callbackSequence.push(callback);
-        this.callbackIndex = 0;
-    }
-
-    /**
-     * Loads the words to recognize
-     */
-    private loadWords() : void {
-        // load words
-        this.worker.postMessage({'command' : 'addWords', 'data' : this.words});
-    }
-
-    /**
-     * Loads the ith grammar to recognize
-     */
-    private loadGrammar(i : number) : void {
-        this.worker.postMessage({'command' : 'addGrammar', 'data' : this.grammars[i].g});
-    }
-
-    /**
-     * Get the hypotheses stored by this recognizer consumer
-     * @returns The hypotheses stored.
-     */
-    public getHypotheses() : any[] {
-        return this.hypotheses;
-    }
-
-    /**
-     * Callback to deal with worker messages back to the main thread
-     * @param e The message sent to the main thread
[…]

### 2015-03-10 _cordova/www/js/speechprocessing/WordBank.ts

@@ -1,55 +1,0 @@
-/**
- * WordBank is a managed collection of words to speak
- */
-class WordBank {
-    private current : number;
-    private words : any[];
-
-    constructor() {
-        this.words = [];
-        this.current = 0;
-    }
-
-    /**
-     * Sets the current word bank
-     * @param wordBank The word bank to set
-     */
-    public setWords(wordBank : string[]) {
-        this.words = wordBank;
-        this.current = 0;
-    }
-
-    /**
-     * Gets the current (right/wrong) pair
-     * @returns {any|null} The pair, null if not found
-     */
-    public getCurrentPair() {
-        return this.words[this.current] || null;
-    }
-
-    /**
-     * Gets the current (right/wrong) index
-     * @returns {number} The index
-     */
-    public getCurrentIndex() {
-        return this.current;
-    }
-
-    /**
-     * Gets the next word to display, returns null if one is not
-     * available.
-     * @returns {string} The word
-     */
-    public next() : string {
-        if (this.words.length == 0) return null;
-
-        this.current++;
-        this.current %= this.words.length;
-
-        var pair = this.words[this.current];
-
-        return pair.right;
-    }
-}
-
-export = WordBank;

### 2015-03-10 Paper/paper.tex

@@
 Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time.
-As these were the two most important features Kreider discussed, we designed Kimbee around them as core features.
+As these were the two most important features Kreider discussed, we designed {\em Kimbee} around them as core features.
 
@@
 We target this project toward web technologies to allow wide distribution and adoption.
-From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay.
-This required us to explore various new web technologies including HTML5 Web Workers for multithreading and the UserMedia HTML5 API.
+From a design standpoint, we aimed to make each system loosely connected and non-disruptive to game-play.
+This required us to explore various new web technologies including HTML5 Web Workers for multi-threading and the UserMedia HTML5 API.
 
@@
 The web technology stack is advanced enough to handle our needs: there is a JavaScript port of the popular speech processing library CMU Sphinx, and we now have access to the user's microphone via UserMedia HTML5 API.
-After creating our project in the browser, we then can translate it to native applications via Apache Cordova, a web distribution technology based on embeddeding a web component inside a native application container on mobile devices.
+After creating our project in the browser, we then can translate it to native applications via Apache Cordova, a web distribution technology based on embedding a web component inside a native application container on mobile devices.
 
@@
 These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data.
-Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers.
-When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads.
+Harvesting and processing microphone levels is a multi-threaded process implemented with HTML5 Web Workers.
+When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in separate threads.
 Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
@@
 \begin{enumerate}
-  \item Web Workers are initalized to start processing the audio stream in parallel.
+  \item Web Workers are initialized to start processing the audio stream in parallel.
   \vspace{-6 pt}
@@
 The {\em Server API} is what connects the {\em Game} to our central recording server.
-Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present.
+Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a Internet connection is present.
 A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device.
@@
 \subsection{Central Server}
-The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Game} instances and the {\em Therapist Portal}.
+The {\em Central Server}, see Figure \ref{fig:tech}, facilitates communication between all the {\em Game} instances and the {\em Therapist Portal}.
 It is written in Node JS and stores data in a MongoDB instance.
@@
 \subsubsection{Audio Encoding \& Recording Storage}
-When a audio file is recieved by a {\em Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
+When a audio file is received by a {\em Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone.
 This file is then compressed and stored into the database as a recording.

### 2015-03-10 src/server/index.js
fixed

@@ -46,7 +46,7 @@ mongoose.connection.on('open', function () {
     app.post('/api/recording/add', recordings.hasChildId, recordings.add);
     app.get('/api/recording', users.isAuthenticated, recordings.getRecording);
 
-    app.listen(1337);
+    app.listen(process.env.PORT || 1337);
 
     console.log('Listening on port 1337...');
 });

### 2015-03-10 _cordova/platforms/android/assets/www/js/common/DOMTextField.ts
Spelling is hard

@@ -1,31 +1,0 @@
-///<reference path="../def/phaser.d.ts" />
-
-/**
- * Represents a text field in the game
- * which is a DOM text field floated over the game
- * and kept in context of the virtual pixel coordinates
- */
-class DOMTextField {
-    private game : Phaser.Game;
-    private x : number;
-    private y : number;
-    private w : number;
-    private h : number;
-
-    constructor(game : Phaser.Game, x : number, y: number, w : number, h : number) {
-        this.game = game;
-        this.x = x;
-        this.y = y;
-        this.w = w;
-        this.h = w;
-
-        this.addToCanvas();
-    }
-
-
-    private addToCanvas() {
-        var parent = this.game.canvas.parentElement;
-    }
-}
-
-export = DOMTextField;

### 2015-03-10 _cordova/platforms/android/assets/www/js/server/Server.ts

@@ -1,88 +1,0 @@
-///<reference path="../def/jquery.d.ts" />
-declare var Hashids : any;
-
-/**
- * The server API singleton
- * This acts as the central server API endpoint for the rest of the app
- */
-class Server {
-    private static URL : string = "/api/";
-
-    private static INSTANCE : Server = null;
-
-    private key : string;
-    private enabled : boolean;
-
-    /**
-     * Should not be called directly. Use getInstance() instead.
-     */
-    constructor() {
-        if (Server.INSTANCE != null) {
-            throw 'Singleton already constructed!';
-        }
-
-        this.enabled = true;
-
-        // Set the client token to a new generated token if one has not
-        // been generated yet.
-        var token : string = window.localStorage.getItem('token');
-        if (token) {
-            this.key = token;
-        } else {
-            var hash : any = new Hashids(Math.random() * 2147483647 + "");
-            this.key = hash.encode((new Date()).getTime());
-            window.localStorage.setItem('token', this.key);
-        }
-
-        console.log(this.key);
-    }
-
-    /**
-     * Gets the singleton instance of the API
-     * @returns {API} the speech processor instance
-     */
-    public static getInstance() : Server {
-        if (Server.INSTANCE == null) {
-            Server.INSTANCE = new Server();
-        }
-
-        return Server.INSTANCE;
-    }
-
-    /**
-     * Helper returns true if this client can send information to the server
-     * @returns {boolean} True if we can send, false otherwise
-     */
-    private canSend() : boolean {
-        return this.enabled && this.key != null;
-    }
-
-    /**
-     * Get the client key used by the application
-     * @return {string} The client key
-     */
-    public getKey() : string {
-        return this.key;
-    }
-
-    /**
-     * Sends a recording to the server
-     * @param {number[]} rawData The raw data of the recording
-     * @param {string} word The word they are saying
-     */
-    public sendRecording(rawData : any, word : string, correctness : number) : void {
-        if (!this.canSend()) return;
-
-        (<any> $).post(Server.URL + 'recording/add', {
-            token : this.key,
-            raw : rawData,
-            word : word,
-            correctness : correctness
-        }, function(data) {
-            console.log("Recording saved on server. Response:");
-            console.log(data);
-        });
-    }
-}
-
-export = Server;

### 2015-03-10 _cordova/platforms/android/assets/www/js/speechprocessing/AudioStorageConsumer.ts

@@ -1,52 +1,0 @@
-/**
- * AudioStorageConsumer is a consumer that simply stores all audio given to it.
- */
-class AudioStorageConsumer {
-    private samples : any;
-    private onStopped : Function;
-
-    constructor(onStopped : Function) {
-        this.samples = [];
-        this.onStopped = onStopped;
-    }
-
-    /**
-     * Get the samples stored by this storage consumer
-     * @returns The samples stored.
-     */
-    public getSamples() {
-        // Flattened samples
-        return this.samples;
-    }
-
-    /**
-     * Process the data dished out by the recorder
-     */
-    private processData(data : any) {
-        this.samples.push(data);
-    }
-
-    /**
-     * Clears this consumers data store
-     */
-    public clear() : void {
-        this.samples = [];
-    }
-
-    /**
-     * Called by web worker message postings via ducktyping
-     * @param e The message posted
-     */
-    public postMessage(e : any) {
-        switch (e.command) {
-            case 'rawData':
-                this.processData(e.raw);
-                break;
-            case 'stop':
-                this.onStopped();
-                break;
-        }
-    }
-}
-
-export = AudioStorageConsumer;

### 2015-03-10 _cordova/platforms/android/assets/www/js/speechprocessing/Microphone.ts

@@ -1,178 +1,0 @@
-import AudioStorageConsumer = require('./AudioStorageConsumer');
-import RecognizerConsumer = require('./RecognizerConsumer');
-import SpeechSettings = require('./SpeechSettings');
-import WordBank = require('./WordBank');
-
-// Vanilla javascript / audio api declarations for typescript
-declare var AudioContext : any;
-declare var window : any;
-declare var navigator : any;
-declare var AudioRecorder : any;
-
-// Deal with prefixed APIs
-window.AudioContext = window.AudioContext || window.webkitAudioContext;
-navigator.getUserMedia = navigator.getUserMedia ||
-                         navigator.webkitGetUserMedia ||
-                         navigator.mozGetUserMedia;
-
-/**
- * Manages communication with the device microphone
- */
-class Microphone {
-    private currentlyRecording : boolean;
-    private audioContext : any;
-    private audioRecorder : any;
-    private clientReadyFunction : Function;
-    private clientResultFunction : Function;
-
-    private numberConsuming : number;
-
-    private storageConsumer : AudioStorageConsumer;
-    private recognizerConsumer : RecognizerConsumer;
-
-    private settings : SpeechSettings;
-    private wordBank : WordBank;
-
-    constructor(clientReadyFunction : Function, settings : SpeechSettings, wordBank : WordBank) {
-        this.settings = settings;
-        this.wordBank = wordBank;
-        this.currentlyRecording = false;
-        this.audioRecorder = null;
-        this.clientReadyFunction = clientReadyFunction;
-
-        try {
-            this.audioContext = new window.AudioContext();
-        } catch (e) {
-            console.log("Error initializing Web Audio");
-        }
-
-        // Get user permissions for audio capture
-        if (navigator.getUserMedia) {
-            navigator.getUserMedia({audio: true},
-                                    (stream) => {this.onInitAudio(stream)},
-                                    (e) => {console.log("No live audio input in this browser");});
-        } else {
-            throw "No web audio support in this browser";
-        }
-    }
-
-    /**
-     * Called when user grants permission to initialize audio capture
-     */
-    private onInitAudio(stream : any) {
-        var volume = this.audioContext.createGain();
-        var input = this.audioContext.createMediaStreamSource(stream);
-        input.connect(volume);
-        this.audioRecorder = new AudioRecorder(input, {volume : volume, worker : './js/vendor/audioRecorderWorker.js'});
-
-        this.spawnConsumers(() => {
-            this.clientReadyFunction();
-        });
-    }
-
-    /**
[…]

### 2015-03-10 _cordova/platforms/android/src/com/nickaaronryan/kimbee/CordovaApp.java

@@ -1,35 +1,0 @@
-/*
-       Licensed to the Apache Software Foundation (ASF) under one
-       or more contributor license agreements.  See the NOTICE file
-       distributed with this work for additional information
-       regarding copyright ownership.  The ASF licenses this file
-       to you under the Apache License, Version 2.0 (the
-       "License"); you may not use this file except in compliance
-       with the License.  You may obtain a copy of the License at
-
-         http://www.apache.org/licenses/LICENSE-2.0
-
-       Unless required by applicable law or agreed to in writing,
-       software distributed under the License is distributed on an
-       "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
-       KIND, either express or implied.  See the License for the
-       specific language governing permissions and limitations
-       under the License.
- */
-
-package com.nickaaronryan.kimbee;
-
-import android.os.Bundle;
-import org.apache.cordova.*;
-
-public class CordovaApp extends CordovaActivity
-{
-    @Override
-    public void onCreate(Bundle savedInstanceState)
-    {
-        super.onCreate(savedInstanceState);
-        super.init();
-        // Set by <content src="index.html" /> in config.xml
-        loadUrl(launchUrl);
-    }
-}

### 2015-03-10 _cordova/www/js/balloongame/BalloonGameState.ts

@@ -1,236 +1,0 @@
-///<reference path="../def/phaser.d.ts" />
-import MicrophoneButton = require('../common/MicrophoneButton');
-import HoneyCounter = require('../common/HoneyCounter');
-import SpeechProcessor = require('../speechprocessing/SpeechProcessor');
-
-
-/**
- * The main balloon game state
- */
-class BalloonGameState extends Phaser.State {
-    private background : Phaser.Sprite;
-    private bee : Phaser.Sprite;
-    private balloon : Phaser.Sprite;
-    private flower : Phaser.Sprite;
-    private honey : Phaser.Group;
-    private tada : Phaser.Sound;
-    private tryagain : Phaser.Sound;
-    private word : Phaser.Text;
-    private microphone : MicrophoneButton;
-    private speechProcessor : SpeechProcessor;
-    private honeyCounter : HoneyCounter;
-    private wasp : Phaser.Group;
-    private fairy : Phaser.Group;
-    private height : number;
-    private width : number;
-    private lastX : number;
-    private lost : boolean;
-    private lastHoneyX : number;
-    private honeyChain : number;
-    private micPause : boolean;
-    private gameOver : Phaser.Text;
-
-    public preload() {
-        this.speechProcessor = SpeechProcessor.getInstance();
-    }
-
-    public create() {
-        var firstWord = this.speechProcessor.getNextWord();
-        var wordStyle = { font: "45px Cambria", fill: "#333333", align: "center" };
-        var gameOverStyle = { font: "80px Cambria", fill: "#000000", align: "center" };
-        this.tada = this.game.add.audio('tada');
-        this.tryagain = this.game.add.audio('try-again');
-
-        this.height = this.world.height;
-        this.width = this.world.width;
-        this.lastX = this.width / 5;
-
-
-        this.background = this.game.add.sprite(0, 0, 'balloonsBackground');
-        this.flower = this.game.add.sprite(this.width * 4 / 5, this. height / 2, 'flower');
-        this.bee = this.game.add.sprite(this.width / 5, this.height / 2, 'beeBig');
-        this.bee.scale.x = 0.7;
-        this.bee.scale.y = 0.7;
-        var anim = this.bee.animations.add('fly');
-        anim.play(10, true);
-        this.game.physics.enable(this.bee, Phaser.Physics.ARCADE);
-        this.bee.body.immovable = true;
-        this.bee.body.velocity.x = 0;
[…]

### 2015-03-10 _cordova/www/js/bootstrap.ts

@@ -1,32 +1,0 @@
-// require.js (our library that manages all these javascript files)
-// needs a "main file" to derive all dependencies from and execute.
-// This is that file.
-
-///<reference path="./def/phaser.d.ts" />
-
-import App = require('./App');
-
-declare var cordova : any;
-declare var PhoneGap : any;
-declare var phonegap : any;
-
-/**
- * Determine whether the file loaded from PhoneGap or not
- */
-function isPhoneGap() {
-    return (typeof cordova != "undefined"
-         || typeof PhoneGap != "undefined"
-         || typeof phonegap != "undefined")
-        && /^file:\/{3}[^\/]/i.test(window.location.href)
-        && /ios|iphone|ipod|ipad|android/i.test(navigator.userAgent);
-}
-
-function ready() {
-    new App();
-}
-
-if (isPhoneGap()) {
-    document.addEventListener("deviceready", ready, false);
-} else {
-    ready();
-}

### 2015-03-10 src/game/js/balloongame/BalloonGameState.ts
Fixed key font, mobile taps register

@@ -291,6 +291,18 @@ class BalloonGameState extends Phaser.State {
             if (this.game.input.mousePointer.y > this.bee.body.y + this.bee.body.height / 4 && this.game.input.mousePointer.y < this.bee.body.bottom - this.bee.body.height / 4) {
                 this.bee.body.velocity.y = 0;
             }
+        } else if (this.game.input.pointer1.isDown && !this.micPause) {
+            if (this.game.input.pointer1.y > this.bee.body.y - this.bee.body.height / 4) {
+                this.bee.body.velocity.y = this.height / 3;
+            }
+
+            if (this.game.input.pointer1.y < this.bee.body.y + this.bee.body.height / 4) {
+                this.bee.body.velocity.y = this.height / -3;
+            }
+
+            if (this.game.input.pointer1.y > this.bee.body.y + this.bee.body.height / 4 && this.game.input.pointer1.y < this.bee.body.bottom - this.bee.body.height / 4) {
+                this.bee.body.velocity.y = 0;
+            }
         } else {
             this.bee.body.velocity.y = 0;
         }

### 2015-03-10 src/game/js/balloongame/BalloonGameState.ts
lets you pass if you suck and get 3 wrong

@@ -130,15 +130,26 @@ class BalloonGameState extends Phaser.State {
     }
 
     private onWrong() {
-        if(this.numCorrect == -3) {
-            if(this.level != 1) {
-                this.level = this.level - 1;
-            }
-            this.numCorrect = 0;
-        } else {
+        if(this.numWrong == 2) {
+            if(this.numCorrect == -3) {
+                if(this.level != 1) {
+                    this.level = this.level - 1;
+                }
+                this.numCorrect = 0;
+            } else {
             this.numCorrect = this.numCorrect - 1;
+            }
+            this.numWrong = 0;
+            var nextWord = this.speechProcessor.getNextWord(this.level);
+            this.word.setText("Now say: " + nextWord);
+            this.word.visible = false;
+            this.game.paused = false;
+            this.microphone.visible = false; 
+            this.unpause();
+        } else {
+            this.tryagain.play();
+            this.numWrong = this.numWrong + 1;
         }
-        this.tryagain.play();
     }
 
     private honeyCollision(bee : Phaser.Sprite, honey : Phaser.Sprite) {
@@ -263,7 +274,7 @@ class BalloonGameState extends Phaser.State {
         var correctness = this.speechProcessor.getCorrectness(result);
         console.log('CORRECTNESS: ' + correctness);
 
-        if(correctness == 0) {
+        if(correctness == 0 || correctness == 1) {
             this.onWrong();
         }
 

### 2015-03-10 src/game/js/server/Server.ts
fixed

@@ -6,7 +6,7 @@ declare var Hashids : any;
  * This acts as the central server API endpoint for the rest of the app
  */
 class Server {
-    private static URL : string = "/api/";
+    private static URL : string = "http://kimbee.herokuapp.com/api/";
 
     private static INSTANCE : Server = null;
 

### 2015-03-11 Paper/paper.tex
Spelling AND DONE BOYS

@@
 From a design standpoint, we aimed to make each system loosely connected and non-disruptive to game-play.
-This required us to explore various new web technologies including HTML5 Web Workers for multi-threading and the UserMedia HTML5 API.
+This required us to explore various new web technologies including HTML5 Web Workers for multiple threads and the UserMedia HTML5 API.
 
@@
   \vspace{-6 pt}
-  \item Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
+  \item Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are then queried for final results of their processing.
 \end{enumerate}
